---
title             : "Neural correlates of choosing between bundles of description and experience-based risky options"
shorttitle        : "Description versus experience-based risk"

author: 
  - name          : "A. Zeynep Enkavi"
    affiliation   : "1"
    corresponding : yes
    address       : "1200 E. Colorado Blvd., Pasadena, CA 91125"
    email         : "zenkavi@caltech.edu"
    role:         
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Gabriela Tavares"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
  - name          : "Antonio Rangel"
    affiliation   : "1"
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Division of Humanities and Social Sciences, California Institute of Technology"
  - id            : "2"
    institution   : "Google"

authornote:

abstract: |
  Enter abstract here
  
keywords          : "risk, uncertainty, lottery, reinforcement learning"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

# Introduction

# Methods

## Participants

```{r echo=FALSE}
demog = read.table('/Users/zeynepenkavi/Downloads/GTavares_2017_arbitration/bids_nifti_wface/participants.tsv', sep='\t', header=TRUE)
num_female = sum(demog$sex == "F")
mean_age = round(mean(demog$age), 2)
```

27 Caltech undergraduates were recruited for the experiment. Two subjects could not be scanned due to discomfort in the scanner so data from 25 subjects  (`r num_female` female, mean age = `r mean_age`) are analyzed. Each subjects completed 300 trials broken down to five runs completed in a single sessions. Participants were compensated $30 for their time and received additional earnings based on their performance as described below. All procedures were approved by the Caltech's IRB and all subjects provided informed consent prior to participation.

## Task

## Procedure

## Behavioral data preprocessing

## Neuroimaging data preprocessing

## Data analysis software
The list of software packages and their versions used for analyses can be found at ...

# Results

## Raw behavioral results

## Cognitive modeling

## Neuroimaging results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
