---
title             : "Neural correlates of choosing between bundles of description and experience-based risky options"
shorttitle        : "Description versus experience-based risk"

author: 
  - name          : "A. Zeynep Enkavi"
    affiliation   : "1"
    corresponding : yes
    address       : "1200 E. Colorado Blvd., Pasadena, CA 91125"
    email         : "zenkavi@caltech.edu"
    role:         
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Gabriela Tavares"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
  - name          : "Antonio Rangel"
    affiliation   : "1"
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Division of Humanities and Social Sciences, California Institute of Technology"
  - id            : "2"
    institution   : "Google"

authornote:

abstract: |
  Enter abstract here
  
keywords          : "risk, uncertainty, lottery, reinforcement learning"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

# Introduction

# Materials and Methods

## Participants

```{r echo=FALSE}
demog = read.table('/Users/zeynepenkavi/Downloads/GTavares_2017_arbitration/bids_nifti_wface/participants.tsv', sep='\t', header=TRUE)
num_female = sum(demog$sex == "F")
mean_age = round(mean(demog$age), 2)
```

27 Caltech undergraduates were recruited for the experiment. Two subjects could not be scanned due to discomfort in the scanner so data from 25 subjects  (`r num_female` female, mean age = `r mean_age`) are analyzed. Each subjects completed 300 trials broken down to five runs completed in a single sessions. Participants were compensated $30 for their time and received additional earnings based on their performance as described below. All procedures were approved by the Caltech's IRB and all subjects provided informed consent prior to participation.

## Task

Participants completed the task in the fMRI scanner. The task consisted of 300 trials broken down into five runs of 60 trials. Each trial began with a central fixation cross that remained on the screen for a random inter-trial interval between four and seven seconds plus a variable amount as described below.

In each trial, the participant had to choose between two pairs presented on the left and right of the screen separated with a gray vertical line. Each pair contained a fractal at the top and a lottery at the bottom. The fractals were randomized across participants from a sample of 25 but they remained the same for the duration of the experiment for a given participant. Each fractal was associated with a probability of a `$`1 reward, which were not shown on the screen. These probabilities drifted slowly and independently between 0.25 and 0.75, according to a Gaussian random walk with $\sigma = 0.025$. Participants were told that these reward probabilities drifted slowly and independently but were not informed about the bounds or the drift rate.

## Behavioral data preprocessing

## Neuroimaging data preprocessing

## Data analysis software
The list of software packages and their versions used for analyses can be found at ...

# Results

## Raw behavioral results

## Cognitive modeling

## Neuroimaging results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
