---
title             : "Allocation of control when choosing between bundles of description and experience-based risky options"
shorttitle        : "Title"

author: 
  - name          : "A. Zeynep Enkavi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1200 E. Colorado Blvd., Pasadena, CA 91125"
    email         : "zenkavi@caltech.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Gabriela Tavares"
    affiliation   : "2"
    role:
      - Conceptualization
      - Investigation
  - name          : "Antonio Rangel"
    affiliation   : "1"
    role:
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "California Institute of Technology"
  - id            : "2"
    institution   : "Google"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Instead of typing your R code in this chunk, you can also pull some code from an external script (preferably in the same project folder). You can do this using the read_chunk function. In your manuscript, create a code chunk that reads in this external script:

```{r external, include = FALSE}
knitr::read_chunk("myScript.R")
```

You can then run subsections of this external script as follows:

```{r plot-audiogram}
```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Task

## Procedure

## Data preprocessing

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

## Raw behavioral results

## Cognitive modeling

# Discussion



\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
