---
title: "Experience vs. description based decision-making project: Behavioral data descriptive stats and cleaning"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(DT)
library(here)
```

Set theme for plots

```{r}
theme_set(theme_bw())
```

Specify path for bespoke helper functions

```{r}
helpers_path = here('helpers/')
```

Read in raw behavioral data

```{r}
source(paste0(helpers_path,'00_get_behavioral_data.R'))
```

# Descriptive stats

## Number of subjects

How many subjects do we have raw data from?

```{r}
length(unique(beh_data$subnum))
```

How many sessions per subject and trials per session? (There is no subject 21 or 26)

```{r}
with(beh_data, table(subnum, session))
```

## Response times

What is the response times distribution?

```{r}
beh_data %>%
  ggplot()+
  geom_histogram(aes(reactionTime), bins=50)
```

How many trials have negative RTs?

```{r}
nrow(beh_data %>% 
  filter(reactionTime < 0))
```

How many trials have very fast RTs (RT<.2 sec)?

```{r}
nrow(beh_data %>% 
  filter(reactionTime >0 & reactionTime <.2))
```

Are trials with RT<.2 disproportionately from one subject?

There is one subject with more trials with unrealistic RTs (07) but even for this subject the number of trials-to-be-excluded is <5% of their data so not excluding any subjects entirely based on RT data. Will exclude individual trials that have unrealistic RTs.

```{r}
beh_data %>% 
  filter(reactionTime < 0.2) %>%
  count(subnum)
```

## Choices

There are two choice-related columns. `responded` and `choiceLeft`. 

The 0's in `responded` map onto those trials with `reactionTime` < 0.

```{r}
table(beh_data$responded)
```

Excluding the non-response trials is `choiceLeft` equally distributed?

```{r}
beh_data %>%
  filter(responded == 1) %>%
  count(choiceLeft)
  
```

# Missing values

Are there missing values anywhere?

```{r}
summary(beh_data)
```

The `NA`s in `fractalDraw`, `leftFractalReward`, `rightFractalReward` are on a non-response trial so they will already be excluded.

```{r}
beh_data %>%
  filter(is.na(leftFractalReward))
```

# Data cleaning steps

- Exclude non-responded trials.
- Exclude trials RTs <.2 seconds. 

These will be incorporated in `clean_behavioral_data.R`

What is left after these steps?

```{r}
clean_beh_data = beh_data %>%
  filter(responded == 1,
         reactionTime > .2)

with(clean_beh_data, table(subnum, session))
```

