---
title: 'Experience vs. description based decision-making project: RL model fits onto
  behavioral data'
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Set up

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(rstan)
library(brms)
library(GGally)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r}
helpers_path = here('helpers/')
```

# Read in data

```{r include=FALSE}
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'extract_var_for_stan.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path, 'facet_wrap_equal.R'))
source(paste0(helpers_path, 'organize_stan_output.R'))
source(paste0(helpers_path, 'identifiability_analysis.R'))
```

Set theme for plots

```{r}
theme_set(theme_bw())
```

# Manipulation check

Is there evidence if "learning" to justify the fitting of an RL model?

As time goes by are subjects more likely to choose the fractal with the higher reward probability? There is a subtle increase in the probability of choosing the fractal with the higher reward probability. This change in probability of choosing the fractal with the higher reward probability is larger when the reward depends only on fractals (except for the last session, which bizarrely has the opposite pattern).

```{r}
tmp = clean_beh_data %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0)))
p1 = tmp %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  # ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="All trials", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))+
  scale_color_manual(values=cbbPalette)+
  theme(legend.position="bottom")

p2 = tmp %>%
  filter(probFractalDraw>.5) %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  # ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="p(Fractal)>.5", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))+
  scale_color_manual(values=cbbPalette)+
  theme(legend.position="bottom")

grid.arrange(p1, p2, nrow=1, ncol=2)
```

```{r}
rm(p1, p2)
```

Bayesian multilevel model checking if the slopes in the above figure are different than 0. 

When looking at all trials (left figure) the overall slope of all sessions is not different than 0 (not shown below). When including an interaction term with session number then there is a very small but non-zero increase in the probability of choosing the better fractal (i.e. learning) in sessions 1 and 3 but not in the other sessions.

```{r eval=FALSE}
# The default prior for population parameters is an improper flat prior over the reals
m = brm(choseBetterFractal ~ trialNum*as.factor(session) + (1|subnum),
        data=tmp, family=bernoulli(link="logit"))
```

```{r eval=FALSE}
summary(m)
```

Filtering only trials where probability of a fractal draw is >.5, i.e. trials where learning about the fractal values would be more consequential we find a slightly stronger increase in the probability of choosing the better fractal later in the session in sessions 1 through 3 though still no effect for the other sessions.

```{r eval=FALSE}
m2= brm(choseBetterFractal ~ trialNum*as.factor(session) + (1|subnum),
        data=tmp %>% filter(probFractalDraw>.5), family=bernoulli(link="logit"))
```

```{r eval=FALSE}
summary(m2)
```

```{r eval=FALSE}
rm(m, m2)
```

```{r echo=FALSE}
rm(tmp)
```

# Define model

On each trial subjects process not only the two fractals but also their relevance to the trial's reward, as well as, the lottery information. So to describe the choice process in this task, including accounting for learning about fractals across trials, the computational model must include all of these factors.

In this model the probability of choosing the option on the left is described as a softmax function that depends on the value difference between the left and right pairs. The free parameter $\beta$ controls the extent to which the choice depends on this value difference instead of chance.

$$p(choice = left) = \frac{1}{1+e^{-\beta(V_{left} - V_{right})}}$$
The value of each pair is defined as a weighted average of both of its components. The two components of each pair, the lottery and the fractal is weighted proportional to their relevance for that trial.

$$V_i = (1-w(pFrac))EV_i + w(pFrac)QV_i, \:i \in \{left, right\}$$
Given the large amount of evidence from behavioral economics suggesting that people do not perceive probabilities linearly but distort them the probability weighting function $\w$ is conceived of as a non-linear function. As described in Gonzalez and Wu (1999) we parameterized it as

$$w(pFrac) = \frac{\delta*pFrac^{\gamma}}{\delta*pFrac^{\gamma}+(1- pFrac)^{\gamma}}$$
where $\delta$ (primarily) controls the elevation/intercept to capture attractiveness of the outcome weighted by the distorted probability and $\gamma$ (primarily) controls curvature to capture the discriminability of distorted probabilities from each other. They call this shape "linear in log odds." Note the parameters control the two aspects of the curve primarily and not completely because the ends of the curves are fixed at 0 and 1 ("pinching").

This is not the only probability distortion function that could have been used. An alternative proposed by Prelec (1998) is $w(pFrac) = exp(-\delta(-log(pFrac))^\gamma)$ which is very similar in shape to the previous one. This one has the key property of "compound invariance" and only studies specifically designed to pit the two functions each other can discriminate them.

While these two models with two parameters each are often indistinguishable models with only one parameter for the probability distortion function is often a worse fit.

The expected value of each lottery is computed by multiplying the probability of winning with the reward amount.

$$EV_{i, t} = p_{i, t} V{i_t}$$
The Q-value of each fractal is adjusted in each trial by a reward prediction error weighted by a learning rate ($\alpha$).

$$QV_{i,t} = QV_{i, t-1} + \alpha(R_{i, t-1}- QV_{i, t-1})$$
# Model fit

```{r}
source(paste0(helpers_path, 'fit_twoValSystemsWithRL.R'))
# Rename objects 
par_ests_nh = par_ests
fit_nh = fit
rm(par_ests, fit)
source(paste0(helpers_path, 'fit_twoValSystemsWithRL_hierarchical.R'))
```

## Log likelihood distributions

Distribution of likelihood across iterations for each subject. Hierarchical fits have higher likelihoods and are more peakier, which would help with distinguishing an MLE estimate if desired.

**Focusing on hierarchical fits only below.**

```{r}
par_ests %>%
  filter(par == "alpha") %>%
  mutate(fit_type = "hierarchical") %>% 
  rbind(par_ests_nh %>%
          filter(par == "alpha") %>%
          mutate(fit_type = "non-hierarchical"))%>%
  ggplot(aes(logLik, fill=fit_type)) +
  geom_histogram(alpha=.5, bins=30, position="identity")+
  facet_wrap(~subnum, scales="free_x")+
  xlab("Log Likelihood")+
  ylab("")+
  ggtitle("Distribution of log likelihoods across the samples for each subject")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())+
  scale_fill_manual(values=c(cbbPalette[1], cbbPalette[2]))
```

```{r}
rm(par_ests_nh, fit_nh)
```

## Parameter point estimates

### Group parameters

```{r}
g_par_ests %>%
  mutate(type='posterior') %>%
  rbind(data.frame(g_alpha = rbeta(16000,1,1),
                   g_gamma = rgamma(16000,1,5),
                   g_delta = rgamma(16000,1,5),
                   g_beta = rgamma(16000,1,2)) %>%
          gather(key, value) %>%
          mutate(type="prior")) %>%
  mutate(type=factor(type,levels=c("prior","posterior"))) %>%
  ggplot(aes(value, fill=type))+
  geom_histogram(bins=30, alpha=.5, position="identity")+
  facet_wrap(~key, scales='free')+
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        panel.grid = element_blank())+
  scale_fill_manual(values = c(cbbPalette[1], cbbPalette[2]))+
  xlab("")+
  ylab("")
```

### Individual parameters

How do the ML and posterior medians differ? 

Most pronounced differences are on $\beta$.

**Note: posterior median estimates are from different iterations/samples whereas the estimates that have the highest likelihood are from the same sample.**

```{r}
tmp1 = par_ests %>%
  group_by(subnum, par) %>%
  filter(logLik == max(logLik))

tmp2 = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = median(value), .groups='keep')

tmp = tmp2 %>%
  left_join(tmp1, by=c("subnum", "par")) 

tmp %>%
  ggplot(aes(est, value))+
  geom_point()+
  geom_abline(slope=1, intercept = 0, linetype="dashed")+
  facet_wrap_equal(~par, scales='free')+
  xlab("Posterior median")+
  ylab("Maximum likelihood")
```

Where does the MLE fall on the posteriors of each parameter? 

```{r fig.height=8, fig.width=4}
par_ests %>%
  ggplot(aes(value))+
  geom_histogram(alpha=.5, bins = 30)+
  facet_grid(subnum~par, scale="free")+
  geom_vline(aes(xintercept = value), tmp1, color=cbbPalette[5])+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        strip.text.x = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("")
```

How far are the likelihoods of the median estimates from the maximum likelihood?

```{r}
tmp3 = par_ests %>%
  group_by(subnum, par) %>%
  mutate(est = median(value), 
         diff_from_med = abs(value - est)) %>%
  filter(diff_from_med == min(diff_from_med)) %>%
  filter(logLik == max(logLik)) %>%
  select(subnum, par, logLik) %>%
  spread(par, logLik)

par_ests %>%
  filter(par == "alpha") %>%
  ggplot(aes(logLik)) +
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~subnum, scales="free_x")+
  xlab("Log Likelihood")+
  ylab("")+
  ggtitle("Distribution of log likelihoods across the samples for each subject \noverlaid with likelihoods of posterior median parameter estimates")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position="bottom")+
  geom_vline(aes(xintercept = alpha, color="alpha"), tmp3)+
  geom_vline(aes(xintercept = beta, color="beta"), tmp3)+
  geom_vline(aes(xintercept = delta, color="delta"), tmp3)+
  geom_vline(aes(xintercept = gamma, color="gamma"), tmp3)+
    scale_color_manual(name="",values = c(alpha = cbbPalette[1], beta=cbbPalette[2], delta=cbbPalette[3], gamma=cbbPalette[4]))

```

```{r}
rm(tmp, tmp1, tmp2, tmp3)
```

**MLE**
- Point estimates from the same sampling iteration  
- MLE estimates differ most from point estimates for beta and gamma so choosing these as point estimates doesn't yield different data for all parameters.  

**Median of posterior**
- Point estimates from the different sampling iteration  
- Median estimates have likelihoods that fall in the middle (instead of the max) of the   likelihood distributions.

When would we need point estimates?  
- Individual difference analyses  
- Prediction error estimates for imaging  

## Covariance between parameters

Are there any dependencies between the parameters? Looking at correlations between samples from the **same** iteration.

```{r}
tmp = par_ests %>%
  group_by(subnum, par) %>%
  mutate(iter = 1:n()) %>%
  select(-logLik) %>%
  group_by(iter) %>%
  spread(par, value) %>%
  ungroup()%>%
  select(-subnum, -iter) 

round(cor(tmp), 3)
```

```{r}
rm(tmp)
```

# Identifiability analysis

Simulate 25 subjects using the median posterior group parameters as true parameters

```{r}
trueGroupPars = g_par_ests %>%
  group_by(key) %>%
  summarise(median_value = round(median(value), 2)) %>%
  spread(key, median_value)

numSims = 25

set.seed(2349813)

truePars = data.frame(alpha=truncnorm::rtruncnorm(numSims, mean=trueGroupPars$g_alpha, a=0, b=1), 
                      beta=truncnorm::rtruncnorm(numSims, mean=trueGroupPars$g_beta, a=0, b=5), 
                      gamma=truncnorm::rtruncnorm(numSims, mean=trueGroupPars$g_gamma, a=0),  
                      delta=truncnorm::rtruncnorm(numSims, mean=trueGroupPars$g_delta, a=0))

modelName = 'fit_twoValSystemsWithRL_hierarchical'

group_par_names=c("g_alpha","g_gamma", "g_delta", "g_beta")
id_par_ests = identifiability_analysis(truePars, modelName, group_par_names = group_par_names)

rm(modelName)
```

```{r}
id_par_ests$par_ests %>%
filter(par == "alpha") %>%
  ggplot(aes(logLik)) +
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~subnum, scales="free_x")+
  xlab("Log Likelihood")+
  ylab("")+
  ggtitle("Distribution of log likelihoods across the samples for each subject")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank())
```

```{r}
id_par_ests$g_par_ests %>%
  ggplot(aes(value))+
  geom_histogram(alpha=.5, bins = 30)+
  geom_vline(aes(xintercept = value), trueGroupPars %>% gather(key, value), color=cbbPalette[5])+
  facet_wrap(~key, scale="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        strip.text.x = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("")
```

```{r}
id_par_ests$par_ests %>%
  ggplot(aes(value))+
  geom_histogram(alpha=.5, bins = 30)+
  facet_grid(subnum~par, scale="free")+
  geom_vline(aes(xintercept = value), truePars %>% mutate(subnum =1:n()) %>% gather(par, value, -subnum), color=cbbPalette[5])+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        strip.text.x = element_text(size=14),
        axis.text.x = element_text(size=14))+
  xlab("")+
  ylab("")
```

# TO DO: Posterior predictive checks

Sample parameters from posterior
Simulate choice data with sampled parameters
Which features of the data are we interested in comparing these to?

```{r}

```
