---
title: "Experience vs. description based decision-making project: Behavioral manipulation checks"
output: html_notebook
---

# Set up environment and load in data

```{r}
library(tidyverse)
```

```{r}
helpers_path = '~/Dropbox/RangelLab/DescribedVsLearned/helpers/'
```

Read in *clean* behavioral data

```{r}
source(paste0(helpers_path,'clean_behavioral_data.R'))
```

Fit Q-learning model to get parameter estimates

```{r}
source(paste0(helpers_path,'fit_qlearning.R'))
```

# Manipulation checks

## Evidence for "learning" fractal values

As time goes by are they more likely to choose the fractal with the higher reward probability? There is a subtle increase in the probability of choosing the fractal with the higher reward probability.

```{r}
clean_beh_data %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
  ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE)
```

This change in probability of choosing the fractal with the higher reward probability is larger when the reward depends only on fractals.

```{r}
clean_beh_data %>%
  filter(probFractalDraw == 1) %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
  ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE)
```

## Correct interpretation of $\pi$

- When p of fractal is 0 do subjects choose based on the EV difference between lotteries? Does the QV difference matter at all?

- When p of fractal is 1 do subjects choose based on the QV difference between fractals? Does the EV difference matter at all?

```{r}
clean_beh_data %>%
  filter(probFractalDraw == 1 | probFractalDraw == 0) %>%
  mutate(leftQVAdv = leftQValue - rightQValue,
         leftLotteryEV = lotteryValue*lotteryProb,
         rightLotteryEV = referenceValue*referenceProb,
         leftEVAdv = leftLotteryEV - rightLotteryEV) %>%
  select(leftQVAdv, leftEVAdv, choiceLeft, probFractalDraw) %>%
  gather(key, value, -choiceLeft, -probFractalDraw) %>%  
  mutate(key = ifelse(key == "leftEVAdv", "EV_left - EV_right", "QV_left - QV_right"),
         probFractalDraw = ifelse(probFractalDraw == 0, "p(Fractal)=0", "p(Fractal)=1"))%>%
  ggplot(aes(value, choiceLeft))+
  geom_jitter(width=0.03, height=0.08, alpha = 0.05)+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE)+
  facet_grid(probFractalDraw~key)+
  xlab("")+
  ylab("p(Left)")
```

- Is there a lottery or fractal bias?

```{r}

```