---
title: "Experience vs. description based decision-making project: Behavioral manipulation checks"
output: html_notebook
---

# Set up environment and load in data

```{r}
library(tidyverse)
```

```{r}
library(gridExtra)
```

```{r}
helpers_path = '~/Documents/RangelLab/DescribedVsLearned/helpers/'
```

Read in *clean* behavioral data

```{r}
source(paste0(helpers_path,'clean_behavioral_data.R'))
```

Fit Q-learning model to get parameter estimates

```{r}
source(paste0(helpers_path,'fit_qlearning.R'))
```

# Manipulation checks

## Evidence for "learning" fractal values

As time goes by are subjects more likely to choose the fractal with the higher reward probability? There is a subtle increase in the probability of choosing the fractal with the higher reward probability. This change in probability of choosing the fractal with the higher reward probability is larger when the reward depends only on fractals (except for the last session, which bizarrely has the opposite pattern).

```{r}
p1 = clean_beh_data %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="All trials", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))

p2 = clean_beh_data %>%
  filter(probFractalDraw == 1) %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="p(Fractal)=1", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))

grid.arrange(p1, p2, nrow=1, ncol=2)
```

```{r}
rm(p1, p2)
```

**ADD Bayesian multilevel model and check the significance of slopes**

```{r}

```

## Correct interpretation of $\pi$

- When p of fractal is 0 do subjects choose based on the EV difference between lotteries? Does the QV difference matter at all?

- When p of fractal is 1 do subjects choose based on the QV difference between fractals? Does the EV difference matter at all?

```{r}
clean_beh_data %>%
  filter(probFractalDraw == 1 | probFractalDraw == 0) %>%
  mutate(leftQVAdv = leftQValue - rightQValue,
         leftLotteryEV = lotteryValue*lotteryProb,
         rightLotteryEV = referenceValue*referenceProb,
         leftEVAdv = leftLotteryEV - rightLotteryEV) %>%
  select(leftQVAdv, leftEVAdv, choiceLeft, probFractalDraw) %>%
  gather(key, value, -choiceLeft, -probFractalDraw) %>%  
  mutate(key = ifelse(key == "leftEVAdv", "EV_left - EV_right", "QV_left - QV_right"),
         probFractalDraw = ifelse(probFractalDraw == 0, "p(Fractal)=0", "p(Fractal)=1"))%>%
  ggplot(aes(value, choiceLeft))+
  geom_jitter(width=0.03, height=0.08, alpha = 0.05)+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE)+
  facet_grid(probFractalDraw~key)+
  xlab("")+
  ylab("p(Left)")
```

**ADD Bayesian multilevel model and check the significance of slopes**

```{r}

```

# Lottery bias

When the better lottery and the better fractal (based on the learned Q value) suggest different options do subjects choose more frequently based on the lottery or their fractal Q Value? Yes, there is a general tendency towards choosing the option with the better lottery even when the trial reward depends less on the lottery and more on the fractal (p(Fractal) >=.5). Only when the outcome depend entirely on the fractal are people more likely to choose the option with the better fractal but even then there is a non-negligible portion of choices determined by the lottery EV. 

```{r}
clean_beh_data %>%
  mutate(leftLotteryEV = lotteryValue*lotteryProb,
         rightLotteryEV = referenceValue*referenceProb,
         leftLotteryBetter = leftLotteryEV>rightLotteryEV,
         choseBetterLottery = ifelse(leftLotteryBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftLotteryBetter & choiceLeft == 0, 1, 0)),
         leftFractalBetter = leftQValue>rightQValue,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
  filter(choseBetterFractal != choseBetterLottery) %>%
  group_by(probFractalDraw, subnum) %>%
  summarise(choseBetterLottery = mean(choseBetterLottery),
            choseBetterFractal = mean(choseBetterFractal),
            .groups='keep') %>%
  gather(key, value, -probFractalDraw, -subnum) %>%
  ggplot(aes(as.factor(probFractalDraw), value, color=key))+
  geom_boxplot()+
 labs(x="p(Fractal)",y="Proportion of choices",color="", title="Lottery bias in conflict trials")

```

**ADD statistical test to check if the proportion of lottery based choices are higher than 50% for all levels of $\pi$**

```{r}

```

