---
title: "Experience vs. description based decision-making project: RL model fits onto behavioral data"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Set up environment and load in data

```{r}
library(tidyverse)
library(gridExtra)
library(rstan)
library(brms)
library(GGally)
library(here)
```

```{r}
helpers_path = here('helpers/')
```

# Read in *clean* behavioral data

```{r}
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'extract_var_for_stan.R'))
source(paste0(helpers_path, 'get_qvals.R'))
```

Set theme for plots

```{r}
theme_set(theme_bw())
```

# Evidence for "learning" fractal values

Is there evidence if "learning" to justify the fitting of an RL model?

As time goes by are subjects more likely to choose the fractal with the higher reward probability? There is a subtle increase in the probability of choosing the fractal with the higher reward probability. This change in probability of choosing the fractal with the higher reward probability is larger when the reward depends only on fractals (except for the last session, which bizarrely has the opposite pattern).

```{r}
tmp = clean_beh_data %>%
  mutate(leftFractalBetter = fractalLeftProb>fractalRightProb,
         choseBetterFractal = ifelse(leftFractalBetter & choiceLeft == 1, 1, 
                                     ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0)))
p1 = tmp %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  # ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="All trials", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))+
  scale_color_manual(values=cbbPalette)+
  theme(legend.position="bottom")

p2 = tmp %>%
  filter(probFractalDraw>.5) %>%
  ggplot(aes(trialNum, choseBetterFractal, col=as.factor(session)))+
  # ggplot(aes(trialNum, choseBetterFractal))+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
  labs(title="p(Fractal)>.5", x="Trial Number", y="p(Chose better fractal)", color="Session")+
  coord_cartesian(ylim=c(0.4,.8))+
  scale_color_manual(values=cbbPalette)+
  theme(legend.position="bottom")

grid.arrange(p1, p2, nrow=1, ncol=2)
```

```{r}
rm(p1, p2)
```

Bayesian multilevel model checking if the slopes in the above figure are different than 0. 

When looking at all trials (left figure) the overall slope of all sessions is not different than 0 (not shown below). When including an interaction term with session number then there is a very small but non-zero increase in the probability of choosing the better fractal (i.e. learning) in sessions 1 and 3 but not in the other sessions.

```{r}
# The default prior for population parameters is an improper flat prior over the reals
m = brm(choseBetterFractal ~ trialNum*as.factor(session) + (1|subnum),
        data=tmp, family=bernoulli(link="logit"))
```

```{r}
summary(m)
```

Filtering only trials where probability of a fractal draw is >.5, i.e. trials where learning about the fractal values would be more consequential we find a slightly stronger increase in the probability of choosing the better fractal later in the session in sessions 1 through 3 though still no effect for the other sessions.

```{r}
m2= brm(choseBetterFractal ~ trialNum*as.factor(session) + (1|subnum),
        data=tmp %>% filter(probFractalDraw>.5), family=bernoulli(link="logit"))
```

```{r}
summary(m2)
```

```{r}
rm(m, m2, tmp)
```

# Define two systems model

On each trial is subjects process not only the two fractals but also their relevance to the trial's reward, as well as, the lottery information. So to describe the choice process in this task, including accounting for learning about fractals across trials, the computational model must include all of these factors.

In this model the probability of choosing the option on the left is described as a softmax temperature that depends on the value difference between the left and right pairs. The free parameter $\beta$ controls the extent to which the choice depends on this value difference instead of chance.

$$p(choice = left) = \frac{1}{1+e^{-\beta(V_{left} - V_{right})}}$$
The value of each pair is defined as a weighted average of both of its components. The two components of each pair, the lottery and the fractal is weighted proportional to their relevance for that trial.

$$V_i = (1-w(pFrac))EV_i + w(pFrac)QV_i, \:i \in \{left, right\}$$
Given the large amount of evidence from behavioral economics suggesting that people do not perceive probabilities linearly but distort them the probability weighting function $\w$ is conceived of as a non-linear function. As described in Gonzalez and Wu (1999) we parameterized it as

$$w(pFrac) = \frac{\delta*pFrac^{\gamma}}{\delta*pFrac^{\gamma}+(1- pFrac)^{\gamma}}$$
where $\delta$ (primarily) controls the elevation/intercept to capture attractiveness of the outcome weighted by the distorted probability and $\gamma$ (primarily) controls curvature to capture the discriminability of distorted probabilities from each other. They call this shape "linear in log odds." Note the parameters control the two aspects of the curve primarily and not completely because the ends of the curves are fixed at 0 and 1 ("pinching").

This is not the only probability distortion function that could have been used. An alternative proposed by Prelec (1998) is

$$w(pFrac) = exp(-\delta(-log(pFrac))^\gamma)$$
which is very similar in shape to the previous one. This one has the key property of "compound invariance" and only studies specifically designed to pit the two functions each other can discriminate them.

While these two models with two parameters each are often indistinguishable models with only one parameter for the probability distortion function is often a worse fit.

The expected value of each lottery is computed by multiplying the probability of winning with the reward amount.

$$EV_{i, t} = p_{i, t} V{i_t}$$
The Q-value of each fractal is adjusted in each trial by a reward prediction error weighted by a learning rate ($\alpha$).

$$QV_{i,t} = QV_{i, t-1} + \alpha(R_{i, t-1}- QV_{i, t-1})$$
## Fit Q learning + two value system simultaneously

Organize data

```{r}
num_subjs = length(unique(clean_beh_data$subnum))

num_trials = clean_beh_data %>%
  count(subnum) %>%
  select(n)
num_trials = num_trials$n

#subjects in rows, trials in columns
choices = extract_var_for_stan(clean_beh_data, choiceLeft)

clean_beh_data = clean_beh_data %>%
  mutate(leftLotteryEV = lotteryValue*lotteryProb,
         rightLotteryEV = referenceValue*referenceProb)

ev_left = extract_var_for_stan(clean_beh_data, leftLotteryEV)

ev_right = extract_var_for_stan(clean_beh_data, rightLotteryEV)

fractal_outcomes_left = extract_var_for_stan(clean_beh_data, leftFractalReward)

fractal_outcomes_right = extract_var_for_stan(clean_beh_data, rightFractalReward)

trial_pFrac = extract_var_for_stan(clean_beh_data, probFractalDraw)

m_data=list(num_subjs = num_subjs,
            num_trials = num_trials,
            choices = choices,
            ev_left = ev_left,
            ev_right = ev_right,
            fractal_outcomes_left = fractal_outcomes_left,
            fractal_outcomes_right = fractal_outcomes_right,
            trial_pFrac = trial_pFrac)

rm(num_subjs, num_trials, choices, ev_left, ev_right, fractal_outcomes_left, fractal_outcomes_right, trial_pFrac)
```

## Fit model for all subjects

```{r}
if(file.exists(paste0(helpers_path, 'stanModels/fit_twoValSystemsWithRL.RDS'))){
  fit = readRDS(paste0(helpers_path, 'stanModels/fit_twoValSystemsWithRL.RDS'))
} else {
  m = stan_model(paste0(helpers_path, 'stanModels/fit_twoValSystemsWithRL.stan'))
  fit = sampling(m, data=m_data)
  saveRDS(fit, paste0(helpers_path, 'stanModels/fit_twoValSystemsWithRL.RDS'))
  rm(m, m_data)}
```

## Organize model output

```{r}
# Extract parameters from fit object
par_ests = data.frame(extract(fit, c("alpha","gamma", "delta", "beta")))  %>%
  gather(key, value) %>%
  separate(key, c('par', 'subj'), sep='\\.')

# Add correct subject identifiers
par_ests = data.frame(subnum = unique(clean_beh_data$subnum)) %>%
  mutate(subj = as.character(1:n())) %>%
  right_join(par_ests, by='subj') %>%
  select(-subj)
```

# Examine two value systems parameters

**ARE MEDIAN ESTIMATES THE SAME AS THOSE THAT YIELD THE HIGHEST LIKELIHOOD OF THE SAMPLED VALUES?**

Distributions of the recovered (median) parameters

```{r}
par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = median(value), .groups='keep') %>%
  ggplot(aes(est))+
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~par, scales='free_x')+
  xlab("Median estimates for all subjects")
```

Are there any dependencies between the parameters? gamma is correlated with both beta and delta.

```{r}
par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = median(value), .groups='keep') %>%
  ungroup() %>%
  spread(par, est) %>%
  select(-subnum) %>%
  ggpairs(progress = FALSE)
```

How do the median estimates suggest the probability of a fractal draw is distorted for each subject?

Using Gonzalez and Wu's (1999) terminology the fact that almost all subjects probability weighting functions are below the 45-degree line (i.e. objective probability) regardless of the inverse-S shape is not about diminishing sensitivy/discriminability (slope) but about **attractiveness** (intercept, elevation). The fractal is almost always less attractive to subjects than it really should be given its probability in determining their reward.

Unlike the simple case where the probability weighting function represents the probability of a reward, however, in this case the probability of a reward is the joint probability of p(Fractal)*p(chosen Fractal's reward)

```{r}
tmp = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = median(value), .groups='keep') %>%
  filter(par != "beta" & par != "alpha") %>%
  spread(par, est)

tmp = do.call("rbind", replicate(11, tmp, simplify = FALSE)) %>%
  arrange(subnum) %>%
  ungroup() %>%
  mutate(pFrac = rep(seq(0, 1, .1), 25), 
         wpFrac = (delta*pFrac^gamma)/(delta*pFrac^gamma + (1-pFrac)^gamma)) 

tmp %>%
  mutate(delta_gt_1 = ifelse(delta>=1, 1, 0),
         gamma_gt_1 = ifelse(gamma>=1,"gamma >= 1", "gamma < 0")) %>%
  ggplot(aes(pFrac, wpFrac, group=subnum))+
  geom_line(aes(col = as.factor(gamma_gt_1)))+
  geom_abline(slope=1, intercept=0, linetype="dashed")+
  labs(x="p(Fractal)", y="w(pFractal)", title="Distortion of p(Fractal)", color = element_blank())
```
How does the distortion of the fractal draw probability change for different values of delta and gamma? Where do the subjects' median estimates fall on this spectrum?

Facets - values of pFrac (true prob of Fractal)
Blue w(pFrac)>pFrac - overweighting prob fractal
Red pFrac>w(pFrac) - underweighting prob fractal

```{r}
tmp = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = median(value), .groups='keep') %>%
  spread(par, est)

expand.grid(rep(list(seq(0,1.5,.1)), 3)) %>%
  rename(delta=Var1, gamma=Var2, pFrac=Var3)%>%
  mutate(wpFrac = (delta*(pFrac^gamma)) / ((delta*(pFrac^gamma) + ((1-pFrac)^gamma))), 
         distortion = pFrac-wpFrac) %>%
  filter(pFrac > 0 & pFrac < 1) %>%
  mutate(pFrac = paste0("p(Fractal) = ", pFrac)) %>%
  ggplot2::ggplot(aes(as.factor(delta), as.factor(gamma)))+
  geom_raster(aes(fill=distortion))+
  facet_wrap(~as.factor(pFrac))+
  labs(x="\U03B4", y="\U03B3", 
       fill="Overestimation -> underestimation", 
       title="Distortion of p(Fractal)")+
  scale_fill_gradient2(low = scales::muted("blue"), high=scales::muted("red"))+
  theme(axis.ticks = element_blank(), axis.text.x = element_text(angle=90), legend.position="bottom")+
  scale_y_discrete(breaks=seq(0, 1.5, .3))+
  annotate("point", x = 10*tmp$delta, y=10*tmp$gamma)
```
