---
title: "Experience vs. description based decision-making project: Post imaging analyses checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
```

```{r include=FALSE}
helpers_path = here('helpers/')
source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
```

Add estimated model parameters and inferred bundle values using those parameters.

```{r}
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests)
```

## Correlation between reggressors

Is there a correlation between valChosen and valUnchosen? Yes.

```{r}
clean_beh_data = clean_beh_data %>%
  mutate(valChosen = ifelse(choiceLeft, leftBundleVal, rightBundleVal),
         valUnchosen = ifelse(choiceLeft == 0, leftBundleVal, rightBundleVal),
         wpFracBins = as.factor(round(wpFrac,1)),
         leftQVAdvWeighted = leftQVAdv*wpFrac,
         leftEVAdvWeighted = leftEVAdv*(1-wpFrac)) 
```

The values of the bundles also depend on the distorted probabilities. The more a subject thinks the reward depends on the fractal (lighter colors) the lowers both bundles' value.

```{r}
with(clean_beh_data, cor(valChosen, valUnchosen))
clean_beh_data %>%
  ggplot(aes(valChosen, valUnchosen, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

Why is there a correlation between valChosen and valUnchosen?  

Is the correlation there for the components that go into valChosen and valUnchosen?  

Looking at the bundle values regardless of what is chosen we see the same pattern as above where the bundles' values are higher overall the less the reward is thought to rely on the fractals.

```{r}
with(clean_beh_data, cor(leftBundleVal, rightBundleVal))
clean_beh_data %>%
  # filter(wpFrac == 1) %>%
  ggplot(aes(leftBundleVal, rightBundleVal, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

```{r}
with(clean_beh_data, cor(leftQValue, rightQValue))
clean_beh_data %>%
    # filter(wpFrac == 1) %>%
  ggplot(aes(leftQValue, rightQValue, color=wpFrac))+
  geom_point()+
  facet_grid(~as.factor(leftLotteryEV))+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

```{r}
with(clean_beh_data, cor(leftQValue, rightQValue))
clean_beh_data %>%
    # filter(wpFrac == 1) %>%
  ggplot(aes(leftQValue, rightQValue))+
  geom_point()+
  facet_grid(~wpFracBins)+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```


```{r}
with(clean_beh_data, cor(leftQValue, leftBundleVal))
clean_beh_data %>%
  ggplot(aes(leftQValue, leftBundleVal, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

```{r}
with(clean_beh_data, cor(leftLotteryEV, leftBundleVal))
clean_beh_data %>%
  ggplot(aes(leftLotteryEV, leftBundleVal, col=wpFrac))+
  geom_jitter(width=.01)+
  # geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

```{r}
with(clean_beh_data, cor(leftLotteryEV, leftQValue))
clean_beh_data %>%
  ggplot(aes(leftLotteryEV, leftQValue, col=wpFrac))+
  geom_jitter(width=.01)+
  # geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")
```

```{r}
clean_beh_data %>%
  filter(reward < 5) %>%
  ggplot(aes(reward, valChosen, color=rpe))+
  geom_jitter(height=0.1)
```

## Logit model comparison

Is a model where choice depends only on the lottery value difference explain data better than a model that doesn't include the fractal value difference?

```{r}
m1 = brm(choiceLeft ~ leftQVAdv + leftEVAdv + probFractalDraw + leftQVAdv:probFractalDraw + leftEVAdv:probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m1 = add_criterion(m1, "waic")

m2 = brm(choiceLeft ~ leftEVAdv * probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m2 = add_criterion(m2, "waic")
```

```{r}
m3 = brm(choiceLeft ~ leftbundleValAdv * probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m3 = add_criterion(m3, "waic")
```

```{r}
m1a = brm(choiceLeft ~ leftQVAdvWeighted + leftEVAdvWeighted + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m1a = add_criterion(m1a, "waic")
```

```{r}
loo_compare(m1, m1a, m2, m3, criterion = "waic")
```

```{r}
m3$criteria
```

```{r}
m1a$criteria
```

```{r}
m3
```

```{r}
m1a
```

# Where is QV in the brain?

Are we not finding a neural correlate for fractal value regressors because they are more variable across subjects?

```{r}
source(paste0(helpers_path,'logit_choiceLeft_randomEffects_conflictCollapsed.R'))
source(paste0(helpers_path,'logit_choiceLeft_randomEffects_conflictCollapsed_pFracWeightedValDiff.R'))
```

```{r}
out_choiceLeft_re_pfw %>%
  filter(var != "intercept") %>%
  pivot_wider(values_from = c("Estimate", "Q2.5", "Q97.5"),
              id_cols = c(subnum, probFractalDraw),
              names_from = var) %>%
  ggplot(aes(Estimate_qv_slopes, Estimate_ev_slopes))+
  geom_point()+
  geom_errorbar(aes(ymin=Q2.5_ev_slopes, ymax=Q97.5_ev_slopes), alpha=.5, color=cbbPalette[2])+
  geom_errorbarh(aes(xmin=Q2.5_qv_slopes, xmax=Q97.5_qv_slopes), alpha=.5, color=cbbPalette[1])+
  facet_wrap(~probFractalDraw)+
  labs(x="Logit slope for QV(left)-QV(right)", y="Logit slope for EV(left)-EV(right)")+
  theme_bw()
```

```{r}
out_choiceLeft_re %>%
  filter(var != "intercept") %>%
  pivot_wider(values_from = c("Estimate", "Q2.5", "Q97.5"),
              id_cols = c(subnum, probFractalDraw),
              names_from = var) %>%
  ggplot(aes(Estimate_qv_slopes, Estimate_ev_slopes))+
  geom_point()+
  geom_errorbar(aes(ymin=Q2.5_ev_slopes, ymax=Q97.5_ev_slopes), alpha=.5, color=cbbPalette[2])+
  geom_errorbarh(aes(xmin=Q2.5_qv_slopes, xmax=Q97.5_qv_slopes), alpha=.5, color=cbbPalette[1])+
  facet_wrap(~probFractalDraw)+
  labs(x="Logit slope for QV(left)-QV(right)", y="Logit slope for EV(left)-EV(right)")+
  theme_bw()
```

Compare width of errorbars more directly?
You're trying to capture where there is more individual variability.
Not where an individual's estimates might be more variable.
So what you should look at is the variance of estimates for each slope at each pfractal level.

```{r}
out_choiceLeft_re_pfw %>%
  filter(var != "intercept") %>%
  ggplot(aes(as.factor(probFractalDraw), Estimate, color=var))+
  geom_boxplot()
```

```{r}
out_choiceLeft_re %>%
  filter(var != "intercept") %>%
  ggplot(aes(as.factor(probFractalDraw), Estimate, color=var))+
  geom_boxplot()
```