---
title: "Experience vs. description based decision-making project: Post imaging analyses checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
```

```{r include=FALSE}
helpers_path = here('helpers/')

source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical_rpeWhenFractalRewarded.R'))
fit_rpeWhenFractalRewarded = fit
g_par_ests_rpeWhenFractalRewarded = g_par_ests
par_ests_rpeWhenFractalRewarded = par_ests

source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical_rpeChosenBundleFractal.R'))
fit_rpeChosenBundleFractal = fit
g_par_ests_rpeChosenBundleFractal = g_par_ests
par_ests_rpeChosenBundleFractal = par_ests

source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
```

```{r}
clean_beh_data_original = add_inferred_pars(clean_beh_data, par_ests, model_name="original")
clean_beh_data_rpeChosenBundleFractal = add_inferred_pars(clean_beh_data, par_ests_rpeChosenBundleFractal, model_name="rpeChosenBundleFractal")
clean_beh_data_rpeWhenFractalRewarded = add_inferred_pars(clean_beh_data, par_ests_rpeWhenFractalRewarded, model_name="rpeWhenFractalRewarded")
```

# Model comparison of different RPE representations

## Behavioral fit comparison

There are individual differences in the best fitting model.

```{r}
par_ests %>%
  mutate(model = "original") %>%
  rbind(par_ests_rpeChosenBundleFractal %>% mutate(model = "rpeChosenBundleFractal")) %>%
  rbind(par_ests_rpeWhenFractalRewarded %>% mutate(model = "rpeWhenFractalRewarded")) %>%
  ggplot(aes(logLik, fill=model))+
  geom_histogram(bins=30, position="identity", alpha=0.5)+
  facet_wrap(~subnum, scales='free')+
  scale_fill_manual(values=cbbPalette[1:3])+
  theme(legend.position = "bottom")+
  labs(x="",y="", fill="", title = "Distribution of log likelihoods")
```

```{r}
best_model_for_subj = par_ests %>%
  mutate(model = "original") %>%
  rbind(par_ests_rpeChosenBundleFractal %>% mutate(model = "rpeChosenBundleFractal")) %>%
  rbind(par_ests_rpeWhenFractalRewarded %>% mutate(model = "rpeWhenFractalRewarded")) %>%
  group_by(model, subnum) %>%
  summarise(aveLL = mean(logLik),.groups='keep') %>%
  ungroup() %>%
  group_by(subnum) %>%
  mutate(minaveLL = min(aveLL)) %>%
  spread(model, aveLL) %>%
  mutate(winningModel = ifelse(minaveLL == original, "original", ifelse(minaveLL == rpeChosenBundleFractal, "rpeChosenBundleFractal", "rpeWhenFractalRewarded"))) %>%
  select(-minaveLL) 

best_model_for_subj %>%
  ungroup()%>%
  count(winningModel)
```

## How are the parameter estimates related between the three models 

```{r}
par_ests %>%
  mutate(model = "original") %>%
  rbind(par_ests_rpeChosenBundleFractal %>% mutate(model = "rpeChosenBundleFractal")) %>%
  rbind(par_ests_rpeWhenFractalRewarded %>% mutate(model = "rpeWhenFractalRewarded")) %>%
  filter(par == "alpha") %>%
  ggplot(aes(value, fill=model)) +
  geom_histogram(bins=30, position="identity", alpha=0.5)+
  facet_wrap(~subnum, scales='free')+
  scale_fill_manual(values=cbbPalette[1:3])+
  theme(legend.position = "bottom")+
  labs(x="",y="", fill="", title = "Distribution of learning rates")
```

Plotting mean posterior estimates for each subject in the following two plots.

Models where the RPE is not updated on each trial tend to estimate slightly higher learning rates.

```{r}
clean_beh_data_original %>%
  mutate(model = "original") %>%
  select(subnum, model, alpha) %>%
  rbind(clean_beh_data_rpeChosenBundleFractal %>%
          mutate(model = "rpeChosenBundleFractal") %>%
          select(subnum, model, alpha)) %>%
  rbind(clean_beh_data_rpeWhenFractalRewarded %>%
          mutate(model = "rpeWhenFractalRewarded") %>%
          select(subnum, model, alpha)) %>%
  distinct() %>%
  gather(par, est, -subnum, -model) %>%
  spread(model, est) %>%
  gather(model, value, -subnum, -par, -original) %>%
  ggplot(aes(original, value)) +
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  facet_grid(model ~ par, scales='free')+
  theme_bw()
  
```

```{r}
clean_beh_data_original %>%
  mutate(model = "original") %>%
  select(subnum, model, beta, delta, gamma) %>%
  rbind(clean_beh_data_rpeChosenBundleFractal %>%
          mutate(model = "rpeChosenBundleFractal") %>%
          select(subnum, model, beta, delta, gamma)) %>%
  rbind(clean_beh_data_rpeWhenFractalRewarded %>%
          mutate(model = "rpeWhenFractalRewarded") %>%
          select(subnum, model, beta, delta, gamma)) %>%
  distinct() %>%
  gather(par, est, -subnum, -model) %>%
  spread(model, est) %>%
  gather(model, value, -subnum, -par, -original) %>%
  ggplot(aes(original, value)) +
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  facet_grid(model ~ par, scales='free')+
  theme_bw()
  
```

## Correlation of RPE regressors for each model

Depicting three different subjects in the columns.

```{r}
clean_beh_data_original %>%
  mutate(model = "original") %>%
  group_by(subnum) %>%
  mutate(trialNumCont = 1:n()) %>%
  select(subnum, model, trialNumCont, rpeLeftRightSum) %>%
  rbind(clean_beh_data_rpeChosenBundleFractal %>%
          mutate(model = "rpeChosenBundleFractal") %>%
          group_by(subnum) %>%
          mutate(trialNumCont = 1:n()) %>%
          select(subnum, model, trialNumCont, rpeLeftRightSum)) %>%
  rbind(clean_beh_data_rpeWhenFractalRewarded %>%
          mutate(model = "rpeWhenFractalRewarded")%>%
          group_by(subnum) %>%
          mutate(trialNumCont = 1:n()) %>%
          select(subnum, model, trialNumCont, rpeLeftRightSum)) %>%
  spread(model, rpeLeftRightSum) %>%
  gather(model, value, -subnum, -trialNumCont, -original) %>%
  filter(subnum %in% c("02", "04", "08")) %>%
  ggplot(aes(original, value)) +
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")+
  facet_grid(model~subnum, scales='free')+
  theme_bw()
  
```

## What would a reliability of value signal look like?

Get behavioral data with the parameter estimates and **RPE's from the best fitting model for each subject**.

```{r}
source(paste0(helpers_path, 'save_imaging_events_wBestRpe.R'))
```

What do the RPEs look like? Is there enough variance in them if you wanted to use their absolute value as a "reliability" signal?

```{r}
clean_beh_data %>%
  select(leftFractalRpe, rightFractalRpe) %>%
  gather(key, value) %>%
  ggplot(aes(value))+
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~key)
```

```{r}
clean_beh_data %>%
  select(leftFractalRpe, rightFractalRpe) %>%
  gather(key, value) %>%
  ggplot(aes(abs(value)))+
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~key)
```
Are absolute RPE distributions similar for both fractals for all subjects or do some subjects learn more/less about one fractal than the other?

```{r}
clean_beh_data %>%
  select(leftFractalRpe, rightFractalRpe, subnum) %>%
  gather(key, value, -subnum) %>%
  filter(abs(value)>0) %>%
  ggplot(aes(abs(value), fill=key))+
  geom_histogram(alpha=.5, bins=30, position="identity")+
  facet_wrap(~subnum)+
  theme(legend.position ="bottom")+
  scale_fill_manual(values=c(cbbPalette[1:2]))+
  labs(fill="")
```
Subjects 3, 5, 8, 10, 15, 27 might be learning differently about the two fractals.

```{r}
clean_beh_data %>%
  select(leftFractalRpe, rightFractalRpe, subnum) %>%
  gather(key, value, -subnum) %>%
  mutate(value=abs(value)) %>% #reliability
  filter(value>0) %>%
  group_by(subnum, key) %>%
  summarise(.groups = 'keep', 
            sem_val = sem(value), 
            mean_val = mean(value)) %>%
  ggplot(aes(subnum, mean_val, fill=key))+
  geom_bar(stat="identity",position=position_dodge(width = .9), alpha=.5)+
  geom_errorbar(aes(ymin=mean_val-sem_val, ymax=mean_val+sem_val), position=position_dodge(width = .9), width=.25)+
  theme(legend.position = "bottom")+
  scale_fill_manual(values=c(cbbPalette[1:2]))+
  labs(fill="", y="")
```

## Response times vs prob fractal

```{r}
clean_beh_data %>%
  mutate(log_rt = log(reactionTime), 
         probFractalDraw = as.factor(probFractalDraw)) %>%
  group_by(subnum, probFractalDraw) %>%
  summarise(mean_log_rt = mean(log_rt), .groups='keep') %>%
  ungroup()%>%
  group_by(probFractalDraw)%>%
  summarise(sem_log_rt = sem(mean_log_rt),
            mean_log_rt = mean(mean_log_rt)) %>%
  ggplot(aes(probFractalDraw, mean_log_rt))+
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=  mean_log_rt - sem_log_rt, ymax=mean_log_rt + sem_log_rt), width=.2)
```
