---
title: "Experience vs. description based decision-making project: Post imaging analyses checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
```

```{r include=FALSE}
helpers_path = here('helpers/')
source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
```

Add estimated model parameters and inferred bundle values using those parameters.

```{r}
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests)

clean_beh_data = clean_beh_data %>%
  mutate(wpFracBins = as.factor(round(wpFrac,1)),
         leftQVAdvWeighted = leftQVAdv*wpFrac,
         leftEVAdvWeighted = leftEVAdv*(1-wpFrac)) 
```

# Is RPE sum a good regressor to capture learning? 

For the off diagonal trials in the plot below rpe sum would be small but is there less learning in those trials? Probably not.
    
```{r}
clean_beh_data %>%
  ggplot(aes(leftFractalRpe, rightFractalRpe, color=rpeLeftRightSum))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed")
```
# Model comparison of different RPE representations

## Behavioral fit comparison

```{r}

```

## How are the parameter estimates related between the three models 

```{r}

```

## How are `rpeWhenFractalRewarded` and `rpeChosenBundleFractal` related to `rpeLeftRightSum`

```{r}

```

