---
title: "Experience vs. description based decision-making project: Post imaging analyses checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
```

```{r include=FALSE}
helpers_path = here('helpers/')
source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
```

Add estimated model parameters and inferred bundle values using those parameters.

```{r}
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests)

clean_beh_data = clean_beh_data %>%
  mutate(valChosen = ifelse(choiceLeft, leftBundleVal, rightBundleVal),
         valUnchosen = ifelse(choiceLeft == 0, leftBundleVal, rightBundleVal),
         wpFracBins = as.factor(round(wpFrac,1)),
         leftQVAdvWeighted = leftQVAdv*wpFrac,
         leftEVAdvWeighted = leftEVAdv*(1-wpFrac)) 
```

## Correlation between reggressors

### Value

Is there a correlation between valChosen and valUnchosen? Yes.

```{r}
with(clean_beh_data, cor(valChosen, valUnchosen))
```
    
A second thing to note about the correlation between the bundle values is that they also depend on the distorted probabilities. The more a subject thinks the reward depends on the fractal (lighter colors) the lower both bundles' value. 

A third interesting pattern is that choices above the diagonal where the value of the unchosen bundle is higher than the value of the chosen bundle must be trials where subjects chose differently than what the value difference suggested.

Below they are broken down by the five levels of the lottery EV difference. Facet values < 0 are trials where the right/reference lottery is better.

```{r}
clean_beh_data %>%
  ggplot(aes(valChosen, valUnchosen, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed") + 
  facet_grid(.~as.factor(leftEVAdv))+
  theme(legend.position="bottom")
```

What are the two prawns in the graph above? The split is by choice side.

```{r}
clean_beh_data %>%
  ggplot(aes(valChosen, valUnchosen, col=as.factor(choiceLeft)))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed") + 
  facet_grid(.~as.factor(leftEVAdv))+
  theme(legend.position="bottom")+
  labs(color="choiceLeft")+
  scale_color_manual(values=cbbPalette[1:2])
```

Why is there a correlation between valChosen and valUnchosen?  

Looking at the bundle values regardless of what is chosen we see the same pattern as above where the bundles' values are higher overall the less the reward is thought to rely on the fractals.

```{r}
clean_beh_data %>%
  ggplot(aes(leftBundleVal, rightBundleVal, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed") + 
  facet_wrap(~as.factor(leftEVAdv))
```
Is the correlation there for the components that go into valChosen and valUnchosen?  

The five prawns are for the levels of lottery value difference (can confirm by coloring by that).

```{r}
clean_beh_data %>%
  mutate(lab_col = paste0(subnum, ", alpha = ",round(alpha, 3))) %>%
  ggplot(aes(leftBundleVal, rightBundleVal, col=wpFrac))+
  geom_point()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")+
  facet_wrap(~lab_col)
```
How much the value of the bundles correlate with each other is associated with learning. The higher the learning rate the less the values of the bundles correlate with each other.

```{r}
clean_beh_data %>%
  group_by(subnum) %>%
  summarise(val_cor = cor(leftBundleVal, rightBundleVal),
            alpha = unique(alpha)) %>%
  ggplot(aes(alpha, val_cor))+
  geom_point()+
  geom_smooth(method="lm", formula='y~x')
```
The Q values have little to no variance for small learning rates.

```{r}
clean_beh_data %>%
  mutate(lab_col = paste0(subnum, ", alpha = ",round(alpha, 3))) %>%
  ggplot(aes(leftQValue*wpFrac, rightQValue*wpFrac, color=alpha))+
  geom_point()+
  facet_wrap(~lab_col)+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")+
  theme(legend.position = "none")
```
Things to note/explain:
1. Correlation between bundle values
--> Depends on learning rates. No variance in Q values for small learning rates translates to high correlation between bundle values

2. Higher bundle values for lower wpFrac
This is true even for people with high learning rates. So where is it coming from?
Since it is there for everybody it shouldn't depend on the prob distortion parameters beta or gamma either.
When wpFrac = 1 the bundle value depends only on the lottery value
--> Lottery EV's are higher than QV's in general

```{r}
clean_beh_data %>%
  select(leftLotteryEV, leftQValue, rightQValue) %>%
  gather(key, value) %>%
  ggplot(aes(value, fill=key))+
  geom_histogram(position = "identity", alpha = 0.5, bins=30)+
  scale_fill_manual(values=cbbPalette[1:3])+
  labs(fill="")
```
Is this by design? Are true fractal values also lower than the EVs?

```{r}
clean_beh_data %>%
  select(leftLotteryEV, fractalLeftProb, fractalRightProb) %>%
  gather(key, value) %>%
  ggplot(aes(value, fill=key))+
  geom_histogram(position = "identity", alpha = 0.5, bins=30)+
  scale_fill_manual(values=cbbPalette[3:1])+
  labs(fill="")
```

### Reward and rpe

```{r}
clean_beh_data %>%
  filter(reward < 5) %>%
  ggplot(aes(reward, valChosen, color=rpe))+
  geom_jitter(height=0.1)
```

## Logit model comparison: what effects choice?

Is a model where choice depends only on the lottery value difference explain data better than a model that doesn't include the fractal value difference?

```{r}
m1 = brm(choiceLeft ~ leftQVAdv + leftEVAdv + probFractalDraw + leftQVAdv:probFractalDraw + leftEVAdv:probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m1 = add_criterion(m1, "waic")

m2 = brm(choiceLeft ~ leftEVAdv * probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m2 = add_criterion(m2, "waic")
```

```{r}
m3 = brm(choiceLeft ~ leftbundleValAdv * probFractalDraw + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m3 = add_criterion(m3, "waic")
```

```{r}
m1a = brm(choiceLeft ~ leftQVAdvWeighted + leftEVAdvWeighted + (1|subnum),
            data=clean_beh_data, family=bernoulli(link="logit"), silent=2, refresh=0)
m1a = add_criterion(m1a, "waic")
```

```{r}
loo_compare(m1, m1a, m2, m3, criterion = "waic")
```

```{r}
m3$criteria
```

```{r}
m1a$criteria
```

```{r}
m3
```

```{r}
m1a
```



## Where is QV in the brain?

Are we not finding a neural correlate for fractal value regressors because they are more variable across subjects?

```{r}
source(paste0(helpers_path,'logit_choiceLeft_randomEffects_conflictCollapsed.R'))
source(paste0(helpers_path,'logit_choiceLeft_randomEffects_conflictCollapsed_pFracWeightedValDiff.R'))
```

```{r}
out_choiceLeft_re_pfw %>%
  filter(var != "intercept") %>%
  pivot_wider(values_from = c("Estimate", "Q2.5", "Q97.5"),
              id_cols = c(subnum, probFractalDraw),
              names_from = var) %>%
  ggplot(aes(Estimate_qv_slopes, Estimate_ev_slopes))+
  geom_point()+
  geom_errorbar(aes(ymin=Q2.5_ev_slopes, ymax=Q97.5_ev_slopes), alpha=.5, color=cbbPalette[2])+
  geom_errorbarh(aes(xmin=Q2.5_qv_slopes, xmax=Q97.5_qv_slopes), alpha=.5, color=cbbPalette[1])+
  facet_wrap(~probFractalDraw)+
  labs(x="Logit slope for QV(left)-QV(right)", y="Logit slope for EV(left)-EV(right)")+
  theme_bw()
```

```{r}
out_choiceLeft_re %>%
  filter(var != "intercept") %>%
  pivot_wider(values_from = c("Estimate", "Q2.5", "Q97.5"),
              id_cols = c(subnum, probFractalDraw),
              names_from = var) %>%
  ggplot(aes(Estimate_qv_slopes, Estimate_ev_slopes))+
  geom_point()+
  geom_errorbar(aes(ymin=Q2.5_ev_slopes, ymax=Q97.5_ev_slopes), alpha=.5, color=cbbPalette[2])+
  geom_errorbarh(aes(xmin=Q2.5_qv_slopes, xmax=Q97.5_qv_slopes), alpha=.5, color=cbbPalette[1])+
  facet_wrap(~probFractalDraw)+
  labs(x="Logit slope for QV(left)-QV(right)", y="Logit slope for EV(left)-EV(right)")+
  theme_bw()
```

Compare width of errorbars more directly?
You're trying to capture where there is more individual variability.
Not where an individual's estimates might be more variable.
So what you should look at is the variance of estimates for each slope at each pfractal level.

```{r}
out_choiceLeft_re_pfw %>%
  filter(var != "intercept") %>%
  ggplot(aes(as.factor(probFractalDraw), Estimate, color=var))+
  geom_boxplot()
```

```{r}
out_choiceLeft_re %>%
  filter(var != "intercept") %>%
  ggplot(aes(as.factor(probFractalDraw), Estimate, color=var))+
  geom_boxplot()
```