---
title: "Experience vs. description based decision-making project: Adding arbitration to behavioral modeling"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
library(broom)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
helpers_path = here('helpers/')

set.seed(385723)
```

Adding in parameters from the two systems model for all subjects (i.e. not choosing the best fitting one per subject)

```{r}
source(paste0(helpers_path,'fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests, model_name="original")
```

Helper function that loops provided task conditions to generate simulated trials

```{r}
sim_task = function(sub_data, ...){
  kwargs = list(...)
  if (!("nonDecisionTime" %in% kwargs)){
    kwargs$nonDecisionTime = 0
  }
  
  # Create placeholder output df
  out = data.frame(EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, probFractalDraw = NA, choice = NA, reactionTime = NA)
  
  # Loop through all trials of a subjects data (or just all the rows of the input)
  for(i in 1:nrow(sub_data)) {
    
    # Simulate RT and choice for a single trial with given DDM parameters and trial stimulus values
    cur_out = sim_trial(d=kwargs$d, sigma = kwargs$sigma, nonDecisionTime = kwargs$nonDecisionTime,
                        EVLeft=sub_data$leftLotteryEV[i], EVRight = sub_data$rightLotteryEV[i], 
                        QVLeft = sub_data$leftQValue[i], QVRight= sub_data$rightQValue[i] , 
                        probFractalDraw = sub_data$probFractalDraw[i])
    
    # Append the trial to the rest of the output
    out = rbind(out, cur_out)
    
  }
  
  # Drops only first row instead of all NAs to keep trials where iterations timed out and a decision was not made
  out = out[-1,]
  
  return(out)
}
```

Helper function for sanity checks on simulated data

```{r}
sim_sanity_checks = function(sim_data, checks = c(1,2,3,4, 5)){
  #Check 1
  if (1 %in% checks){
    print(paste0("Proportion of time out trials is: ", round(sum(is.na(sim_data$reactionTime))/nrow(sim_data), 3)))
  }
  
  
  # Check 2
  if(2 %in% checks){
    p = sim_data %>%
    drop_na()%>%
    filter(probFractalDraw == 0 | probFractalDraw == 1) %>%
    mutate(choiceLeft =ifelse(choice == "left", 1, ifelse(choice == "right", 0, NA))) %>%
    mutate(EVLeftMinRight = EVLeft - EVRight,
           QVLeftMinRight = QVLeft - QVRight) %>%
    select(-choice, -EVLeft, -EVRight, -QVLeft, -QVRight) %>%
    gather(key, value, -probFractalDraw, -reactionTime, -choiceLeft) %>%
    ggplot(aes(value, choiceLeft))+
    geom_jitter(height = .1)+
    geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, alpha=.1)+
    facet_grid(key ~ probFractalDraw)
  print(p)
  }
  
  
  # Check 3
  if(3 %in% checks){
    p = sim_data %>%
    mutate(probFractalDraw = as.factor(probFractalDraw)) %>%
    ggplot(aes(reactionTime, fill=probFractalDraw)) +
    geom_histogram(position="identity", bins=30) +
    theme(legend.position="bottom")+
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    labs(title="RT long tail?")
  print(p)
  }
  
  
  # Check 4
  if(4 %in% checks){
    p = sim_data %>%
    drop_na()%>%
    mutate(probFractalDraw = as.factor(probFractalDraw), 
           log_rt = log(reactionTime)) %>%
    group_by(probFractalDraw) %>%
    summarise(mean_log_rt = mean(log_rt),
              sem_log_rt = sem(log_rt)) %>%
    ggplot(aes(probFractalDraw, mean_log_rt))+
    geom_point()+
    geom_errorbar(aes(ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt), width=.2)+
    labs(title="Inverse U and faster when pFrac ==1?")
  print(p)
  }
  
  # Check 5
  if(5 %in% checks){
    sim_data %>%
      mutate(probFractalDraw = as.factor(probFractalDraw),
             choiceLeft = ifelse(choice == "left", 1, ifelse(choice=="right", 0, NA)),
             EVDiff = EVLeft - EVRight, 
             QVDiff = QVLeft - QVRight) %>%
      nest(data = -probFractalDraw) %>% 
      mutate(
        fit = map(data, ~ glm(choiceLeft ~ EVDiff + QVDiff, data = .x, family=binomial(link="logit"))),
        tidied = map(fit, tidy)
      ) %>% 
      unnest(tidied) %>%
      filter(term != "(Intercept)") %>%
      select(probFractalDraw, term, estimate, std.error) %>%
      ggplot(aes(probFractalDraw, estimate, col=term, group=term))+
      geom_point()+
      geom_line()+
      geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
      geom_hline(aes(yintercept=0), linetype="dashed")+
      scale_color_manual(values = cbbPalette[2:1])+
      theme(legend.position = "bottom")+
      labs(color="", title="Relevant attribute effect on choice")
  }  
}

```

## Model 1: Integrate both starting at stim presentation

DDM that can take our task specific arguments as input

```{r}
sim_trial = function(d, sigma,  barrier=1, nonDecisionTime=0, bias=0, timeStep=10, maxIter=1000, epsilon = 0.0002, ...){
  
  # d : drift rate
  # sigma: sd of the normal distribution 
  # timeStep: in ms
  # nonDecisionTime: in ms
  # maxIter: num max samples. if a barrier isn't hit by this sampling of evidence no decision is made. If time step is 10ms and maxIter is 1000 this would be a (1000 iterations * 10 ms (per iteration) / 1000 convert back to sec =) 10sec timeout maximum
  
  RDV = bias
  time = 0
  elapsedNDT = 0
  choice = 0
  RT = NA
  
  kwargs = list(...)
  EVLeft=kwargs$EVLeft
  EVRight=kwargs$EVRight
  QVLeft=kwargs$QVLeft
  QVRight=kwargs$QVRight
  probFractalDraw=kwargs$probFractalDraw
  
  while (time<maxIter){
    
    # If the RDV hit one of the barriers, the trial is over.
    if (RDV >= barrier | RDV <= -barrier){
      RT = (time * timeStep)/1000 #convert back to secs
      if (RDV >= barrier){
        choice = "left"
      } else if (RDV <= -barrier){
        choice = "right"
      }
      break
    } 
    
    # nonDecisionTime/timeStep gives how many sampling iterations the nonDecisionTime corresponds to
    nonDecIters = nonDecisionTime / timeStep
    # If elapsed time is less than the number of sampling iterations required for the nonDecisionTime set evidence sampling distribution mean to 0 so any move from starting point would only be noise
    if (elapsedNDT < nonDecIters){
      mu_mean = 0
      elapsedNDT = elapsedNDT + 1
    } else{
      # If the nonDecisionTime has passed set the mean of the distribution the decision variable will be sampled from to a value proportional to the value difference and the drift rate 
      valueLeft = probFractalDraw*QVLeft + (1-probFractalDraw)*(EVLeft)
      valueRight = probFractalDraw*QVRight + (1-probFractalDraw)*(EVRight)
      mu_mean = d*(valueLeft - valueRight)
    }
    
    # Sample the change in RDV from the distribution with mean proportional to the value difference
    mu = rnorm(1, mu_mean, epsilon)
    RDV = RDV + rnorm(1, mu, sigma)
    
    # Increment sampling iteration
    time = time + 1
  }
  
  #Organize output 
  out = data.frame(EVLeft = EVLeft, EVRight = EVRight, QVLeft = QVLeft, QVRight = QVRight, probFractalDraw = probFractalDraw, choice=choice, reactionTime = RT)
  return(out)
}
```

Filter data for a few subjects with a range of learning rates (i.e. variance in QValue differences) to simulate RTs using DDM 

```{r}
sub_data = clean_beh_data %>%
  filter(subnum  %in% c("01", "03", "05","07", "09", "11", "13", "15", "17", "19")) %>%
  select(leftQValue, rightQValue, leftLotteryEV, rightLotteryEV, probFractalDraw, reactionTime, choiceLeft, subnum)
```

How do the sanity checks look in the sampled data?

```{r}
sim_sanity_checks(sub_data %>%
                    select(-subnum) %>%
                    rename(QVLeft = leftQValue, QVRight = rightQValue, EVLeft = leftLotteryEV, EVRight = rightLotteryEV) %>%
                    mutate(choice = ifelse(choiceLeft == 1, "left", "right")))
```

**NOTE on drift rate: with a value like d=0.002 there are too many timeout trials because the scale of the value difference is much smaller than e.g. the value difference in the aDDM papers**

### Sanity checks for simulated data.

```{r}
sim_sub_data_m1_1 = sim_task(sub_data = sub_data, d = .01, sigma = .1)
```

```{r}
sim_sanity_checks(sim_sub_data_m1_1)
```

Too fast with d=0.01. Can we slow it down with d=.005?

```{r}
sim_sub_data_m1_2 = sim_task(sub_data = sub_data, d = .005, sigma = .1)
```

```{r}
sim_sanity_checks(sim_sub_data_m1_2)
```

Error bars for RTs are very wide. Can we make them smaller with smaller sigma? (from .1 to .05)

```{r}
sim_sub_data_m1_3 = sim_task(sub_data = sub_data, d = .005, sigma = .05)
```

```{r}
sim_sanity_checks(sim_sub_data_m1_3)
```

## Model 2: Begin integration about Q values earlier if that is the only relevant option

```{r}
sim_trial = function(d, sigma,  barrier=1, nonDecisionTime=0, bias=0, timeStep=10, maxIter=1000, epsilon = 0.0002,...){
  
  # d : drift rate
  # sigma: sd of the normal distribution 
  # timeStep: in ms
  # nonDecisionTime: in ms
  # maxIter: num max samples. if a barrier isn't hit by this sampling of evidence no decision is made. If time step is 10ms and maxIter is 1000 this would be a 10sec timeout maximum
  
  RDV = bias
  time = 0
  elapsedNDT = 0
  choice = 0
  RT = NA
  
  kwargs = list(...)
  EVLeft=kwargs$EVLeft
  EVRight=kwargs$EVRight
  QVLeft=kwargs$QVLeft
  QVRight=kwargs$QVRight
  probFractalDraw=kwargs$probFractalDraw
  stimDelay = 2000 #Stimulus screen comes on 2 secs after the presentation of probFractalDraw
  stimDelayIters = stimDelay / timeStep
  nonDecIters = nonDecisionTime / timeStep
  
  while (time<maxIter){
    
    # If the RDV hit one of the barriers, the trial is over.
    if (RDV >= barrier | RDV <= -barrier){
      RT = (time * timeStep)/1000 #convert ms back to secs
      
      if (RT<(stimDelay/1000)){
        RT=rnorm(1, mean = 1, sd = 0.6) #if decision is reached before the stim screen sample rt from distribution with empirical mean and sd for probFractalDraw == 1 trials
        if(RT < 0){
          RT = RT * (-1)
        }
      }
      
      if (RDV >= barrier){
        choice = "left"
      } else if (RDV <= -barrier){
        choice = "right"
      }
      break
    } 
    
    # Stim hasn't been presented yet
    # integration begins using only QVs for trials when they are the only relevant attribute
    if (time < stimDelayIters & probFractalDraw == 1){
      mu_mean = d*(QVLeft - QVRight)
    } else{ 
      if (elapsedNDT < nonDecIters){
        mu_mean = 0
        elapsedNDT = elapsedNDT + 1
        } else{
          # stim has been presented. integration of both attributes continues
          valueLeft = probFractalDraw*QVLeft + (1-probFractalDraw)*(EVLeft)
          valueRight = probFractalDraw*QVRight + (1-probFractalDraw)*(EVRight)
          mu_mean = d*(valueLeft - valueRight)
        }
      
    }
    
    # Sample the change in RDV from the distribution.
    mu = rnorm(1, mu_mean, epsilon)
    RDV = RDV + rnorm(1, mu, sigma)
    
    # Increment sampling iteration
    time = time + 1
  }
  
  #Organize output 
  out = data.frame(EVLeft = EVLeft, EVRight = EVRight, QVLeft = QVLeft, QVRight = QVRight, probFractalDraw = probFractalDraw, choice=choice, reactionTime = RT)
  return(out)
}
```

Simulate data for filtered subjects with same DDM parameters for everyone

```{r}
sim_sub_data2 = sim_task(sub_data = sub_data, d = .01, sigma = .1)
```

### Sanity checks

```{r}
sim_sanity_checks(sim_sub_data2)
```

