---
title: "Experience vs. description based decision-making project: DDM fitting to subject data"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Setup

Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
helpers_path = here('helpers/')

set.seed(38573)
```

Adding in parameters from the two systems model for all subjects (i.e. not choosing the best fitting one per subject)

```{r}
 # do this first not to mess with cluster setup
source(paste0(helpers_path,'ddmSims/fit_task.R'))
source(paste0(helpers_path,'ddmSims/sim_task.R'))

source(paste0(helpers_path,'ddmSims/sim_sanity_checks.R'))
source(paste0(helpers_path,'twoSystemsFitting/fit_twoValSystemsWithRL_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests, model_name="original")

rm(fit, g_par_ests, par_ests, get_qvals, organize_stan_output, add_inferred_pars, extract_var_for_stan)
```

Create empty list that will store the trial simulators for the forthcoming models.

```{r}
sim_trial_list = list()
fit_trial_list = list()
```


# Testing parameter recovery

## Model 2b: Asymmetric prob distortion

- Distort probFractalDraw when integrating info about fractals but no distortion for lotteries
- Intended to capture the stepwise nature of the logit slopes for the QV difference but the linear nature for the EV difference

```{r}
source(paste0(helpers_path, 'ddmSims/ddm_model2b.R'))
sim_trial_list[['model2b']] = sim_trial
fit_trial_list[['model2b']] = fit_trial
```

## Test single trial

```{r}
100 %>% 
  rerun() %>%
  map_df(~data.frame(sim_trial(d=.04, sigma=0.01, barrierDecay=0, delta=3, gamma=3, EVLeft = .7, EVRight = .2, QVLeft = .7, QVRight = .2, probFractalDraw = .4))) %>%
  summarise(meanRT = mean(reactionTime),
            numLeft = sum(choice == "left"))

```
Are likelihoods higher on average for a parameter combination that is far from the true parameters? No. Not sure why.

```{r}
tmp1 = 100 %>% 
  rerun() %>%
  map_df(~data.frame(fit_trial(d=.04, sigma=0.01, barrierDecay=0, delta=3, gamma=3, EVLeft = .7, EVRight = .2, QVLeft = .7, QVRight = .2, probFractalDraw = .4, choice = "left", reactionTime = .7))) %>%
  mutate(par_type = "true")
```

```{r}
tmp2 = 100 %>% 
  rerun() %>%
  map_df(~data.frame(fit_trial(d=.002, sigma=0.1, barrierDecay=0, delta=3, gamma=3, EVLeft = .7, EVRight = .2, QVLeft = .7, QVRight = .2, probFractalDraw = .4, choice = "left", reactionTime = .7))) %>%
  mutate(par_type = "far")
```

```{r}
rbind(tmp1, tmp2) %>%
  ggplot(aes(par_type, log(likelihood))) +
  geom_boxplot()
```

```{r}
rm(tmp1, tmp2)
```

## Test all trials in a task

Can the likelihood function correctly identify the parameter combination that generated the data? Is the sum of likelihoods for all trials highest for the correct combination than any other combination?

```{r}
sub_data = clean_beh_data %>%
  filter(subnum  %in% c("19")) %>%
  select(leftQValue, rightQValue, leftLotteryEV, rightLotteryEV, probFractalDraw, reactionTime, choiceLeft, subnum) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue)
```

```{r}
true_dat = sim_task(sub_data, model_name = "model2b", d=0.02, sigma = 0.007, delta = 3, gamma = 3, barrierDecay = 0.004, epsilon = 0.03, nonDecisionTime = 0)
```

```{r}
fit1_data = fit_task(true_dat, model_name = "model2b", d=0.02, sigma = 0.007, delta = 3, gamma = 3, barrierDecay = 0.004, epsilon = 0.03, nonDecisionTime = 0)
```

```{r}
fit2_data = fit_task(true_dat, model_name = "model2b", d=0.05, sigma = 0.01, delta = 2, gamma = 2, barrierDecay = 0.001, epsilon = 0, nonDecisionTime = 0)
```

```{r}
fit3_data = fit_task(true_dat, model_name = "model2b", d=0.03, sigma = 0.01, delta = 3, gamma = 3, barrierDecay = 0, epsilon = 0.0004, nonDecisionTime = 0)
```

Are the sum of likelihoods are higher using the true parameter combination compared to false combinations?

```{r}
sum(fit1_data$likelihood) > sum(fit2_data$likelihood)
```

```{r}
sum(fit1_data$likelihood) > sum(fit3_data$likelihood)
```

```{r}
fit1_data %>%
  mutate(par_type = "true") %>%
  rbind(fit2_data %>% mutate(par_type = "false_1")) %>%
  rbind(fit3_data %>% mutate(par_type = "false_2")) %>%
  ggplot(aes(par_type, log(likelihood))) +
  geom_boxplot()+
  xlab("")
```

# Parameter recovery

