---
title: "Experience vs. description based decision-making project: DDM parameter recovery with the `optim` function"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Setup

Set up environment and load in data

```{r include=FALSE, message=FALSE}
library(tidyverse)
library(here)
library(gridExtra)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
helpers_path = here('analysis/helpers/')
cpueaters_paths = '/Users/zeynepenkavi/CpuEaters/DescribedVsLearned_beh/analysis/helpers/'
source(paste0(helpers_path, 'ddModels/ddm_par_recovery_report.R'))

set.seed(38573)
```

# Recovery with random starts on random datasets

Note: This took ~1 hour for a single subject's data running two jobs on each node for 25 compute nodes.

`docker run --rm -it -v ~/.aws:/root/.aws -v $(pwd):/cluster_scripts amazon/aws-cli s3 sync  s3://described-vs-experienced/ddModels/cluster_scripts/optim_out /cluster_scripts/optim_out`

Sample plots summarizing the simulations

```{r}
model_name = "model1a"
data_name = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')

ddm_par_recovery_report(model_ = model_name, data_ = data_name, optim_out_path_=optim_out_path)
```

```{r}
ddm_par_recovery_report(model_ = model_name, data_ = data_name, optim_out_path_=optim_out_path, diff_pct_plots_ = TRUE)
```

To get a sense of recovery success for different parameter combinations I created 20 random datasets using the following steps:   

- Sample `d` and `sigma` from a uniform distribution between 0 and 1 and `delta` and `gamma` from a uniform distribution between 1 and 8.   
- Simulate data for a single subject using the same conditions (QV and EV pairs) across parameter combinations.  
- Run `optim` (the built-in optimizer using the Nelder-Mead algorithm) with 1000 random starts on each of these 20 datasets.  
- The starting values were sampled from the same distributions described above.  

## Results

- [Scatter plots of start and convergend points in each iteration for all parameters](../outputs/fig/ddm_recovery_rand_datasets_scatter.pdf)  
  - Variance in recovered parameters is always higher for `delta` and `gamma` than for `d` and `sigma`  
  - There is almost invariably a correlation between start and end points for `delta` and `gamma` but not for `d` and `sigma`  
- [Median percentage of difference for each parameter across datasets](../outputs/fig/ddm_recovery_rand_datasets_diff_pct.pdf)
  - `Delta` and `gamma` are not always the worst recovered parameters. There are cases, albeit fewer, where `d` and `sigma` are not recovered well either (7 of 20 datasets). A quick look suggests these are cases with very small `sigma`.
  - [Percentage of difference by true value](../outputs/fig/ddm_recovery_rand_datasets_pct_diff_by_true_value.pdf): no strong relationship unless d or sigma are very small, in which case they are not recovered.
- Correlation between recovered parameters
  - [Delta and gamma](../outputs/fig/ddm_recovery_rand_datasets_delta_gamma_cor.pdf.pdf)
  - [d and sigma](../outputs/fig/ddm_recovery_rand_datasets_d_sigma_cor.pdf.pdf)

```{r eval=FALSE}
model_name = "model1a"
data_prefix = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
fig_out_path = paste0(here(), '/outputs/fig/')

out_iters = data.frame()

for(i in 1:20){
  cur_out = get_optim_out(model_ = model_name, data_=paste0(data_prefix, i), optim_out_path_ = optim_out_path, iters= TRUE)
  cur_out$dataset = i
  cur_out$true_pars = get_true_pars(data_=paste0(data_prefix, i), true_pars_path_ =  true_pars_path, return_str_ = TRUE)
  out_iters = rbind.all.columns(out_iters, cur_out)
}

out_iters = out_iters %>%
  rename(d = Param1, sigma = Param2, delta = Param3, gamma = Param4, nll = Result)
``` 

```{r eval=FALSE}
p_df = out_iters %>%
  filter(Iteration != 1) %>%
  filter(abs(delta) < 10 & delta > 0) %>%
  filter(abs(gamma) < 10 & gamma > 0) %>%
  group_by(dataset) %>%
  mutate(dg_cor = cor(delta, gamma)) %>%
  ungroup()

p_df_annot = p_df %>% 
  select(true_pars, dg_cor) %>%
  distinct() %>%
  mutate(dg_cor = paste0("r = ", round(dg_cor, 3)))
  
p = p_df %>% ggplot(aes(delta, gamma)) +
  geom_point(color="gray", size=.5)+
  facet_wrap(~true_pars, labeller = labeller(true_pars = label_wrap_gen(26) ) ) +
  geom_text(data = p_df_annot, aes(x = 2.5, y = 2.5, label = dg_cor), size=3)

ggsave(file=paste0(fig_out_path, 'ddm_recovery_rand_datasets_delta_gamma_cor.pdf'), p, height = 8, width=11, units="in")

```

```{r eval=FALSE}
p_df = out_iters %>%
  filter(Iteration != 1) %>%
  group_by(dataset) %>%
  mutate(ds_cor = cor(d, sigma)) %>%
  ungroup()

p_df_annot = p_df %>% 
  select(true_pars, ds_cor) %>%
  distinct() %>%
  mutate(ds_cor = paste0("r = ", round(ds_cor, 3)))
  
p = p_df %>% ggplot(aes(d, sigma)) +
  geom_point(color="gray", size=.5)+
  facet_wrap(~true_pars, labeller = labeller(true_pars = label_wrap_gen(26) ), scales="free") +
  geom_text(data = p_df_annot, aes(x= Inf, y=Inf,label = ds_cor), size=3, vjust = "top", hjust = "right")

ggsave(file=paste0(fig_out_path, 'ddm_recovery_rand_datasets_d_sigma_cor.pdf'), p, height = 8, width=11, units="in")

```

```{r eval=FALSE}
# Correlation between delta and gamma for the best estimate (the one with the lowest negative log likelihood) across datasets

out_iters %>%
  filter(Iteration != 1) %>%
  group_by(dataset) %>%
  filter(nll == min(nll)) %>%
  ggplot(aes(delta, gamma))+
  geom_point()+
  xlim(1,10)+
  ylim(1, 10)+
  labs(title = "Correlation between delta and gamma for the best estimate across datasets")
```

```{r eval=FALSE}
model_name = "model1a"
data_prefix = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
fig_out_path = paste0(here(), '/outputs/fig/')

out_pars = data.frame()

for(i in 1:20){
  cur_out = get_optim_out(model_ = model_name, data_=paste0(data_prefix, i), optim_out_path_ = optim_out_path, iters= FALSE)
  cur_out$dataset = i
  cur_true_pars = get_true_pars(data_=paste0(data_prefix, i), true_pars_path_ =  true_pars_path, return_str_ = FALSE)$true_pars
  cur_true_pars = cur_true_pars %>% rename(true= value)
  cur_out = cur_out %>%
    rename(d = Param1, sigma = Param2, delta = Param3, gamma = Param4) %>%
    gather(key, est, -dataset) %>%
    left_join(cur_true_pars, by="key") %>%
    mutate(abs_diff_pct = abs(est-true)/true*100)
  out_pars = rbind.all.columns(out_pars, cur_out)
}
  
```

```{r eval=FALSE}
p = out_pars %>%
  filter(true>0) %>%
  group_by(dataset, key) %>%
  summarise(.groups="keep",
            median_diff_pct = median(abs_diff_pct),
            true = unique(true)) %>%
  ggplot(aes(true, median_diff_pct)) +
  geom_point() +
  facet_wrap(~key, scales="free")+
  labs(x="True parameter value", y="Median % difference between true and recovered value")

ggsave(file=paste0(fig_out_path, 'ddm_recovery_rand_datasets_pct_diff_by_true_value.pdf'), p, height = 8, width=11, units="in")
```


Given the correlation between delta and gamma maybe a try a parameterization with a single parameter for the distortion function? In fact, the logit slopes suggest that there isn't really any overweighting of probFractalDraw even for higher values at the group level (not to mention the large individual differences). So maybe what we need is not a sigmoid function but one that underweights almost all probFractalDraw values.

```{r}
delt = .1
gamm = 5

data.frame(prob = seq(0,1,.1)) %>%
  mutate(distorted_delta_gamma = (delt * (prob)^gamm) / ( (delt * (prob)^gamm) + (1-prob)^gamm ),
         distorted_delta_1 = ((prob)^gamm) / ( ((prob)^gamm) + (1-prob)^gamm )  ,
         distorted_gamma_1 = (delt * (prob)) / ( (delt * (prob)) + (1-prob)),) %>%
  gather(key, value, -prob) %>%
  ggplot(aes(prob, value, color=key))+
  geom_point()+
  geom_line()+
  geom_abline(aes(intercept=0, slope = 1), linetype="dashed")+
  theme(legend.position = "bottom")+
  labs(color="")
```

# Delta-gamma grid search

- Grid of recovery success for delta and gamma when d and sigma are fixed
  - Fix d = 0.1, sigma = 0.08 for delta and gamma = c(.1, .2, 1, 3, 5) 25 datasets, Note when delta == 1 you have the green and when gamma == 1 you have the blue curve
    - 4 heatmaps: for each combination delta and gamma what is the median percentage of difference for each parameter across the 1000 iterations 
    - [Similar to the heatmaps below](../outputs/fig/ddm_recovery_dg_grid_pct_diff_by_true_value.pdf)
        - Recovery of d and sigma are better when delta and gamma are > 1
    - [Correlations between recovered d and sigma are often high](../outputs/fig/ddm_recovery_dg_grid_d_sigma_cor.pdf)
    - [Correlations between recovered delta and gamma increase as true delta increases. For delta < 1 recovered gamma values are terrible](../outputs/fig/ddm_recovery_dg_grid_delta_gamma_cor.pdf)
    - [](../outputs/fig/ddm_recovery_dg_grid_scatter.pdf)
    - [](../outputs/fig/ddm_recovery_dg_grid_diff_pct.pdf)

```{r}
model_name = "model1a"
data_prefix = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
fig_out_path = paste0(here(), '/outputs/fig/')

dg_grid_diff_pct = data.frame()

for(i in 21:45){
  cur_out = ddm_par_recovery_report(model_ = model_name, data_ = paste0(data_prefix, i), optim_out_path_=optim_out_path, diff_pct_plots_ = TRUE)$diff_pct_data
  cur_out$dataset = i-20
  dg_grid_diff_pct = rbind.all.columns(dg_grid_diff_pct, cur_out)
}
```

```{r}
dg_grid_diff_pct %>% filter(key == "delta") %>% select(-median_diff) %>%
  left_join(dg_grid_diff_pct %>% filter(key == "gamma")%>% select(-median_diff), by="dataset") %>%
  left_join(dg_grid_diff_pct %>% filter(key == "d")%>% select(-true_val), by="dataset") %>%
  rename(delta = true_val.x, gamma = true_val.y) %>%
  select(-key.x, -key.y, -key) %>%
  mutate(delta = as.factor(delta),
         gamma = as.factor(gamma)) %>%
  ggplot(aes(delta, gamma, fill=median_diff))+
  geom_tile() +
  labs(title= "Median percentage difference between true and recovered d")+
  theme(legend.position = "bottom")

dg_grid_diff_pct %>% filter(key == "delta") %>% select(-median_diff) %>%
  left_join(dg_grid_diff_pct %>% filter(key == "gamma")%>% select(-median_diff), by="dataset") %>%
  left_join(dg_grid_diff_pct %>% filter(key == "sigma")%>% select(-true_val), by="dataset") %>%
  rename(delta = true_val.x, gamma = true_val.y) %>%
  select(-key.x, -key.y, -key) %>%
  mutate(delta = as.factor(delta),
         gamma = as.factor(gamma)) %>%
  ggplot(aes(delta, gamma, fill=median_diff))+
  geom_tile() +
  labs(title= "Median percentage difference between true and recovered sigma")+
  theme(legend.position = "bottom")

dg_grid_diff_pct %>% filter(key == "delta") %>% select(-median_diff) %>%
  left_join(dg_grid_diff_pct %>% filter(key == "gamma")%>% select(-median_diff), by="dataset") %>%
  left_join(dg_grid_diff_pct %>% filter(key == "delta")%>% select(-true_val), by="dataset") %>%
  rename(delta = true_val.x, gamma = true_val.y) %>%
  select(-key.x, -key.y, -key) %>%
  mutate(delta = as.factor(delta),
         gamma = as.factor(gamma)) %>%
  ggplot(aes(delta, gamma, fill=median_diff))+
  geom_tile() +
  labs(title= "Median percentage difference between true and recovered delta")+
  theme(legend.position = "bottom")

dg_grid_diff_pct %>% filter(key == "delta") %>% select(-median_diff) %>%
  left_join(dg_grid_diff_pct %>% filter(key == "gamma")%>% select(-median_diff), by="dataset") %>%
  left_join(dg_grid_diff_pct %>% filter(key == "gamma")%>% select(-true_val), by="dataset") %>%
  rename(delta = true_val.x, gamma = true_val.y) %>%
  select(-key.x, -key.y, -key) %>%
  mutate(delta = as.factor(delta),
         gamma = as.factor(gamma)) %>%
  ggplot(aes(delta, gamma, fill=log(median_diff)))+
  geom_tile() +
  labs(title= "Median percentage difference between true and recovered gamma")+
  theme(legend.position = "bottom")
```

```{r eval=FALSE}
model_name = "model1a"
data_prefix = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
fig_out_path = paste0(here(), '/outputs/fig/')

out_iters = data.frame()

for(i in 21:45){
  cur_out = get_optim_out(model_ = model_name, data_=paste0(data_prefix, i), optim_out_path_ = optim_out_path, iters= TRUE)
  cur_out$dataset = i-20
  cur_out$true_pars = get_true_pars(data_=paste0(data_prefix, i), true_pars_path_ =  true_pars_path, return_str_ = TRUE)
  out_iters = rbind.all.columns(out_iters, cur_out)
}

out_iters = out_iters %>%
  rename(d = Param1, sigma = Param2, delta = Param3, gamma = Param4, nll = Result)
```

```{r eval=FALSE}
p_df = out_iters %>%
  filter(Iteration != 1) %>%
  filter(abs(delta) < 10 & delta > 0) %>%
  filter(abs(gamma) < 10 & gamma > 0) %>%
  group_by(dataset) %>%
  mutate(dg_cor = cor(delta, gamma)) %>%
  ungroup()

p_df_annot = p_df %>% 
  select(true_pars, dg_cor) %>%
  distinct() %>%
  mutate(dg_cor = paste0("r = ", round(dg_cor, 3)))
  
p = p_df %>% ggplot(aes(delta, gamma)) +
  geom_point(color="gray", size=.5)+
  facet_wrap(~true_pars, labeller = labeller(true_pars = label_wrap_gen(26) ) ) +
  geom_text(data = p_df_annot, aes(x = 2.5, y = 2.5, label = dg_cor), size=3)

ggsave(file=paste0(fig_out_path, 'ddm_recovery_dg_grid_delta_gamma_cor.pdf'), p, height = 8, width=11, units="in")

```

```{r eval=FALSE}
p_df = out_iters %>%
  filter(Iteration != 1) %>%
  group_by(dataset) %>%
  mutate(ds_cor = cor(d, sigma)) %>%
  ungroup()

p_df_annot = p_df %>% 
  select(true_pars, ds_cor) %>%
  distinct() %>%
  mutate(ds_cor = paste0("r = ", round(ds_cor, 3)))
  
p = p_df %>% ggplot(aes(d, sigma)) +
  geom_point(color="gray", size=.5)+
  facet_wrap(~true_pars, labeller = labeller(true_pars = label_wrap_gen(26) ), scales="free") +
  geom_text(data = p_df_annot, aes(x= Inf, y=Inf,label = ds_cor), size=3, vjust = "top", hjust = "right")

ggsave(file=paste0(fig_out_path, 'ddm_recovery_dg_grid_d_sigma_cor.pdf'), p, height = 8, width=11, units="in")

```

```{r eval=FALSE}
model_name = "model1a"
data_prefix = "sim_single_sub_data"
optim_out_path = paste0(cpueaters_paths, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
fig_out_path = paste0(here(), '/outputs/fig/')

out_pars = data.frame()

for(i in 21:45){
  cur_out = get_optim_out(model_ = model_name, data_=paste0(data_prefix, i), optim_out_path_ = optim_out_path, iters= FALSE)
  cur_out$dataset = i-20
  cur_true_pars = get_true_pars(data_=paste0(data_prefix, i), true_pars_path_ =  true_pars_path, return_str_ = FALSE)$true_pars
  cur_true_pars = cur_true_pars %>% rename(true= value)
  cur_out = cur_out %>%
    rename(d = Param1, sigma = Param2, delta = Param3, gamma = Param4) %>%
    gather(key, est, -dataset) %>%
    left_join(cur_true_pars, by="key") %>%
    mutate(abs_diff_pct = abs(est-true)/true*100)
  out_pars = rbind.all.columns(out_pars, cur_out)
}
  
```

```{r eval=FALSE}
p = out_pars %>%
  filter(true>0) %>%
  group_by(dataset, key) %>%
  summarise(.groups="keep",
            median_diff_pct = median(abs_diff_pct),
            true = unique(true)) %>%
  ggplot(aes(true, median_diff_pct)) +
  geom_point() +
  facet_wrap(~key, scales="free")+
  labs(x="True parameter value", y="Median % difference between true and recovered value")

ggsave(file=paste0(fig_out_path, 'ddm_recovery_dg_grid_pct_diff_by_true_value.pdf'), p, height = 8, width=11, units="in")
```

Fix (don't optimize over) d and sigma in recovery!

Should I do this hard-coding the d and sigma values in a new model model1a_fixed or by adding the option to have fixed parameters to fit_task and get_nll functions?

```{r}

```

------------------------------------------------------------------------------------------------
More data per optimization? (currently for single subject)
Hierarchical estimation?

Would you compute posterior among these different optimized values? Is there any point in doing that even when there is no iteration that has converged on the true values?

```{r}

```


