---
title: "Experience vs. description based decision-making project: DDM parameter recovery multiple round optimization"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Setup

Set up environment and load in data

```{r include=FALSE, message=FALSE}
library(here)
helpers_path = here('analysis/helpers/')
cpueaters_path = '/Users/zeynepenkavi/CpuEaters/DescribedVsLearned_beh/analysis/helpers/'
fig_out_path = paste0(here(),'/outputs/fig/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')
```

```{r include=FALSE, message=FALSE, eval=FALSE}
library(tidyverse)
library(gridExtra)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}

source(paste0(helpers_path, 'optimPostProcess/par_recovery_report.R'))

source(paste0(helpers_path, 'ddModels/fit_task.R'))
sim_trial_list = list()
fit_trial_list = list()

library(visualMLE)

set.seed(385736)
```

# 3 parameter model

Recovery exercises both on random datasets, as well as, on a grid of delta and gamma showed a correlation between these parameters and therefore issues in identifiability.   

Motivated also by the logit analyses for the whole sample, which showed that while the weight of EVs decreased monotonically, weight of QVs followed more a step function/was possibly consistently underweighted I decided to switch the probability distortion function to a single parameter one.  

In this notebook I look at how well the parameters of a now three parameter model (d, sigma, delta) are recovered using two different optimization methods.  

To understand how well recovery works (especially for delta) using a three parameter model (d, sigma, delta) I systematically varied each parameter and generated 36 datasets to optimize over. The datasets were generated using the combination of the true values `true_ds = c(.001, .06 , .5)`, `true_sigmas = c(.001, .08, .3)`, `true_deltas = c(.1, .5 , 1, 3)`.  

## Data and helper functions

```{r eval=FALSE}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/')
true_pars_path = paste0(helpers_path, 'ddModels/cluster_scripts/test_data/')

model = "model1c"
data_suffix = "sim_single_sub_data"

data_nums = c(46:81)
sim_types = c("sim3", "sim3b")

# Note this takes a little bit
comp_data = data.frame()

for(i in 1:length(data_nums)){
  cur_data_num = data_nums[i]
  for(j in 1:length(sim_types)){
    cur_sim_type = sim_types[j]
    cur_out = par_recovery_report(model_ = model, data_ = paste0(data_suffix,cur_data_num), optim_out_path_= paste0(optim_out_path, cur_sim_type, '/'), true_pars_path_ = true_pars_path, diff_pct_plots_ = TRUE)$diff_pct_data
    cur_out$sim_type = cur_sim_type
    cur_out$data_num = as.character(cur_data_num)
    comp_data = rbind.all.columns(comp_data, cur_out)
  }
}
```

```{r eval=FALSE}
plot_heatmaps = function(x_par = "d", y_par = "sigma", fill_par = "delta", plt_sim_type = "sim3"){
  
  comp_data = comp_data %>%
    mutate(true_val = as.factor(true_val)) %>%
    filter(sim_type == plt_sim_type)
  
  tmp1 = comp_data %>%
    filter(key == x_par) %>%
    select(key, true_val, data_num) %>%
    spread(key, true_val)
  
  tmp2 = comp_data %>%
    filter(key == y_par) %>%
    select(key, true_val, data_num) %>%
    spread(key, true_val)
  
  tmp3 = comp_data %>%
    filter(key == fill_par) %>%
    select(key, true_val, data_num) %>%
    spread(key, true_val) %>%
    rename(true_val = fill_par)
  
  tmp4 = comp_data %>%
    filter(key == fill_par) %>%
    select(key, median_diff, data_num) %>%
    spread(key, median_diff) %>%
    rename(median_diff = fill_par)
  
  p = tmp1 %>%
    left_join(tmp2, by="data_num") %>%
    left_join(tmp3, by="data_num") %>%
    left_join(tmp4, by="data_num") %>%
    mutate(median_diff_clipped = ifelse(median_diff>100, 101, median_diff)) %>%
    ggplot(aes_string(x=x_par, y=y_par))+
    geom_tile(aes(fill=median_diff_clipped))+
    facet_grid(.~true_val)+
    theme(legend.position = "bottom")+
    labs(x=x_par, y=y_par, fill=paste0("Median % difference between true and estimated ", fill_par))
  return(p)
}
```

## Sim3: Single round optimization

```{r eval=FALSE}
fig_fn = 'ddm_recovery_sim3'
```

How bad was delta recovery for each combination of d and sigma (3 by 3 heatmap) panels for each value of delta (4 panels)  
How bad was d recovery for each combination of delta and sigma (3 by 4 heatmap) panels for each value of d (3 panels)  
How bad was sigma recovery for each combination of d and delta (3 by 4 heatmap) panels for each value of sigma (3 panels)  

```{r eval=FALSE}
p1 = plot_heatmaps(x_par = "d", y_par = "sigma", fill_par = "delta") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
p2 = plot_heatmaps(fill_par = "d", y_par = "sigma", x_par = "delta") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
p3 = plot_heatmaps(y_par = "d", fill_par = "sigma", x_par = "delta") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
```

```{r eval=FALSE}
g = arrangeGrob(grobs=list(p1, p2, p3), nrow=3)
# ggsave(file=paste0(fig_out_path, fig_fn, '_diff_pct_heatmaps.jpg'), g, height = 8, width=11, units="in")
ggsave(file=paste0(fig_out_path, fig_fn, '_diff_pct_heatmaps.pdf'), g, height = 8, width=11, units="in")
```

```{r echo=FALSE, out.width='100%'}
fig_name = 'ddm_recovery_sim3_diff_pct_heatmaps.jpg'
knitr::include_graphics(paste0(fig_out_path, fig_name))
```

**Conclusion:**  
- When d is very small (.001) delta < 1 can't be recovered.  
- Delta can recovered with some success for medium and high values of d and medium and low values of sigma.  
- For the sample parameters I tried initially (d=.06, sigma=.08, delta=3) delta recovery is particularly poor compared to other cases when delta=3.  
- When d and sigma are very small (0.001) they can't be recovered.  
- d can be successfully recovered for other cases with lower difference from true value as the true value of d increases.  
- sigma can be successfull recovered when not very small.  

## Sim3b: Two round optimization 

```{r eval=FALSE}
fig_fn = 'ddm_recovery_sim3b'
```

How bad was delta recovery for each combination of d and sigma (3 by 3 heatmap) panels for each value of delta (4 panels)  
How bad was d recovery for each combination of delta and sigma (3 by 4 heatmap) panels for each value of d (3 panels)  
How bad was sigma recovery for each combination of d and delta (3 by 4 heatmap) panels for each value of sigma (3 panels)  

```{r eval=FALSE}
p1 = plot_heatmaps(x_par = "d", y_par = "sigma", fill_par = "delta", plt_sim_type = "sim3b") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
p2 = plot_heatmaps(fill_par = "d", y_par = "sigma", x_par = "delta", plt_sim_type = "sim3b") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
p3 = plot_heatmaps(y_par = "d", fill_par = "sigma", x_par = "delta", plt_sim_type = "sim3b") +
  theme(legend.margin=margin(0,0,0,0), legend.box.margin=margin(-10,-10,0,-10))
```

```{r eval=FALSE}
g = arrangeGrob(grobs=list(p1, p2, p3), nrow=3)
ggsave(file=paste0(fig_out_path, fig_fn, '_diff_pct_heatmaps.pdf'), g, height = 8, width=11, units="in")
```

```{r echo=FALSE, out.width='100%'}
fig_name = 'ddm_recovery_sim3b_diff_pct_heatmaps.jpg'
knitr::include_graphics(paste0(fig_out_path, fig_name))
```

**Conclusion:**  
- d and sigma recovery conclusions are largely the same for two round and single round optimization.  
- delta recovery for delta < 1 is slightly worse than single round optimization (remember for the first round it is fixed at 1 so it seems it does not move sufficiently for the second round).  
- delta recovery for delta > 1 is also worse than single round optimization.  

## Comparison of sim3 and sim3b   

Scatter plot of median percentage difference from true value for single round (x-axis) vs two round (y-axis) for each parameter

```{r eval=FALSE}
fig_fn = 'ddm_recovery_sim3_sim3b'
```

```{r eval=FALSE}
p = comp_data %>%
  mutate(median_diff_clipped = ifelse(median_diff > 100, 101, median_diff)) %>%
  select(-median_diff) %>%
  group_by(key) %>%
  spread(sim_type, median_diff_clipped) %>%
  ggplot(aes(sim3, sim3b, color=as.factor(true_val)))+
  geom_point(size=4)+
  geom_abline(aes(slope=1, intercept=0), linetype="dashed") +
  facet_wrap(~key)+
  labs(title="Comparison of recovery success between optimization methods\n(median % difference between true and estimated value)",
       x="One round optimization",
       y="Two round optimization",
       color= "True value")+
  theme(legend.position = "bottom")

ggsave(file=paste0(fig_out_path, fig_fn, '_diff_pct_comparison.pdf'), p, height = 8, width=11, units="in")
```

```{r echo=FALSE, out.width='100%'}
fig_name = 'ddm_recovery_sim3_sim3b_diff_pct_comparison.jpg'
knitr::include_graphics(paste0(fig_out_path, fig_name))
```

**Conclusion:**  
- For small d both methods are bad.  
- For medium d single round is worse if sigma is too small. Otherwise two round is worse.  
- For large d two round is always worse.  
- For small sigma both are bod.  
- For medium sigma two round is either comparable or worse.  
- For large sigma both are good.  
- For delta < 1 two rounds is slightly to severely worse.  
- For delta = 1 both methods are comparable.  
- For delta > 1 two rounds is worse.  
- Overall, two round optimization doesn't improve recovery.  

Next:  
- If I fit this model to subject's data, what are the parameter distributions and how good is the fit (fit model using 2/3 and predict left out 1/3)  
- (Kill roptim cluster)  
- Joint DDM and RL modeling  
- Hierarchical estimation  

Meeting note:   
- Make likelihood surface for one of the recovered delta-gamma correlation scatter plots  

------------------------------------------------------------------------------------------------
More data per optimization? (currently for single subject)

Would you compute posterior among these different optimized values? Is there any point in doing that even when there is no iteration that has converged on the true values?