---
title: "Experience vs. description based decision-making project: DDM RL joint modeling"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

Note: This only takes fractal rewards into account. The overall trial reward is not included anywhere.

Before building a model including trial reward first check whether this has any behavioral effect.
What behavioral effect could/should it have? 
It shouldn't affect learning, fractal rewards only depend on their own probabilities. 
It shouldn't affect choice separate from all the other components of EV, QV and their weighted sum based on probFractalDraw because it is a direct function of those components.

It might affect perseverance, ie choosing the same side if a reward was received for the previous trial.

```{r include=FALSE, message=FALSE}
library(tidyverse)
library(here)
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
helpers_path = here('analysis/helpers/')
library(visualMLE)
set.seed(38573)
```

```{r message=FALSE}
source(paste0(helpers_path,'ddrlModels/sim_task_sequential.R'))
test_trial_conditions = read.csv(paste0(helpers_path, 'ddrlModels/cluster_scripts/test_data/test_trial_conditions.csv'))
```

Empty lists to store the trial simulators for the forthcoming models.

```{r}
sim_trial_list = list()
```

```{r}
source(paste0(helpers_path, 'ddrlModels/r_dd_rl_models/ddrl_model1c.R'))

sim_trial_list[['model1c']] = sim_trial
```

```{r}
tru_d = .06
tru_sigma = .08
tru_alpha = .3
tru_delta = .5
```

Test single trial simulation function

```{r}
QVLeft = 0.4
QVRight = 0.2
sim_trial(d = tru_d, sigma = tru_sigma, alpha = tru_alpha, delta = tru_delta, 
         EVLeft = test_trial_conditions$EVLeft[1], EVRight = test_trial_conditions$EVRight[1],
         leftFractalReward = test_trial_conditions$leftFractalReward[1], rightFractalReward = test_trial_conditions$rightFractalReward[1],
         probFractalDraw = test_trial_conditions$probFractalDraw[1],
         QVLeft = QVLeft, QVRight = QVRight)
```
Test multiple trial simulation function

```{r}
# Simulate choice and RT for the replicated trial conditions
sim_task_sequential(test_trial_conditions, model_name = "model1c", d = tru_d, sigma = tru_sigma, delta = tru_delta, alpha = tru_alpha)
```