---
title: 'Experience vs. description based decision-making project: DDRL with Stan (probabilistic estimation)'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

# Set up

```{r include=FALSE}
library(tidyverse)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
library(RWiener)
```

```{r}
helpers_path = here('analysis/helpers/')
```

```{r include=FALSE}
source(paste0(helpers_path, 'facet_wrap_equal.R'))
source(paste0(helpers_path, 'rlModels/make_posterior_predictive_data.R'))
source(paste0(helpers_path, 'rlModels/identifiability_analysis.R'))
```

Set theme for plots

```{r}
theme_set(theme_bw())
```

# Pure dd

- Not hierarchical  
- Estimating individual threshold, bias, drift rate and NDT  
- Not including value difference between options  
- No learning  

```{r message=FALSE}
source(paste0(helpers_path,'ddrlModels/fit_pure_dd_stan.R'))
par_ests_var = par_ests
```

## Log likelihood distributions

```{r}
par_ests_var %>%
  filter(par == "alpha") %>% #filtering one parameter bc likelihood for combinations of parameters is the same. nothing special abt alpha here
  ggplot(aes(logLik)) +
  geom_histogram(alpha=.5, bins=30, position="identity")+
  facet_wrap(~subnum, scales="free_x")+
  xlab("Log Likelihood")+
  ylab("")+
  ggtitle("Distribution of log likelihoods across the samples for each subject")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank())
```

## Parameter estimates

Drift rates for most subjects are very peaky but for five subjects they are much more variable.

```{r}
par_ests_var %>%
  ggplot(aes(value)) +
  geom_histogram(bins=30)+
  facet_grid(subnum ~ par, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank())
```

## Covariance between parameters

```{r}
tmp = par_ests_var %>%
  group_by(par) %>%
  mutate(iter = 1:n()) %>%
  group_by(iter) %>%
  spread(par, value) %>%
  ungroup() %>%
  select(-iter, -logLik, -subnum)

round(cor(tmp), 3)  
```

## Posterior predictive checks

Using mean posterior estimates

Predicted vs actual RT distributions conditioned on choice

```{r}
sub_par_ests_var = par_ests_var %>%
  group_by(subnum , par) %>%
  summarise(mean_val = mean(value), .groups="keep") %>%
  spread(par, mean_val)
```

```{r}
sim_data_var = data.frame()
for(i in 1:nrow(sub_par_ests_var)){
  
  sim_sub_data = rwiener(n = 300, alpha = sub_par_ests_var$alpha[i], tau = sub_par_ests_var$tau[i], beta = sub_par_ests_var$beta[i], delta = sub_par_ests_var$delta[i])
  sim_sub_data$subnum = sub_par_ests_var$subnum[i]
  if(i == 1){
    sim_data_var = sim_sub_data
  } else{
    sim_data_var = rbind(sim_data_var, sim_sub_data)
  }
}
```

```{r fig.height=10}
sim_data_var %>%
  mutate(resp = ifelse(resp == "upper", "left", "right"),
         data_type = "sim") %>%
  rbind(clean_beh_data %>%
          select(subnum, choiceLeft,reactionTime) %>%
          rename(q=reactionTime, resp=choiceLeft) %>%
          mutate(resp = ifelse(resp == 1, "left", "right"),
                 data_type = "true")) %>%
  ggplot(aes(q, fill=data_type))+
  geom_density(alpha=.5, color=NA)+
  facet_grid(subnum~resp, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
```

# Pure dd with fixed pars

- Boundary separation alpha fixed at 2  
- Bias beta fixed at .5 (no bias)
- NDT tau fixed at .1

```{r}
source(paste0(helpers_path,'ddrlModels/fit_pure_dd_fixpars_stan.R'))
par_ests_fix = par_ests
```

## Log likelihood distributions

Compare log likelihoods to previous model where three other parameters were estimated instead of fixed.  

Model with fixed parameters is consistently a worse fit.

```{r}
par_ests_fix %>%
  filter(par == "delta") %>% #filtering one parameter bc likelihood for combinations of parameters is the same. nothing special abt alpha here
  mutate(data_type="sim_fix") %>%
  rbind(par_ests_var %>%
          filter(par == "delta") %>% #filtering one parameter bc likelihood for combinations of parameters is the same. nothing special abt alpha here
          mutate(data_type="sim_var")) %>%
  ggplot(aes(logLik, fill=data_type)) +
  geom_histogram(alpha=.5, bins=30, position="identity")+
  facet_wrap(~subnum, scales="free_x")+
  xlab("Log Likelihood")+
  ylab("")+
  ggtitle("Distribution of log likelihoods across the samples for each subject")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
```

## Parameter estimates

Compare drift rates to previous model where three other parameters were estimated instead of fixed.

```{r}
par_ests_fix %>%
  mutate(data_type="sim_fix") %>%
  rbind(par_ests_var %>%
          filter(par == "delta") %>%
          mutate(data_type = "sim_var")) %>%
  ggplot(aes(value, fill=data_type)) +
  geom_histogram(bins=30, position="identity", alpha=.5)+
  facet_wrap(~subnum, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
```
## Posterior predictive checks

Using mean posterior estimates

Predicted vs actual RT distributions conditioned on choice

```{r}
sub_par_ests_fix= par_ests_fix %>%
  group_by(subnum , par) %>%
  summarise(mean_val = mean(value), .groups="keep") %>%
  spread(par, mean_val)
```

```{r}
sim_data_fix = data.frame()
for(i in 1:nrow(sub_par_ests_fix)){
  
  sim_sub_data = rwiener(n = 300, alpha = 2, tau = .1, beta = .5, delta = sub_par_ests_fix$delta[i])
  sim_sub_data$subnum = sub_par_ests_fix$subnum[i]
  if(i == 1){
    sim_data_fix = sim_sub_data
  } else{
    sim_data_fix = rbind(sim_data_fix, sim_sub_data)
  }
}
```

```{r fig.height=10}
sim_data_var %>%
  mutate(resp = ifelse(resp == "upper", "left", "right"),
         data_type = "sim_var") %>%
  rbind(sim_data_fix %>%
  mutate(resp = ifelse(resp == "upper", "left", "right"),
         data_type = "sim_fix")) %>%
  rbind(clean_beh_data %>%
          select(subnum, choiceLeft,reactionTime) %>%
          rename(q=reactionTime, resp=choiceLeft) %>%
          mutate(resp = ifelse(resp == 1, "left", "right"),
                 data_type = "true")) %>%
  ggplot(aes(q, fill=data_type))+
  geom_density(alpha=.5, color=NA)+
  facet_grid(subnum~resp, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank())
```

# Model 1c: DDRL

- Boundary separation alpha fixed at 2  
- Bias beta fixed at .5 (no bias)
- NDT tau fixed at .1

```{r}
source(paste0(helpers_path,'ddrlModels/fit_ddrl_model1c.R'))
```

## Parameter estimates

```{r}
g_par_ests %>%
  ggplot(aes(value)) +
  geom_histogram(bins=30)+
  facet_wrap(~key, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank())
```

```{r}
par_ests %>%
  ggplot(aes(value)) +
  geom_histogram(bins=30)+
  facet_grid(subnum ~ par, scales="free")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        panel.grid = element_blank())
```

How do the learning rates and deltas from this model compare to the hierarchical rl with softmax as the choice rule?

```{r}

```


## Posterior predictive checks

```{r}
sub_par_ests = par_ests %>%
  group_by(subnum , par) %>%
  summarise(mean_val = mean(value), .groups="keep") %>%
  spread(par, mean_val)
```

```{r}
sim_data = data.frame()
for(i in 1:nrow(sub_par_ests)){
  
  # This will have to be for each trial bc the delta depends on the val difference in that trial
  # First generate the Q Values for all trials using the mean a posterior alpha for each subject
  
  # sim_sub_data = rwiener(n = 300, alpha = 2, tau = .1, beta = .5, delta = )
  # 
  # sim_sub_data$subnum = sub_par_ests_var$subnum[i]
  # if(i == 1){
  #   sim_data_var = sim_sub_data
  # } else{
  #   sim_data_var = rbind(sim_data_var, sim_sub_data)
  # }
}
```

Compare both choices and RTs

```{r fig.height=10}

```

