---
title: 'Experience vs. description based decision-making project: Raw behavioral findings'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

# Set up

```{r include=FALSE}
library(broom)
library(tidyverse)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
```

```{r}
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
```

```{r}
clean_beh_data = clean_beh_data %>%
  mutate(EVRight = referenceProb * referenceValue,
         EVLeft = lotteryValue * lotteryProb,
         conflictTrial = ifelse( (EVLeft<EVRight) & (fractalLeftProb>fractalRightProb), "conflict", ifelse( (EVLeft>EVRight) & (fractalLeftProb<fractalRightProb), "conflict", "no conflict")), #this puts all EVLeft == EVRight trials into the no conflict bin
         leftLotteryBetter = EVLeft-EVRight>0,
         leftFractalBetter = (fractalLeftProb)-(fractalRightProb)>0,
         lotteriesSame = EVLeft == EVRight,
         fractal_diff = abs(fractalLeftProb - fractalRightProb),
         lottery_ev_diff = round(abs(EVLeft - EVRight),3),
         lottery_ev_diff = ifelse(lottery_ev_diff ==0, "no EV diff", ifelse(lottery_ev_diff == .2, "small EV diff", ifelse(lottery_ev_diff == .4, "large EV diff", NA))),
         lottery_ev_diff = factor(lottery_ev_diff, levels=c("no EV diff", "small EV diff", "large EV diff"), labels = c("no", "small", "large")),
         choseBetterLotteryBundle = ifelse(leftLotteryBetter & choiceLeft == 1, 1, ifelse(!leftLotteryBetter & choiceLeft == 0, 1, 0)),
         choseBetterFractalBundle = ifelse(leftFractalBetter & choiceLeft == 1, 1, ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0)),
         leftBundleValue = (probFractalDraw*fractalLeftProb) + ((1-probFractalDraw)*EVLeft),
         rightBundleValue = (probFractalDraw * fractalRightProb) + ((1-probFractalDraw)*EVRight),
         leftBundleBetter = leftBundleValue > rightBundleValue,
         choseBetterOverallBundle = ifelse(leftBundleBetter & choiceLeft == 1, 1, ifelse(!leftBundleBetter & choiceLeft == 0, 1, 0)),
         logRt = log(reactionTime),
         probFractalDraw = as.factor(probFractalDraw))
```

# Reaction Time

## Attribute relevance

Distribution for each attribute relevance level. There is a difference in choice speed depending on attribute relevance.

```{r}
clean_beh_data %>%
  ggplot(aes(reactionTime))+
  geom_density(aes(fill=probFractalDraw), position = "identity", alpha=.5, color=NA)+
  scale_fill_brewer(palette="PRGn")
```

Decisions are slowest when both attributes are equally relevant. They are also categorically faster when only fractals matter for reward.

```{r}
clean_beh_data %>%
  group_by(probFractalDraw) %>%
  summarise(meanLogRt = mean(logRt),
            semLogRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, meanLogRt))+
  geom_point()+
  geom_errorbar(aes(ymin=meanLogRt - semLogRt, ymax=meanLogRt + semLogRt), width=.2)
```

Do we see this pattern for all subjects? Most but not all. Subjects 9 nd 10 look particularly weird.

```{r}
clean_beh_data %>%
  group_by(subnum, probFractalDraw) %>%
  summarise(.groups="keep",
            meanLogRt = mean(logRt),
            semLogRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, meanLogRt))+
  geom_point()+
  geom_errorbar(aes(ymin=meanLogRt - semLogRt, ymax=meanLogRt + semLogRt), width=.2)+
  facet_wrap(~subnum, scales="free_y")
```

Does RT depend on any other experimental manipulation?  

## True fractal values

Does it depend on the objective fractal values? Not on average but there are individual differences.

```{r}
clean_beh_data %>%
  select(subnum, reactionTime, fractalLeftProb, fractalRightProb, probFractalDraw) %>%
  gather(key, value, -subnum, -reactionTime, -probFractalDraw) %>%
  ggplot(aes(value, reactionTime))+
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "lm",se=FALSE, alpha=.1, size=1)+
  geom_smooth(formula = 'y~x', method = "lm")+
  facet_grid(key~probFractalDraw)
```

## EV of varying lottery

Does it depend on the amount or probability of the varying lottery? No. Not for anyone (or any probFractalDraw level; not shown).

```{r}
clean_beh_data %>%
  select(subnum, reactionTime, lotteryValue, lotteryProb) %>%
  gather(key, value, -subnum, -reactionTime) %>%
  ggplot(aes(value, reactionTime))+
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "lm",se=FALSE, alpha=.1, size=1)+
  geom_smooth(formula = 'y~x', method = "lm")+
  facet_wrap(~key, scales="free_x")
```

## Conflict trials

Does it depend on whether the objective values for each attribute agree or disagree on which is the better bundle? No.

```{r}
clean_beh_data %>%
  group_by(probFractalDraw, conflictTrial) %>%
  summarise(.groups="keep",
            meanLogRt = mean(logRt),
            semLogRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, meanLogRt, color=conflictTrial))+
  geom_point()+
  geom_errorbar(aes(ymin=meanLogRt - semLogRt, ymax=meanLogRt + semLogRt), width=.2)+
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

## Value difference

Choice is faster for larger differences between the lotteries *when* lotteries are more relevant for reward. Otherwise the effect disappears.

```{r}
clean_beh_data %>%
  group_by(probFractalDraw, lottery_ev_diff) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(lottery_ev_diff, mean_logRt))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  facet_wrap(~probFractalDraw)+
  xlab("Lottery EV difference")
```

Larger fractal value differences *does not* translate to faster choice. There are large individual differences but the average effects are either 0 or in the opposite direction.

Why not?  
Because subjects are not aware/have not learned the value difference?
Because information about the fractals has been processed before the stimulus presentation so the whatever effect fractal value difference might have had is dissipated when we begin measuring RT and the only stimulus processing that happens from that point on is about the lotteries and integration of bundle values?

```{r}
clean_beh_data %>%
  ggplot(aes(fractal_diff, logRt)) + 
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "lm",se=FALSE, alpha=.1, size=1)+
  geom_smooth(formula = 'y~x', method = "lm")+
  facet_grid(.~probFractalDraw)
```

On average there is no effect of the relative value differences on RT.

```{r}
clean_beh_data %>%
  ggplot(aes(fractal_diff, logRt)) + 
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "lm",se=FALSE, alpha=.1, size=1)+
  geom_smooth(formula = 'y~x', method = "lm")+
  facet_grid(lottery_ev_diff~probFractalDraw)
```

## Learning

Does it depend on trial number/learning how to do the task? Yes. Subjects get faster in later runs on average. In the first run they also get faster with each trial.

```{r}
clean_beh_data %>%
  ggplot(aes(trialNum, logRt))+
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "lm",se=FALSE, alpha=.1, size=1)+
  geom_smooth(formula = 'y~x', method = "lm")+
  facet_grid(.~session)
```

## Choice side

Are they faster when they choose left vs right? Since the learned attribute options are both fractals the stimulus difference lies in the lotteries. The bundle on the **right** has the fixed and the one on the right has the varying lottery. So left choices might be slower since they require more processing.

This doesn't seem to be the case overall.

```{r}
clean_beh_data %>%
  group_by(choiceLeft, probFractalDraw) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choiceLeft = ifelse(choiceLeft == 0, "right (varying Lottery)", "left (reference Lottery)")) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=choiceLeft))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

There isn't a difference between the lack of this effect depending on whether there is a conflict between the attributes.

```{r}
clean_beh_data %>%
  group_by(choiceLeft, probFractalDraw, conflictTrial) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choiceLeft = ifelse(choiceLeft == 0, "right (varying Lottery)", "left (reference Lottery)")) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=choiceLeft))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  theme(legend.position = "bottom",
        legend.title = element_blank())+
  facet_grid(conflictTrial~.)


```

## Choice based on lottery

When the lotteries don't have the same EV (80% of the trials) are subjects faster when they choose the bundle with the better lottery? Yes, when the lottery matters more for the reward. This suggests less/no integration of additional attribute (fractals) when correctly choosing based on the relevant attribute. Trials where the lotteries mattered more for the reward but the better lottery bundle was not selected could be considered "errors".

```{r}
clean_beh_data %>%
  filter(!lotteriesSame) %>%
  group_by(probFractalDraw, choseBetterLotteryBundle) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choseBetterLotteryBundle = as.factor(choseBetterLotteryBundle)) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=choseBetterLotteryBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  theme(legend.position = "bottom")
```
The effect is driven by different types of conflict trials at different levels of probFractalDraw.

```{r}
clean_beh_data %>%
  filter(!lotteriesSame) %>%
  group_by(probFractalDraw, choseBetterLotteryBundle, conflictTrial) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choseBetterLotteryBundle = as.factor(choseBetterLotteryBundle)) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=choseBetterLotteryBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  theme(legend.position = "bottom")+
  facet_grid(conflictTrial~.)
```
## Choice based on fractal

Are they faster when they choose the bundle with the better fractal? No systematic difference.  

```{r}
clean_beh_data %>%
  group_by(probFractalDraw, choseBetterFractalBundle) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choseBetterFractalBundle = as.factor(choseBetterFractalBundle)) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=choseBetterFractalBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2)+
  theme(legend.position = "bottom")
```

## RT patterns to model  

**Attribute relevance effects**   
- The more similar each attribute is in its relevance for reward the slower the choice.  
- When only the fractals matter choice is categorically faster.  

**Value difference effects**
- Choice is faster for larger EV difference when lotteries matter more for reward.   
- RT does NOT depend on fractal value difference, implying that when modeling RT this might not have to be taken into account.  

**Task learning effect**
- Subjects are on average faster the more trials they have done especially going from the first to the second run.  

**Choice effects**
- Subjects are slightly faster when they choose the bundle with the better lottery when the lottery matters more for the reward. This suggests less/no integration of additional attribute (fractals) when correctly choosing based on the relevant attribute. Trials where the lotteries mattered more for the reward but the better lottery bundle was not selected can be thought of as errors or choices in which the deliberation process was contaminated by the an irrelevant attribute (*opposite of a speed-accuracy tradeoff*).This effect is driven more by no conflict trials. There is no difference in RT for conflict trials depending on whether the bundle with the better lottery was chosen. Maybe the detection as a conflict draws attention/highlights the relevance of an attribute for a reward.  
- A similar effect does not exist for choosing the bundle with the better fractal when fractals are more relevant for reward. This might support the idea that processing of fractals happens before the stimuli are presented (/before we begin measuring RT).  

# Choice

**Analyzing choice without using any model-based measures**

## Side

Proportion of left choice by probFractalDraw for all subjects. No systematic idiosyncratic side bias.

```{r}
clean_beh_data %>%
  group_by(subnum, probFractalDraw, conflictTrial) %>%
  summarise(.groups = "keep",
            propLeft = sum(choiceLeft)/n()) %>%
  ggplot(aes(probFractalDraw, propLeft))+
  geom_boxplot()+
  # geom_jitter(height=0, width=.1, alpha=.5, aes(color=as.numeric(subnum)))+
  geom_hline(yintercept=.5, color="gray")+
  theme(legend.position = "none")+
  facet_grid(conflictTrial~.)
```

## Choice based on lottery

When the lotteries don't have the same EV do subjects choose the bundle with the better lottery? This should depend on how much the reward depends on the lotteries. Subject do choose the bundle with the better lottery more frequently when it matters for the reward. They appropriately choose it less frequently when the reward depends more on the fractals and the fractals suggest a different bundle to be the better one (conflict trials)

```{r}
clean_beh_data %>%
  filter(EVLeft != EVRight) %>%
  group_by(probFractalDraw, subnum, conflictTrial) %>%
  summarise(.groups="keep",
            prop_choseBetterLotteryBundle = mean(choseBetterLotteryBundle)) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterLotteryBundle))+
  geom_boxplot()+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~.)
  
```

Do they get better with time?  
- Some improvement for pFracDraw <=.5 especially from run 1 to run 2
- Even for pFracDraw <= .5 trials no conflict trials are slightly worse than conflict trials.
- For trials where fractals matter more for the reward (pFracDraw > .5) performance is worse in both types of conflict trials. In conflict trials the drop for choosing the bundle with the better lottery is not as sharp as it should be and in no conflict trials choice of bundle with better lottery is not as high even though it is also the bundle with the better fractal.  

```{r}
clean_beh_data %>%
  filter(EVLeft != EVRight) %>%
  mutate(session = paste0("run ", session)) %>%
  group_by(probFractalDraw, conflictTrial, session) %>%
  summarise(.groups="keep",
            prop_choseBetterLotteryBundle = mean(choseBetterLotteryBundle),
            sem_choseBetterLotteryBundle = sd(choseBetterLotteryBundle)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterLotteryBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = prop_choseBetterLotteryBundle-sem_choseBetterLotteryBundle,
                    ymax = prop_choseBetterLotteryBundle+sem_choseBetterLotteryBundle), width=.2)+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~session)+
  theme(legend.position = "none")
```

## Choice based on fractal

```{r}
clean_beh_data %>%
  # filter(EVLeft != EVRight) %>% #including these trials makes it the reciprocal of the above plot
  group_by(probFractalDraw, subnum, conflictTrial) %>%
  summarise(.groups="keep",
            prop_choseBetterFractalBundle = mean(choseBetterFractalBundle)) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterFractalBundle))+
  geom_boxplot()+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~.)
  
```

Do they get better with time?  
No new conclusions compared to the comparable graph above even when including trials with equal lottery EVs. Choice when the learned attribute matters for the reward is not as good as it is for when the described attribute (lotteries) matter more for the reward.

```{r}
clean_beh_data %>%
   mutate(session = paste0("run ", session)) %>%
  group_by(probFractalDraw, conflictTrial, session) %>%
  summarise(.groups="keep",
            prop_choseBetterFractalBundle = mean(choseBetterFractalBundle),
            sem_choseBetterFractalBundle = sd(choseBetterFractalBundle)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterFractalBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = prop_choseBetterFractalBundle-sem_choseBetterFractalBundle,
                    ymax = prop_choseBetterFractalBundle+sem_choseBetterFractalBundle), width=.2)+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~session)+
  theme(legend.position = "none")
```

## Choice based on bundle value

```{r}
clean_beh_data %>%
  group_by(probFractalDraw, subnum, conflictTrial) %>%
  summarise(.groups="keep",
            prop_choseBetterOverallBundle = mean(choseBetterOverallBundle)) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterOverallBundle))+
  geom_boxplot()+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~.)
  
```

```{r}
clean_beh_data %>%
   mutate(session = paste0("run ", session)) %>%
  group_by(probFractalDraw, conflictTrial, session) %>%
  summarise(.groups="keep",
            prop_choseBetterOverallBundle = mean(choseBetterOverallBundle),
            sem_choseBetterOverallBundle = sd(choseBetterOverallBundle)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, prop_choseBetterOverallBundle))+
  geom_point()+
  geom_errorbar(aes(ymin = prop_choseBetterOverallBundle-sem_choseBetterOverallBundle,
                    ymax = prop_choseBetterOverallBundle+sem_choseBetterOverallBundle), width=.2)+
  geom_hline(aes(yintercept=.5), color="grey")+
  facet_grid(conflictTrial~session)+
  theme(legend.position = "none")
```

## Logit analysis with true values 

```{r}
clean_beh_data %>%
  select(EVLeft, EVRight, fractalLeftProb, fractalRightProb, probFractalDraw, choiceLeft) %>%
  mutate(EVDiff = scale(EVLeft - EVRight), 
         fractalDiff = scale(fractalLeftProb - fractalRightProb)) %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ EVDiff + fractalDiff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error) %>%
  ggplot(aes(probFractalDraw, estimate, col=term, group=term))+
      geom_point()+
      geom_line()+
      geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
      geom_hline(aes(yintercept=0), linetype="dashed")+
      scale_color_manual(values = cbbPalette[2:1])+
      theme(legend.position = "bottom")+
      labs(color="", title="Relevant attribute effect on choice")
```

Individual differences in this pattern are very large. The pattern doesn't really exist clearly for any subject.

```{r warning=FALSE, message=FALSE}
tmp = clean_beh_data %>%
  select(subnum, EVLeft, EVRight, fractalLeftProb, fractalRightProb, probFractalDraw, choiceLeft) %>%
  mutate(EVDiff = scale(EVLeft - EVRight), 
         fractalDiff = scale(fractalLeftProb - fractalRightProb)) %>%
  nest(data = -c(probFractalDraw, subnum)) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ EVDiff + fractalDiff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(subnum, probFractalDraw, term, estimate, std.error)
```

```{r warning=FALSE, message=FALSE}
tmp %>% ggplot(aes(probFractalDraw, estimate, col=term, group=term))+
      geom_point()+
      geom_line()+
      geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
      geom_hline(aes(yintercept=0), linetype="dashed")+
      scale_color_manual(values = cbbPalette[2:1])+
      theme(legend.position = "none")+
      labs(color="") +
  facet_wrap(~subnum, scales="free")+
  ylim(-5, 5)
```

## Perseverance of choice 

are they more likely to choose the rewarded side
rewarded how? trial reward or fractal reward?

fractal draw vs lottery draw
X
reward vs no reward
X
leftFrac rewarded, leftFrac not rewarded
X
rightFrac rewarded, rightFrac not rewarded

No difference in perseverance depending on whether the trial was rewarded exxcept for 3/20 cases.  
When lottery 

```{r}
clean_beh_data %>%
  select(subnum, trialNum, choiceLeft, reward, fractalDraw, probFractalDraw) %>%
  group_by(subnum) %>% # so the last choice for one subject does not bleed into the first choice of the next subject
  mutate(lastChoiceSide = lag(choiceLeft),
         lastFractalDraw = lag(fractalDraw),
         choseLastSide = choiceLeft == lastChoiceSide,
         rewarded = reward > 0) %>%
  filter(trialNum > 1) %>% #remove first trial of each run
  ungroup()%>%
  group_by(lastFractalDraw, rewarded, probFractalDraw) %>%
  summarise(.groups='keep',
            prop_choseLastSide = mean(choseLastSide, na.rm=T),
            sem_choseLastSide = sd(choseLastSide, na.rm=T)/sqrt(n())) %>%
  mutate(lastRewardAttribute = ifelse(lastFractalDraw == 1, "fractal", "lottery")) %>%  
  ggplot(aes(probFractalDraw, prop_choseLastSide, color=lastRewardAttribute))+
  geom_point(position = position_dodge(width=.5))+
  geom_errorbar(aes(ymin=prop_choseLastSide-sem_choseLastSide, ymax=prop_choseLastSide+sem_choseLastSide), width=.2, position=position_dodge(width=.5))+
  geom_hline(aes(yintercept=.5), color="gray")+
  facet_grid(rewarded~.)+
  theme(legend.position = "bottom")
  
```

longest streak of the same side

```{r}
clean_beh_data %>%
  select(subnum, trialNum, choiceLeft, reward, fractalDraw, probFractalDraw) %>%
  group_by(subnum) %>% # so the last choice for one subject does not bleed into the first choice of the next subject
  mutate(lastChoiceSide = lag(choiceLeft),
         choseLastSide = choiceLeft == lastChoiceSide,
         diffChoseLastSide = c(NA,diff(choseLastSide))) %>%
  filter(trialNum > 1)
```

## Learning of fractal values

what do the drifting reward probabilities look like
is there a good signal to learn?

should I model "learning" for the whole task?

```{r}
clean_beh_data %>%
  group_by(subnum) %>%
  mutate(trialNum = 1:n()) %>%
  select(fractalLeftProb, fractalRightProb, trialNum, subnum) %>%
  gather(key, value, -trialNum, -subnum) %>%
  ggplot(aes(trialNum, value, color=key))+
  geom_line()+
  geom_vline(xintercept=60, color="gray")+
  geom_vline(xintercept=120, color="gray")+
  geom_vline(xintercept=180, color="gray")+
  geom_vline(xintercept=240, color="gray")+
  facet_wrap(~subnum)+
  theme(legend.position = "bottom",
        legend.title=element_blank())


```


## Differential learning 

more learning for rewarded side or chosen bundle fractal?

## Choice patterns to model

- Better performance for trials where the lotteries matter more for the reward.
- Asymmetric distortion of attribute relevance: Lottery slopes decline linearly but fractal slopes have a more step-like shape.
- 
