---
title: 'Experience vs. description based decision-making project: Figure for Arrowhead poster'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---



```{r include=FALSE}
library(broom)
library(tidyverse)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
fig_out_path = paste0(here(), '/outputs/fig/')
theme_set(theme_bw())
```

```{r}
clean_beh_data = clean_beh_data %>%
  mutate(EVRight = referenceProb * referenceValue,
         EVLeft = lotteryValue * lotteryProb,
         conflictTrial = ifelse( (EVLeft<EVRight) & (fractalLeftProb>fractalRightProb), "conflict", ifelse( (EVLeft>EVRight) & (fractalLeftProb<fractalRightProb), "conflict", "no conflict")), #this puts all EVLeft == EVRight trials into the no conflict bin
         leftLotteryBetter = EVLeft-EVRight>0,
         leftFractalBetter = (fractalLeftProb)-(fractalRightProb)>0,
         lotteriesSame = EVLeft == EVRight,
         fractal_diff = abs(fractalLeftProb - fractalRightProb),
         lottery_ev_diff = round(abs(EVLeft - EVRight),3),
         lottery_ev_diff = ifelse(lottery_ev_diff ==0, "no EV diff", ifelse(lottery_ev_diff == .2, "small EV diff", ifelse(lottery_ev_diff == .4, "large EV diff", NA))),
         lottery_ev_diff = factor(lottery_ev_diff, levels=c("no EV diff", "small EV diff", "large EV diff"), labels = c("no", "small", "large")),
         choseBetterLotteryBundle = ifelse(leftLotteryBetter & choiceLeft == 1, 1, ifelse(!leftLotteryBetter & choiceLeft == 0, 1, 0)),
         choseBetterFractalBundle = ifelse(leftFractalBetter & choiceLeft == 1, 1, ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0)),
         leftBundleValue = (probFractalDraw*fractalLeftProb) + ((1-probFractalDraw)*EVLeft),
         rightBundleValue = (probFractalDraw * fractalRightProb) + ((1-probFractalDraw)*EVRight),
         leftBundleBetter = leftBundleValue > rightBundleValue,
         choseBetterOverallBundle = ifelse(leftBundleBetter & choiceLeft == 1, 1, ifelse(!leftBundleBetter & choiceLeft == 0, 1, 0)),
         logRt = log(reactionTime),
         probFractalDraw = as.factor(probFractalDraw))
```

```{r message=FALSE}
# model_name = 'fit_rl_hierarchical_oneParamSymmNonLinearProbDistortion_rpeBoth.R'
# source(paste0(helpers_path, 'rlModels/', model_name))

source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamDoubleSymmLinearProbDistortion_rpeBoth.R'))
```

```{r}
source(paste0(helpers_path, 'get_qvals.R'))

# Add mean posterior estimates to clean_beh_data
clean_beh_data = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data = clean_beh_data %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="original")) %>%
  ungroup() %>%
  mutate(EVDiff = scale(EVLeft - EVRight),
         QVDiff = scale(leftQValue - rightQValue),
         fractalDiff = scale(fractalLeftProb - fractalRightProb))
```

# Attribute logits

```{r}
tmp1 = clean_beh_data %>%
   nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ EVDiff + fractalDiff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error) %>%
  mutate(model = "m1")

tmp2 = clean_beh_data %>%
   nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ EVDiff + QVDiff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error) %>%
  mutate(model = "m2")

p = tmp2 %>%
rbind(tmp1 %>% filter(term == "fractalDiff")) %>%
  mutate(term = ifelse(term == "EVDiff", "Lottery EV difference", ifelse(term == "fractalDiff", "True fractal difference", "Learned QV difference")),
         term = factor(term, levels = c("True fractal difference", "Lottery EV difference", "Learned QV difference"))) %>%
  ggplot(aes(probFractalDraw, estimate, col=term, group=term))+
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2,size=3)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[1:3] )+
  labs(color="", y="Logit slope estimate", x="p(Fractal)")+  
  theme(legend.position = c(.7,.88),
        legend.background = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=20))


ggsave(file=paste0(fig_out_path, 'poster_group_logit.jpg'), p, height = 5, width=8, units="in")
p
```

# RL model comparison

```{r}
sampled_logLiks = readRDS('~/Downloads/sampled_logLiks.RDS')

tmp = sampled_logLiks %>%
  group_by(model_name) %>%
  summarise(sem_logLik = sd(logLik)/sqrt(n()),
            mean_logLik = mean(logLik),
            numpar = unique(numpar),
            symm = unique(symm),
            shape = unique(shape),
            rpe = unique(rpe)) %>%
  mutate(model_name = as.factor(model_name),
         model_name = reorder(model_name, mean_logLik))

p = tmp %>%
  ggplot(aes(model_name, mean_logLik, col=rpe, shape = symm, alpha = shape))+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=mean_logLik - sem_logLik, ymax=mean_logLik + sem_logLik, linetype=numpar),size=2)+
  labs(x="Model", y="Mean Log likelihood")+
  scale_alpha_manual(values=c(.6, 1), name="",
                     breaks = c("LinearProbDistortion", "NonLinearProbDistortion"),
                     labels = c("Linear", "NonLinear"))+
  scale_shape_manual(values = c(16, 17), name="")+
  scale_color_manual(breaks=c("_rpeBoth", "_rpeChosenBundleFractal", "_rpeWhenFractalRewarded"),
                     labels=c("Both", "Chosen", "Rewarded"),
                     name="",
                     values=c(cbbPalette[5], cbbPalette[3], cbbPalette[7]))+
  scale_linetype_manual(values = c("solid", "dashed"), name="")+
  theme(legend.position = "bottom",
        legend.background = element_blank(),
        legend.box = "vertical",
        panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.title = element_text(size=24),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.title.y = element_text(margin = margin(t = 0, r = 25, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 25, r = 0, b = 0, l = 0)))

#grab legend before removing it
legend <- cowplot::get_legend(p)

p =p + theme(legend.position = "none")
p
ggsave(file=paste0(fig_out_path, 'poster_rl_model_comparison.jpg'), p, height = 5, width=8, units="in")

grid::grid.newpage()
grid::grid.draw(legend)

```

# RT by value difference

```{r}
p = clean_beh_data %>%
  group_by(probFractalDraw, lottery_ev_diff) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, mean_logRt,color=lottery_ev_diff))+
  geom_point(position=position_dodge(width=.5), size=3)+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=0,position=position_dodge(width=.5), size=2)+
  labs(color="Lottery EV difference", y="Mean Log RT", x="p(Fractal)")+
  scale_color_manual(values = c(cbbPalette[3], cbbPalette[5:6]))+
   theme(legend.position = c(.34,.2),
        legend.background = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20))+
  guides(color=guide_legend(nrow=1))+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.36, .36))
  

ggsave(file=paste0(fig_out_path, 'poster_rt_by_lottery_ev_diff.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
tmp = clean_beh_data %>%
  group_by(subnum) %>%
  # mutate(diff_level = ifelse(QVDiff < quantile(QVDiff, probs=c(.33))[[1]], "small",
  #                                   ifelse(QVDiff > quantile(QVDiff, probs=c(.66))[[1]], "large", "medium")),
  #        diff_level = factor(diff_level, levels=c("small", "medium", "large"))) %>%
  mutate(fractal_qv_diff = abs(leftQValue - rightQValue),
         fractal_qv_diff = ifelse(fractal_qv_diff < quantile(fractal_qv_diff, probs=c(.33))[[1]], "small",
                                    ifelse(fractal_qv_diff > quantile(fractal_qv_diff, probs=c(.66))[[1]], "large", "medium")),
         diff_level = factor(fractal_qv_diff, levels=c("small", "medium", "large"))) %>%
  ungroup() %>%
  group_by(probFractalDraw, diff_level) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(diff_type = "Learned Q-Values")

tmp2 = clean_beh_data %>%
  mutate(diff_level = ifelse(lottery_ev_diff == "no", "small", ifelse(lottery_ev_diff == "small", "medium", "large")),
         diff_level = factor(diff_level, levels=c("small", "medium", "large")))%>%
  group_by(probFractalDraw, diff_level) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(diff_type = "Lottery EVs")

p = clean_beh_data %>%
  group_by(subnum) %>%
  mutate(fractal_prob_diff = abs(fractalLeftProb - fractalRightProb),
         diff_level = ifelse(fractal_prob_diff < quantile(fractal_prob_diff, probs=c(.33))[[1]], "small",
                                    ifelse(fractal_prob_diff > quantile(fractal_prob_diff, probs=c(.66))[[1]], "large", "medium")),
         diff_level = factor(diff_level, levels=c("small", "medium", "large"))) %>%
  ungroup() %>%
  group_by(probFractalDraw, diff_level) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(diff_type="True Fractal Values") %>%
  rbind(tmp) %>%
  rbind(tmp2) %>%
  mutate(diff_type = factor(diff_type, levels = c("Lottery EVs", "True Fractal Values", "Learned Q-Values"))) %>%
  ggplot(aes(probFractalDraw, mean_logRt,color=diff_level))+
  geom_point(position=position_dodge(width=.5), size=3)+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=0,position=position_dodge(width=.5), size=2)+
  labs(color="Difference Level", y="Mean Log RT", x="p(Fractal)")+
  scale_color_manual(values = c(cbbPalette[3], cbbPalette[5:6]))+
   theme(legend.position = "bottom",
        legend.background = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20),
        strip.text = element_text(size=20))+
  guides(color=guide_legend(nrow=1), alpha=guide_legend(nrow=1))+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.36, .36))+
  facet_wrap(~diff_type, nrow=3)

ggsave(file=paste0(fig_out_path, 'poster_rt_by_value_diff_corrected_GROUPED.jpg'), p, height = 15, width=8, units="in")
p
```
# Error RTs

```{r}
p = clean_beh_data %>%
  filter(!lotteriesSame) %>%
  group_by(probFractalDraw, choseBetterLotteryBundle) %>%
  summarise(.groups="keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  mutate(choseBetterLotteryBundle = ifelse(choseBetterLotteryBundle ==1, "TRUE", "FALSE"),
         basedOn = "Lottery EV") %>%
  rename(betterChoice = choseBetterLotteryBundle) %>%
  rbind(clean_beh_data %>%
          mutate(leftQVBetter = (leftQValue)-(rightQValue)>0,
                 choseBetterQVBundle = ifelse(leftFractalBetter & choiceLeft == 1, 1, ifelse(!leftFractalBetter & choiceLeft == 0, 1, 0))) %>%
          group_by(probFractalDraw, choseBetterQVBundle) %>%
          summarise(.groups="keep",
                    mean_logRt = mean(logRt),
                    sem_logRt = sd(logRt)/sqrt(n())) %>%
          mutate(choseBetterQVBundle = ifelse(choseBetterQVBundle ==1, "TRUE", "FALSE"),
                 basedOn = "Fractal QV") %>%
          rename(betterChoice = choseBetterQVBundle)) %>%
  ggplot(aes(probFractalDraw, mean_logRt, shape=betterChoice, color=basedOn, group=basedOn))+
  geom_point( position = position_dodge(width = .5), size=3)+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2, size=1.5, position = position_dodge(width = .5))+
  theme(legend.position = c(.34,.3),
        legend.background = element_blank(),
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20))+
  guides(color=guide_legend(nrow=1), shape=guide_legend(nrow=1))+
  labs(x="p(Fractal)", y = "Mean log RT", color="Based On", shape="Better Choice")+
  scale_color_manual(values = cbbPalette[1:2])+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.36, .36))

ggsave(file=paste0(fig_out_path, 'poster_rt_by_better_choice.jpg'), p, height = 5, width=8, units="in")
p
```

# DDM demo figures

3 integrators all with their own drift and noise rates
Arbitrator integrator starts biased towards lotteries
If pFractalDraw == 1 fractal integrator (not the arbitrator) starts biased towards the better fractal
Attribute relevance (pFractalDraw) affects attribute integrators directly, not the arbitrator
Arbitrator depends on the difference in absolute attribute integrator RDVs

```{r}
rdv = .25
rt = 200
d = .003
s = .08
out = data.frame(rdv = c(rdv, rep(NA, rt-1)))
for(i in 1:(rt-1)){
  change = rnorm(n = 1, mean=d, sd = s)
  out$rdv[i+1] = out$rdv[i]+change
  if(abs(out$rdv[i+1])>1){
    break
  }
}

p = out %>%
  drop_na() %>%
  mutate(step = 1:n()) %>%
  ggplot(aes(step, rdv))+
  geom_line(group=1, size=2) +
  geom_hline(aes(yintercept=max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=(-1)*max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  # theme_classic()+
  ylim(-1*max(out$rdv), max(out$rdv))+
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())+
  labs(x="", y="")

p
# ggsave(file=paste0(fig_out_path, 'poster_arbitrator_integrator.jpg'), p, height = 5, width=8, units="in")

```

```{r}
rdv = 0
rt = 200
d = -.003
s = .08
out = data.frame(rdv = c(rdv, rep(NA, rt-1)))
for(i in 1:(rt-1)){
  change = rnorm(n = 1, mean=d, sd = s)
  out$rdv[i+1] = out$rdv[i]+change
  if(abs(out$rdv[i+1])>1){
    break
  }
}
p=out %>%
  drop_na() %>%
  filter(abs(rdv) < .75) %>%
  mutate(step = 1:n()) %>%
  ggplot(aes(step, rdv))+
  geom_line(group=1, size=2, color=cbbPalette[1]) +
  geom_hline(aes(yintercept=max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=(-1)*max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  # theme_classic()+
  ylim(-1*max(out$rdv), max(out$rdv))+
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),)+
  labs(x="", y="")

p
# ggsave(file=paste0(fig_out_path, 'poster_fractal_integrator.jpg'), p, height = 5, width=8, units="in")
```

```{r}
rdv = 0
rt = 200
d = .003
s = .08
out = data.frame(rdv = c(rdv, rep(NA, rt-1)))
for(i in 1:(rt-1)){
  change = rnorm(n = 1, mean=d, sd = s)
  out$rdv[i+1] = out$rdv[i]+change
  if(abs(out$rdv[i+1])>1){
    break
  }
}
p=out %>%
  drop_na() %>%
  filter(rdv < .85) %>%
  mutate(step = 1:n()) %>%
  ggplot(aes(step, rdv))+
  geom_line(group=1, size=2, color=cbbPalette[2]) +
  geom_hline(aes(yintercept=max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=(-1)*max(abs(out$rdv), na.rm=T)))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  # theme_classic()+
  ylim(-1*max(out$rdv), max(out$rdv))+
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),)+
  labs(x="", y="")

p
ggsave(file=paste0(fig_out_path, 'poster_lottery_integrator.jpg'), p, height = 5, width=8, units="in")
```
