---
title: 'Experience vs. description based decision-making project: Revisiting DD models'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))

fig_out_path = paste0(here(), '/outputs/fig/')

set.seed(38573)
```

Add distorted value estimates using the hierarchical RL fit.

```{r message=FALSE, warning=FALSE}
# See NB19_RevisitingRLModels.Rmd before deciding on which model to import
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamAsymmLinearProbDistortion_rpeBoth.R'))
# source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamSymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data = clean_beh_data %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data = clean_beh_data %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-probFractalDraw)*lottery_ev_diff, #Asymm distortion
         # distorted_ev_diff = (1 - (theta*probFractalDraw))*lottery_ev_diff, #Not normalized Symm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)

rm(fit, g_par_ests, par_ests)
```

# RT effects to explain

```{r}
# Extract set of stimuli that will be used for simulations
sub_data = clean_beh_data %>%
  # filter(subnum  %in% c("01", "03", "05","07", "09", "11", "13", "15", "17", "19")) %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
```

```{r}
sim_sanity_checks(sub_data, checks=c(1,3,4,5,6,7,8), compare_logits = F, compare_rts = F)
```

## Slow errors check

```{r}
m_data = sub_data %>%
  filter(probFractalDraw != .5) %>%
  mutate(choice = ifelse(choiceLeft == 1, "left", "right"),
         leftLotterySubjBetter = distortedEVDiff > 0,
         leftFractSubjBetter = distortedQVDiff > 0,
         choseBetterSubjLott = ifelse(choice == "left" & leftLotterySubjBetter, "correct", ifelse(choice == "right" & !leftLotterySubjBetter, "correct", "incorrect")),
         choseBetterSubjFrac = ifelse(choice == "left" & leftFractSubjBetter, "correct", ifelse(choice == "right" & !leftFractSubjBetter, "correct", "incorrect")),
         logRt = log(reactionTime),
         fractalMoreRelevant = ifelse(probFractalDraw > .5, "fractal more relevant", "lottery more relevant"),
         fractalMoreRelevant = factor(fractalMoreRelevant, levels=c("lottery more relevant", "fractal more relevant"))) %>%
  select(fractalMoreRelevant, choseBetterSubjLott, choseBetterSubjFrac, logRt, subnum) %>%
        gather(key, value, -fractalMoreRelevant, -logRt, -subnum)
```

Two models for each panel

```{r}
m1 = lme4::lmer(logRt ~ fractalMoreRelevant * value + (1|subnum), data=m_data %>% filter(key == "choseBetterSubjLott"))
m2 = lme4::lmer(logRt ~ fractalMoreRelevant * value + (1|subnum), data=m_data %>% filter(key == "choseBetterSubjFrac"))
```

```{r}
summary(m1)
```

```{r}
summary(m2)
```

Single model looking only on choice based on relevant attribute

```{r}
sm_data = rbind(m_data %>%
        filter(fractalMoreRelevant == "fractal more relevant" & key == "choseBetterSubjFrac"),
      m_data %>%
        filter(fractalMoreRelevant == "lottery more relevant" & key == "choseBetterSubjLott"))

m3 = lme4::lmer(logRt ~ value + (1|subnum), data=sm_data)

summary(m3)
```

# DD Models

## One integrator

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
```

```{r}
sim_trial_list = list()
sim_trial_list[['model1']] = sim_trial
```

### Demo

```{r}
m1 = sim_task(sub_data, model_name = "model1", d=0.04, sigma = 0.06)
```

```{r}
sim_sanity_checks(m1, checks=c(1,3,4), compare_logits = TRUE)
```

## One integrator with early integration

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion_earlyIntegration.R'))
sim_trial_list = list()
sim_trial_list[['model1a']] = sim_trial
```

### Demo

```{r}
m1a = sim_task(sub_data, model_name = "model1a", d=0.032, sigma = 0.062, stimDelay = 180)
sim_sanity_checks(m1a, checks=c(1,3,4,5), compare_logits = TRUE)
```


```{r}
sub_data %>%
  filter(probFractalDraw == 1)
```

## Two integrators

### Demo

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_twoIntegrators_sepProbDistortion.R'))
sim_trial_list = list()
sim_trial_list[['model2']] = sim_trial
```

```{r}
# m2 = sim_task(sub_data, model_name = "model2", dLott=0.03, dFrac=0.06, sigmaLott = 0.03, sigmaFrac = 0.06) #nice rt patterns
# m2_rt = sim_task(sub_data, model_name = "model2", dLott=0.032, dFrac=0.068, sigmaLott = 0.03, sigmaFrac = 0.06)
# note that this parameter setting suggest slow but precise value integration for the lotteries versus fast but noisy value integration for the fractals
# sim_sanity_checks(m2_rt, checks=c(1,4,5), compare_logits = TRUE)
```

```{r}
# m2_lg = sim_task(sub_data, model_name = "model2", dLott=0.02, dFrac=0.03, sigmaLott = 0.06, sigmaFrac = 0.06)
# sim_sanity_checks(m2_lg, checks=c(1,4,5), compare_logits = TRUE)
```

```{r}
m2_11 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.022, sigmaLott = 0.06, sigmaFrac = 0.06)
```

```{r}
m2_12 = sim_task(sub_data, model_name = "model2", dLott=0.044, dFrac=0.022, sigmaLott = 0.06, sigmaFrac = 0.06)
```

```{r}
m2_13 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.044, sigmaLott = 0.06, sigmaFrac = 0.06)
```
 
```{r}
m2_21 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.022, sigmaLott = 0.06, sigmaFrac = 0.08)
```

```{r}
m2_22 = sim_task(sub_data, model_name = "model2", dLott=0.044, dFrac=0.022, sigmaLott = 0.06, sigmaFrac = 0.08)
```

```{r}
m2_23 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.044, sigmaLott = 0.06, sigmaFrac = 0.08)
```

```{r}
m2_31 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.022, sigmaLott = 0.08, sigmaFrac = 0.06)
```

```{r}
m2_32 = sim_task(sub_data, model_name = "model2", dLott=0.044, dFrac=0.022, sigmaLott = 0.08, sigmaFrac = 0.06)
```

```{r}
m2_33 = sim_task(sub_data, model_name = "model2", dLott=0.022, dFrac=0.044, sigmaLott = 0.08, sigmaFrac = 0.06)
```


```{r}
datasets = list(m2_11, m2_12, m2_13, m2_21, m2_22, m2_23, m2_31, m2_32, m2_33)

rt_plots = list()
logit_plots = list()

for(i in 1:length(datasets)){
  cur_data = datasets[[i]]
  cur_dFrac = unique(cur_data$dFrac)
  cur_dLott = unique(cur_data$dLott)
  cur_sigmaFrac = unique(cur_data$sigmaFrac)
  cur_sigmaLott = unique(cur_data$sigmaLott)
  
  annot = paste0("dFrac = ", cur_dFrac, ", dLott = ", cur_dLott,
                   "\nsigmaFrac = ", cur_sigmaFrac,", sigmaLott = ", cur_sigmaLott)

  cur_plots = sim_sanity_checks(cur_data, checks=c(4,5), return_plot = T, logit_facets = F, compare_logits = T)
  
  rt_plots[[i]] = cur_plots[[1]]+labs(title=annot)+theme(title = element_text(size=9), legend.position = "none")
  
  logit_plots[[i]] = cur_plots[[2]]+labs(title=annot)+theme(title = element_text(size=9), legend.position = "none")
  
}


```

```{r}
g = gridExtra::marrangeGrob(grobs = rt_plots, nrow=3, ncol=3, top="")
ggsave(file=paste0(fig_out_path, 'twoIntDemoRtPlots.png'), g, height = 8, width=11, units="in")

g = gridExtra::marrangeGrob(grobs = logit_plots, nrow=3, ncol=3, top="")
ggsave(file=paste0(fig_out_path, 'twoIntDemoLogitPlots.png'), g, height = 8, width=11, units="in")
```

Test fitting function

```{r}
test_trial = sim_trial(dLott=0.03, dFrac=0.05, sigmaLott = 0.03, sigmaFrac = 0.06, distortedEVDiff = .8, distortedQVDiff = 0, EVLeft = NA, QVLeft = NA, EVRight = NA, QVRight = NA, probFractalDraw=NA, debug=T)

test_trial$debug_df %>%
  select(-barrier) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  geom_line()+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_hline(aes(yintercept=-1))+
  theme(legend.position = "bottom",
        panel.grid = element_blank())+
  labs(color="", y = "RDV")
```

```{r}
fit_test_trial = fit_trial(dLott=0.03, dFrac=0.05, sigmaLott = 0.03, sigmaFrac = 0.06, distortedEVDiff = .8, distortedQVDiff = 0, choice = test_trial$out$choice, reactionTime = test_trial$out$reactionTime, EVLeft = NA, QVLeft = NA, EVRight = NA, QVRight = NA, probFractalDraw=NA, debug=T)

fit_test_trial$prStatesLott %>%
  mutate(state = 1:n()) %>%
  gather(time, prob, -state) %>%
  ggplot(aes(time, state, fill=prob))+
  geom_tile()

fit_test_trial$prStatesFrac %>%
  mutate(state = 1:n()) %>%
  gather(time, prob, -state) %>%
  ggplot(aes(time, state, fill=prob))+
  geom_tile()

fit_test_trial$out
```

## Three integrators

Potentially unnecessarily complicated and did not survive any identifiability analyses even when fixing noise parameters

### Demo

Simulate data with a 3 integrator model using half the stimuli filtered earlier and this three integrator model.

**Note: this selection of parameters provides a nice qualitative fit to data. It assumes integration is slower for lotteries than for fractals. This is one way of capturing the difference in processing lottery values, which can only be done after the stimulus presentation, as apposed to fractal values which are learned about trialwise. There are alternative ways of modeling this: e.g. integration for the fractal integrator might start before the stimulus presentation screen; ndt for the lottery integrator (or the arbitrator when the lottery is more relevant) might be longer etc. The way to determine which of these hypotheses is most supported by data would be a model comparison.**

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_threeIntegrators_sepProbDistortion.R'))
sim_trial_list[["model3"]] = sim_trial
```

```{r}
# m3_1 = sim_task(sub_data, model_name = "model3", dLott=0.03, dFrac=0.06, dArb=0.05, sigmaLott = 0.03, sigmaFrac = 0.03)
m3_1 = sim_task(sub_data, model_name = "model3", dLott=0.03, dFrac=0.06, dArb=0.07, sigmaLott = 0.03, sigmaFrac = 0.03)
```

```{r}
sim_sanity_checks(m3_1, checks=c(1,3,4,5,6,7,8), compare_logits = TRUE)
```




