---
title: 'Experience vs. description based decision-making project: Figures for 7/8 lab meeting'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(broom)
library(tidyverse)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
fig_out_path = paste0(here(), '/outputs/fig/')
theme_set(theme_bw())
```

Logit w EV and fractal value

```{r}

```

Logit w EV, fractal value and QV

```{r}

```

Logit w EV, fractal value, QV and prob distortion correction

```{r}

```

RL model comparison

```{r}

```

RT by probFractalDraw

```{r}

```

RT by probfractaldraw split by EV difference level

```{r}

```

RT by probfractaldraw split by QV difference level

```{r}

```

RT for errors

```{r}

```

Demo 1 integrator DDM

```{r}

```

Demo 3 integrator DDM

```{r}

```

Distorted EV vs distorted QV (caveat trials)

```{r}

```

Simulation/fit checks

```{r}

```