---
title: 'Experience vs. description based decision-making project: Figures for 7/8 lab meeting'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
library(broom)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
fig_out_path = paste0(here(), '/outputs/fig/')

set.seed(38573)
```


# Choice

## Logit w EV and fractal value

Add distorted value estimates using the hierarchical RL fit.

```{r message=FALSE, warning=FALSE}

source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamDoubleSymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data = clean_beh_data %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="original")) %>%
  ungroup()

clean_beh_data = clean_beh_data %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-theta)*(1-probFractalDraw)*lottery_ev_diff,
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)

rm(fit, g_par_est, par_ests)
```

```{r}
truev_mod = clean_beh_data %>%
  mutate(probFractalDraw = as.factor(probFractalDraw),
         fractal_prob_diff = fractalLeftProb - fractalRightProb) %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ scale(lottery_ev_diff) + scale(fractal_prob_diff), data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error)

qv_mod = clean_beh_data %>%
  mutate(probFractalDraw = as.factor(probFractalDraw)) %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ scale(lottery_ev_diff) + scale(fractal_qv_diff), data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term == "scale(fractal_qv_diff)") %>%
  select(probFractalDraw, term, estimate, std.error)

qv_theta_mod = clean_beh_data %>%
  mutate(probFractalDraw = as.factor(probFractalDraw),
         fractal_qv_diff_theta = fractal_qv_diff * theta,
         lottery_ev_diff_theta = lottery_ev_diff * (1-theta)) %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ scale(lottery_ev_diff_theta) + scale(fractal_qv_diff_theta), data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error)
```

```{r}
p = rbind(truev_mod, qv_mod) %>%
  mutate(reg = ifelse(term %in% c("scale(lottery_ev_diff)", "scale(lottery_ev_diff_theta)"), "Lottery EV", ifelse(term == "scale(fractal_prob_diff)", "True Fractal P", ifelse(term %in% c("scale(fractal_qv_diff)","scale(fractal_qv_diff_theta)"),"Fractal QV", NA))),
         reg = factor(reg, levels=c("True Fractal P", "Lottery EV", "Fractal QV")),
         theta = grepl("theta", term),
         fract = ifelse(reg == "Fractal QV", T, F)) %>%
  ggplot(aes(probFractalDraw, estimate, col=reg, group=reg, alpha = fract))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[1:3])+
  scale_alpha_manual(values = c(1, 0), guide="none")+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  labs(color="", x= "p(Fractal)", y="Beta estimate")+
  guides(color=guide_legend(nrow=2,byrow=TRUE))

ggsave(file=paste0(fig_out_path, 'labmeet_logit_build1.jpg'), p, height = 5, width=8, units="in")
p
```

## Logit w EV, fractal value and QV

```{r}
p = rbind(truev_mod, qv_mod) %>%
  mutate(reg = ifelse(term %in% c("scale(lottery_ev_diff)", "scale(lottery_ev_diff_theta)"), "Lottery EV", ifelse(term == "scale(fractal_prob_diff)", "True Fractal P", ifelse(term %in% c("scale(fractal_qv_diff)","scale(fractal_qv_diff_theta)"),"Fractal QV", NA))),
         reg = factor(reg, levels=c("True Fractal P", "Lottery EV", "Fractal QV")),
         theta = grepl("theta", term),
         fract = ifelse(reg == "Fractal QV", T, F)) %>%
  ggplot(aes(probFractalDraw, estimate, col=reg, group=reg))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[1:3])+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  labs(color="", x= "p(Fractal)", y="Beta estimate")+
  guides(color=guide_legend(nrow=2,byrow=TRUE))

ggsave(file=paste0(fig_out_path, 'labmeet_logit_build2.jpg'), p, height = 5, width=8, units="in")
p
```

## Logit w EV, fractal value, QV and prob distortion correction

```{r}
p = rbind(truev_mod, qv_mod, qv_theta_mod) %>%
  mutate(reg = ifelse(term %in% c("scale(lottery_ev_diff)", "scale(lottery_ev_diff_theta)"), "Lottery EV", ifelse(term == "scale(fractal_prob_diff)", "True Fractal P", ifelse(term %in% c("scale(fractal_qv_diff)","scale(fractal_qv_diff_theta)"),"Fractal QV", NA))),
         reg = factor(reg, levels=c("True Fractal P", "Lottery EV", "Fractal QV")),
         theta = grepl("theta", term),
         fract = ifelse(reg == "Fractal QV", T, F)) %>%
  ggplot(aes(probFractalDraw, estimate, col=reg, group=term, alpha = theta))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[1:3])+
  scale_alpha_manual(values = c(.3, 1))+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  labs(color="", x= "p(Fractal)", y="Beta estimate")+
  guides(color=guide_legend(nrow=2,byrow=TRUE))

ggsave(file=paste0(fig_out_path, 'labmeet_logit_build3.jpg'), p, height = 5, width=8, units="in")
p
```

## RL model comparison

```{r message=FALSE, warning=FALSE}
numpar_names = c("oneParam", "twoParams")
symm_names = c("Asymm", "Symm")
shape_names = c("LinearProbDistortion", "NonLinearProbDistortion")
rpe_names = c("_rpeBoth", "_rpeChosenBundleFractal", "_rpeWhenFractalRewarded")

model_names = c("oneParamDoubleSymmLinearProbDistortion_rpeBoth") #start with the name that doesn't fit in the rest
model_info = data.frame(model_name = "oneParamDoubleSymmLinearProbDistortion_rpeBoth", numpar=  "oneParam", symm = "Symm", shape = "LinearProbDistortion", rpe="_rpeBoth", norm=1)

for(i in 1:length(numpar_names)){
  for(j in 1:length(symm_names)){
    for(k in 1:length(shape_names)){
      for(l in 1:length(rpe_names)){
        model_name = paste0(numpar_names[i], symm_names[j], shape_names[k], rpe_names[l])
        model_names = c(model_names, model_name)
        cur_row = c(model_name = model_name,numpar = numpar_names[i],symm = symm_names[j],shape = shape_names[k], rpe = rpe_names[l], norm=0)
        model_info=  rbind(model_info, cur_row)
      }
    }
  }
}

rm(i, j, k, l, model_name, numpar_names, rpe_names, shape_names, symm_names, cur_row)
```

Read in or compute the fit statistics.

```{r}
if(file.exists(paste0(helpers_path, 'rlModels/elpds.RDS')) & !exists("elpds")){
  print("Reading in previously saved elpds...")
  elpds = readRDS(paste0(helpers_path, 'rlModels/elpds.RDS'))
  
} else{
  for(i in 1:length(model_names)){
    
    cur_model = model_names[i]
    
    if(i == 1){
      elpds = data.frame(elpd_loo_cv = NA, elpd_loo_cv_se = NA, waic = NA, waic_se = NA, model_name = NA, numpar=  NA, symm = NA, shape = NA, rpe=NA, norm=NA)
    }
    
    source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_', cur_model, '.R'))
    
    logLik = extract(fit, "logLikelihood")$logLikelihood
    cur_loo_cv = data.frame(loo::loo(logLik)$estimates)[1,] #loo_cv elpd estimate
    cur_waic = data.frame(loo::waic(logLik)$estimates)[3,] #waic estimate
    
    cur_row = model_info %>% filter(model_name == cur_model)
    cur_row$elpd_loo_cv = cur_loo_cv$Estimate
    cur_row$elpd_loo_cv_se = cur_loo_cv$SE
    cur_row$waic = cur_waic$Estimate
    cur_row$waic_se = cur_waic$SE
    
    elpds = rbind(elpds, cur_row)
    
    rbind(elpds)
    
    rm(logLik, cur_loo_cv, cur_waic, cur_row, fit, g_par_ests, par_ests)
  }
  rm(i)
}


if(file.exists(paste0(helpers_path, 'rlModels/sampled_logLiks.RDS')) & !exists("sampled_logLiks")){
  sampled_logLiks = readRDS(paste0(helpers_path, 'rlModels/sampled_logLiks.RDS'))
  print("Reading in previously saved samples of log likelihoods...")
} else{
  for(i in 1:length(model_names)){
    
    cur_model = model_names[i]
    
    if(i == 1){
      sampled_logLiks = data.frame(subnum = NA, logLik = NA, model_name=NA)
    }
    
    source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_', cur_model, '.R'))
    
    tmp = par_ests %>%
      filter(par == "alpha") %>% #parameter name doesn't matter. Just get the likelihoods for the model, which are the same for the sampled parameters. This just happens to be a parameter that is common across all models.
      group_by(subnum) %>% 
      mutate(iter = 1:n()) %>%
      filter(iter > 2000) %>% #sample only from post burn-in samples
      sample_n(100) %>%
      select(subnum, logLik) %>%
      mutate(model_name = cur_model)
    
    sampled_logLiks = rbind(sampled_logLiks, tmp) 
    
    rm(tmp, fit, g_par_ests, par_ests)
  }
  rm(i)
}



elpds = elpds %>% drop_na()
sampled_logLiks = sampled_logLiks %>% drop_na()

if(!file.exists(paste0(helpers_path, 'rlModels/elpds.RDS'))){
  saveRDS(elpds, paste0(helpers_path, 'rlModels/elpds.RDS'))
}

if(!file.exists(paste0(helpers_path, 'rlModels/sampled_logLiks.RDS'))){
  saveRDS(sampled_logLiks, paste0(helpers_path, 'rlModels/sampled_logLiks.RDS'))
}

```

```{r}
plot_opts = list(theme(axis.text.x = element_blank(),
                        legend.position = "bottom",
                        panel.grid = element_blank(),
                        legend.box = "vertical",
                        legend.spacing.y = unit(-0.25, "cm")),
                  scale_alpha_manual(values=c(.6, 1), name="Distortion shape",
                                     breaks = c("LinearProbDistortion", "NonLinearProbDistortion"),
                                     labels = c("Linear", "NonLinear")),
                  scale_shape_manual(values = c(16, 17), name="Distorted attribute",
                                     breaks = c("Asymm", "Symm"),
                                     labels = c("Fractal Only", "Both")),
                  scale_color_manual(breaks=c("_rpeBoth", "_rpeChosenBundleFractal", "_rpeWhenFractalRewarded"),
                                     labels=c("Both", "Chosen", "Rewarded"),
                                     name="Learning",
                                     values=c(cbbPalette[5], cbbPalette[3], cbbPalette[7])),
                  scale_linetype_manual(values = c("solid", "dashed"), name="# distortion params",
                                        breaks = c("oneParam", "twoParams"),
                                        labels = c("1", "2")))
```

```{r}
tmp = sampled_logLiks %>%
  left_join(model_info, by="model_name") %>%
  group_by(model_name) %>%
  summarise(sem_logLik = sd(logLik)/sqrt(n()),
            mean_logLik = mean(logLik),
            numpar = unique(numpar),
            symm = unique(symm),
            shape = unique(shape),
            rpe = unique(rpe)) %>%
  mutate(model_name = as.factor(model_name),
         model_name = reorder(model_name, mean_logLik)) 

p = tmp %>%
  ggplot(aes(model_name, mean_logLik, col=rpe, shape = symm, alpha = shape))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_logLik - sem_logLik, ymax=mean_logLik + sem_logLik, linetype=numpar))+
  labs(x="Model", y="Mean Log likelihood")+
  plot_opts

ggsave(file=paste0(fig_out_path, 'labmeet_rl_model_comparison_insample.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
p = elpds %>%
  mutate(model_name = reorder(model_name, elpd_loo_cv)) %>%
  ggplot(aes(model_name, elpd_loo_cv, col=rpe, shape = symm, alpha = shape))+
  geom_point()+
  geom_errorbar(aes(ymin=elpd_loo_cv-elpd_loo_cv_se, ymax=elpd_loo_cv+elpd_loo_cv_se, linetype=numpar), width=.2)+
  labs(x="Model", y="LOO-CV elpd")+
  plot_opts

ggsave(file=paste0(fig_out_path, 'labmeet_rl_model_comparison_outofsample.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
tmp = sampled_logLiks %>%
  left_join(model_info, by="model_name") %>%
  group_by(subnum, model_name) %>%
  summarise(sem_logLik = sd(logLik)/sqrt(n()),
            mean_logLik = mean(logLik),
            numpar = unique(numpar),
            symm = unique(symm),
            shape = unique(shape),
            rpe = unique(rpe), .groups="keep")

p = tmp %>%
  ggplot(aes(model_name, mean_logLik, col=rpe, shape = symm, alpha = shape))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_logLik - sem_logLik, ymax=mean_logLik + sem_logLik, linetype=numpar))+
  labs(x="Model", y="Mean Log likelihood")+
  plot_opts+
  theme(legend.position = "none")+
  facet_wrap(~subnum)

ggsave(file=paste0(fig_out_path, 'labmeet_rl_model_comparison_inddiff.jpg'), p, height = 15, width=25, units="in", dpi = 300)
p
```

# RT

## RT by probFractalDraw

```{r}
p = clean_beh_data %>%
  drop_na()%>%
  mutate(probFractalDraw = as.factor(probFractalDraw), 
         log_rt = log(reactionTime)) %>%
  group_by(probFractalDraw) %>%
  summarise(mean_log_rt = mean(log_rt),
            sem_log_rt = sd(log_rt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, mean_log_rt))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt), width=.2)+
  theme(panel.grid = element_blank())+
  labs(x = "p(Fractal)", y = "Mean Log RT")

ggsave(file=paste0(fig_out_path, 'labmeet_rt_by_pFrac.jpg'), p, height = 5, width=8, units="in")
p
```

## RT by probfractaldraw split by EV difference level

```{r}
p = clean_beh_data %>%
  rename(QVLeft = leftQValue, QVRight = rightQValue, EVLeft = leftLotteryEV, EVRight = rightLotteryEV)%>%
  mutate(lottery_ev_diff = round(abs(EVLeft - EVRight),3),
         lottery_ev_diff = ifelse(lottery_ev_diff ==0, "no EV diff", ifelse(lottery_ev_diff == .2, "small EV diff", ifelse(lottery_ev_diff == .4, "large EV diff", NA))),
         lottery_ev_diff = factor(lottery_ev_diff, levels=c("no EV diff", "small EV diff", "large EV diff"), labels = c("no", "small", "large")),
         logRt = log(reactionTime),
         probFractalDraw = as.factor(probFractalDraw)) %>%
  group_by(probFractalDraw, lottery_ev_diff) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, mean_logRt, color=lottery_ev_diff))+
  geom_point(position=position_dodge(width=.5))+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2,position=position_dodge(width=.5))+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  labs(color="Lottery EV difference", y="Mean Log RT", x="p(Fractal)")+
  scale_color_manual(values = c(cbbPalette[3], cbbPalette[5:6]))

ggsave(file=paste0(fig_out_path, 'labmeet_rt_by_evdiff.jpg'), p, height = 5, width=8, units="in")
p
```

## RT by probfractaldraw split by QV difference level

```{r}

p = clean_beh_data %>%
  rename(QVLeft = leftQValue, QVRight = rightQValue, EVLeft = leftLotteryEV, EVRight = rightLotteryEV)%>%
  # group_by(subnum) %>%
  mutate(logRt = log(reactionTime),
         QVDiff = abs(QVLeft - QVRight),
         diff_level = ifelse(QVDiff < quantile(QVDiff, probs=c(.33))[[1]], "small",
                             ifelse(QVDiff > quantile(QVDiff, probs=c(.66))[[1]], "large", "medium")),
         diff_level = factor(diff_level, levels=c("small", "medium", "large")),
         probFractalDraw = as.factor(probFractalDraw)) %>%
  group_by(probFractalDraw, diff_level) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, mean_logRt,color=diff_level))+
  geom_point(position=position_dodge(width=.5))+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2,position=position_dodge(width=.5))+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  labs(color="Fractal QV difference", y="Mean Log RT", x="p(Fractal)")+
  scale_color_manual(values = c(cbbPalette[3], cbbPalette[5:6]))

ggsave(file=paste0(fig_out_path, 'labmeet_rt_by_qvdiff.jpg'), p, height = 5, width=8, units="in")
p 
```

## RT for errors

```{r}
p = clean_beh_data %>%
  rename(distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)%>%
  mutate(choice = ifelse(choiceLeft == 1, "left", "right")) %>%
  mutate(leftLotterySubjBetter = distortedEVDiff > 0,
         leftFractSubjBetter = distortedQVDiff > 0,
         choseBetterSubjLott = ifelse(choice == "left" & leftLotterySubjBetter, "correct", ifelse(choice == "right" & !leftLotterySubjBetter, "correct", "incorrect")),
         choseBetterSubjFrac = ifelse(choice == "left" & leftFractSubjBetter, "correct", ifelse(choice == "right" & !leftFractSubjBetter, "correct", "incorrect")),
         logRt = log(reactionTime),
         fractalMoreRelevant = ifelse(probFractalDraw > .5, "fractal more relevant", "lottery more relevant"),
         fractalMoreRelevant = factor(fractalMoreRelevant, levels=c("lottery more relevant", "fractal more relevant"))) %>%
  select(fractalMoreRelevant, choseBetterSubjLott, choseBetterSubjFrac, logRt) %>%
  gather(key, value, -fractalMoreRelevant, -logRt) %>%
  group_by(fractalMoreRelevant, key, value) %>%
  summarise(.groups="keep",
            meanLogRt = mean(logRt),
            semLogRt = sd(logRt)/sqrt(n())) %>%
  mutate(correctBasedOn = ifelse(key == "choseBetterSubjLott", "Correct based on Lottery", "Correct based on Fractal"),
         correctBasedOn = factor(correctBasedOn, levels = c("Correct based on Lottery", "Correct based on Fractal"))) %>%
  ggplot(aes(fractalMoreRelevant, meanLogRt, color=value))+
  geom_point(position=position_dodge(width=.5))+
  geom_errorbar(aes(ymin=meanLogRt-semLogRt, ymax=meanLogRt+semLogRt),width=.2,position=position_dodge(width=.5))+
  labs(x="", y = "Mean Log RT", color="")+
  theme(legend.position = "bottom", panel.grid = element_blank())+
  scale_color_manual(values = c("blue", "red"))+
  facet_wrap(~correctBasedOn)


ggsave(file=paste0(fig_out_path, 'labmeet_rt_by_errors.jpg'), p, height = 5, width=8, units="in")
p    
```

# DDM

## Demo 1 integrator DDM

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
```

```{r}
# tmp = sim_trial(dLott=1, dFrac=1, dArb=1, sigmaLott = 0.001, sigmaFrac = 0.001, distortedEVDiff = .25, distortedQVDiff = -.1, probFractalDraw = 2, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

pFrac = .8
theta = .4
EVRight = .5
EVLeft = .7
distortedEVDiff = (1-theta)*(1-pFrac)*(EVLeft-EVRight)
QVLeft = .1
QVRight = .4
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)
VLeft = theta*pFrac*(QVLeft) + (1-theta)*(1-pFrac)*(EVLeft)
VRight = theta*pFrac*(QVRight) + (1-theta)*(1-pFrac)*(EVRight)

tmp = sim_trial(d = .05, sigma = .03, distortedEVDiff = distortedEVDiff, distortedQVDiff = distortedQVDiff, probFractalDraw = NA, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

annot_top = paste0("EVLeft = ", round(EVLeft, 3), ", EVRight = ", round(EVRight, 3), 
                    "\nQVLeft = ", round(QVLeft, 3),", QVRight = ", round(QVRight, 3),
                   "\nVLeft = ", round(VLeft, 3),", VRight = ", round(VRight, 3),
                   "\np(Fractal) = ", round(pFrac, 3),", theta = ", round(theta, 3),
                   "\nd = ", round(tmp$out$d, 3),", sigma = ", round(tmp$out$sigma, 3),
                    "\nchoice = ", tmp$out$choice)

p = tmp$debug_df %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "none",
        panel.grid = element_blank())+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  annotate(geom="text", x=.25, y = .6, label = annot_top, hjust=0)

# ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo.jpg'), p, height = 5, width=8, units="in")
p 

```

```{r}
p = tmp$debug_df %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "none", panel.grid = element_blank())+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  scale_y_continuous(minor_breaks = seq(-1,1,.1))+
  scale_x_continuous(minor_breaks = seq(0, nrow(tmp$debug_df), 10))

# ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo_nogrid.jpg'), p, height = 5, width=8, units="in")
p 
```

```{r}
p = tmp$debug_df %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "none")+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  scale_y_continuous(minor_breaks = seq(-1,1,.1))+
  scale_x_continuous(minor_breaks = seq(0, nrow(tmp$debug_df), 10))

# ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo_grid.jpg'), p, height = 5, width=8, units="in")
p 
```

```{r}
# tmp = sim_trial(dLott=1, dFrac=1, dArb=1, sigmaLott = 0.001, sigmaFrac = 0.001, distortedEVDiff = .25, distortedQVDiff = -.1, probFractalDraw = 2, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

pFrac = .1
theta = .5
EVRight = .5
EVLeft = 0
distortedEVDiff = (1-theta)*(1-pFrac)*(EVLeft-EVRight)
QVLeft = 0
QVRight = .4
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)
VLeft = theta*pFrac*(QVLeft) + (1-theta)*(1-pFrac)*(EVLeft)
VRight = theta*pFrac*(QVRight) + (1-theta)*(1-pFrac)*(EVRight)
sim_d = .5
sim_sigma = .03

tmp = sim_trial(d = sim_d, sigma = sim_sigma, distortedEVDiff = distortedEVDiff, distortedQVDiff = distortedQVDiff, probFractalDraw = NA, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

annot_top = paste0("EVLeft = ", round(EVLeft, 3), ", EVRight = ", round(EVRight, 3), 
                    "\nQVLeft = ", round(QVLeft, 3),", QVRight = ", round(QVRight, 3),
                   "\nVLeft = ", round(VLeft, 3),", VRight = ", round(VRight, 3),
                   "\np(Fractal) = ", round(pFrac, 3),", theta = ", round(theta, 3),
                   "\nd = ", round(tmp$out$d, 3),", sigma = ", round(tmp$out$sigma, 3),
                    "\nchoice = ", tmp$out$choice)
```


```{r}
p = tmp$debug_df %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "none",
        panel.grid.major.y = element_blank())+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  annotate(geom="text", x=.25, y = .6, label = annot_top, hjust=0)+
  scale_y_continuous(minor_breaks = seq(-1,1,.2))+
  scale_x_continuous(minor_breaks = seq(0, nrow(tmp$debug_df), 1))

ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_coarse_demo.jpg'), p, height = 5, width=8, units="in")
p 

```
```{r}
limitRange <- function(fun, mu, sig, min, max) {
  function(x) {
    y <- fun(x, mu, sig)
    y[x < min  |  x > max] <- NA
    return(y)
  }
}
```

```{r}
v = sim_d * (VLeft-VRight)

annot_right = paste0("VDiff = ", round(VLeft-VRight, 3), 
                    "\nv = d * VDiff = ", round(v, 3))

p =ggplot(data.frame(x = c(-.4, .3)), aes(x = x))+
  stat_function(fun = limitRange(dnorm, v, sim_sigma,NA, NA))+
  geom_vline(aes(xintercept = v), linetype="dashed")+
  annotate(geom="text", x=0, y = 6, label = annot_right, hjust=0)+
  # stat_function(fun = limitRange(dnorm, v, sim_sigma, v, -0.1), geom = "area", fill = "blue", alpha = 0.2)+
  theme(panel.grid = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())+
  labs(y="", x="dRDV/dt")

ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo_driftdist.jpg'), p, height = 5, width=8, units="in")
p 
```

```{r}
p =ggplot(data.frame(x = c(-.4, .3)), aes(x = x))+
  stat_function(fun = limitRange(dnorm, v, sim_sigma,NA, NA))+
  geom_vline(aes(xintercept = v), linetype="dashed")+
  annotate(geom="text", x=0, y = 6, label = annot_right, hjust=0)+
  stat_function(fun = limitRange(dnorm, v, sim_sigma, NA, -0.18), geom = "area", fill = "blue", alpha = 0.2)+
  theme(panel.grid = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())+
  labs(y="", x="dRDV/dt")

ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo_driftdist_shaded.jpg'), p, height = 5, width=8, units="in")
p 
```

```{r}
p =ggplot(data.frame(x = c(-.4, .3)), aes(x = x))+
  stat_function(fun = limitRange(dnorm, v, sim_sigma,NA, NA))+
  geom_vline(aes(xintercept = v), linetype="dashed")+
  annotate(geom="text", x=0, y = 6, label = annot_right, hjust=0)+
  stat_function(fun = limitRange(dnorm, v, sim_sigma, NA, -0.05), geom = "area", fill = "blue", alpha = 0.2)+
  theme(panel.grid = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())+
  labs(y="", x="dRDV/dt")

ggsave(file=paste0(fig_out_path, 'labmeet_oneInt_demo_driftdist_shaded2.jpg'), p, height = 5, width=8, units="in")
p 
```

## Demo 3 integrator DDM

```{r}
defcols = c("#F8766D", "#00BA38", "#619CFF")
```

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_threeIntegrators_sepProbDistortion.R'))
```


```{r}
# tmp = sim_trial(dLott=1, dFrac=1, dArb=1, sigmaLott = 0.001, sigmaFrac = 0.001, distortedEVDiff = .25, distortedQVDiff = -.1, probFractalDraw = 2, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

pFrac = .4
theta = .3
EVLeft = 0
EVRight = .8
distortedEVDiff = (1-theta)*(1-pFrac)*(EVLeft-EVRight)
QVLeft = .9
QVRight = 0
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)

sim_dLott = .02
sim_dFrac = .06
sim_dArb = .05
sim_sigma = .03

tmp = sim_trial(dLott=sim_dLott, dFrac=sim_dFrac, dArb=sim_dArb, sigmaLott = sim_sigma, sigmaFrac = sim_sigma, distortedEVDiff = distortedEVDiff , distortedQVDiff = distortedQVDiff , probFractalDraw = 2, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)
```

```{r}
annot_top = paste0("distortedQVDiff = ", round(distortedQVDiff, 3), ", distortedEVDiff = ", round(distortedEVDiff, 3),
                   "\np(Fractal) = ", round(pFrac, 3),", theta = ", round(theta, 3),
                   "\ndFrac = ", round(tmp$out$dFrac, 3),", dLott = ", round(tmp$out$dLott, 3))

p = tmp$debug_df %>%
  select(lotteryRDV, fractalRDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "bottom",
        panel.grid = element_blank())+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  annotate(geom="text", x=.25, y = .6, label = annot_top, hjust=0)+
  scale_color_manual(values=defcols[2:3])

ggsave(file=paste0(fig_out_path, 'labmeet_twoOfThreeInt_demo.jpg'), p, height = 5, width=8, units="in")
p 

```


```{r}
annot_top = paste0("distortedQVDiff = ", round(distortedQVDiff, 3), ", distortedEVDiff = ", round(distortedEVDiff, 3),
                   "\np(Fractal) = ", round(pFrac, 3),", theta = ", round(theta, 3),
                   "\ndFrac = ", round(tmp$out$dFrac, 3),", dLott = ", round(tmp$out$dLott, 3), ", dArb = ", round(tmp$out$dArb, 3),
                    "\nchoice (based on) = ", tmp$out$choice, " (", tmp$out$arbitrator,")")

p = tmp$debug_df %>%
  select(lotteryRDV, fractalRDV, arbitratorRDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "bottom",
        panel.grid = element_blank())+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  annotate(geom="text", x=.25, y = .6, label = annot_top, hjust=0)

ggsave(file=paste0(fig_out_path, 'labmeet_threeInt_demo.jpg'), p, height = 5, width=8, units="in")
p 

```

```{r}
p = tmp$debug_df %>%
  select(lotteryRDV, fractalRDV, arbitratorRDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  # geom_point()+
  geom_line(size=2)+
  geom_hline(aes(yintercept=1))+
  geom_hline(aes(yintercept=-1))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  theme(legend.position = "bottom")+
  labs(color="", x = "Timestep (in 10 ms)", y="RDV")+
  # annotate(geom="text", x=.25, y = .6, label = annot_top, hjust=0)+
  scale_y_continuous(minor_breaks = seq(-1,1,.1))+
  scale_x_continuous(minor_breaks = seq(0, nrow(tmp$debug_df), 2))

ggsave(file=paste0(fig_out_path, 'labmeet_threeInt_demo_grid.jpg'), p, height = 5, width=8, units="in")
p 

```

Distorted EV vs distorted QV (caveat trials)

```{r}

```

Simulation/fit checks

```{r}

```