---
title: 'Experience vs. description based decision-making project: DD model fitting methods and recovery checks'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))


set.seed(38573)
```

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamSymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_symmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-(theta*probFractalDraw))*lottery_ev_diff, #Symm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)

rm(fit, g_par_ests, par_ests)


```

# States-space method

Using one integrator model to demo how the likelihood is computed in the state-space method

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
```

See `NB21_LabMeetingFigures.Rmd` for demo figures.

## Particles

Grid of number of particles in each state at each time point

## Probability

Grid of probability of being in each state at each time point


## Multiple integrators

Start with particles

Visualize Antonio's suggestion of a 2D state space

----------------------------------------------------------------------------------------------------

# Test fitting functions

## One integrator

### Same trial

```{r}
d = 0.03
distortedEVDiff = .3
distortedQVDiff = .1
sigma = .05
n_particles = 250
sim_data = data.frame()

for(i in 1:n_particles){
  tmp = sim_trial(d = d, sigma = sigma, distortedEVDiff =distortedEVDiff, distortedQVDiff =distortedQVDiff, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, probFractalDraw = NA)
  tmp$iter = i
  sim_data = rbind(sim_data, tmp)
}
```

```{r}
fit_trial_list = list(model1 = fit_trial)

d_range = seq(.01, .1, .01)
sigma_range = seq(.01, .1, .01)

recovery_df = data.frame(test_d = NA, test_sigma = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(sigma_range)){
    test_d = d_range[i]
    test_sigma = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_data, par = c(test_d, test_sigma), par_names_ = c("d", "sigma"), model_name = "model1", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_d = test_d, test_sigma = test_sigma, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```


```{r}
recovery_df %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()

#Zoom in
recovery_df %>%
  filter(test_sigma>.04 & test_d < .06)%>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()
```

### Different trials (~single subject)

```{r}
sim_trial_list = list()
sim_trial_list[['model1']] = sim_trial
```

```{r}
n_trials = 300
stimuli = clean_beh_data[1:n_trials,] %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
sim_subj = sim_task(stimuli, model_name = "model1", d=d, sigma=sigma)
# sim_subj
```

```{r}
d_range = seq(.01, .1, .02)
sigma_range = seq(.01, .1, .02)

recovery_df = data.frame(test_d = NA, test_sigma = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(sigma_range)){
    test_d = d_range[i]
    test_sigma = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_subj, par = c(test_d, test_sigma), par_names_ = c("d", "sigma"), model_name = "model1", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_d = test_d, test_sigma = test_sigma, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()

```

```{r}
recovery_df %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()

recovery_df %>%
  filter(test_sigma > .03) %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()
```


## Two integrators

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_twoIntegrators_sepProbDistortion.R'))
fit_trial_list = list(model2 = fit_trial)
sim_trial_list = list(model2 = sim_trial)
```

### Same trial

```{r}

dLott=0.03 
dFrac=0.05
sigmaLott = 0.03 
sigmaFrac = 0.06

distortedEVDiff = .3
distortedQVDiff = .1
n_particles = 250
sim_data = data.frame()

for(i in 1:n_particles){
  tmp = sim_trial(dLott=0.03, dFrac=0.05, sigmaLott = 0.03, sigmaFrac = 0.06, distortedEVDiff =distortedEVDiff, distortedQVDiff =distortedQVDiff, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, probFractalDraw = NA)
  tmp$iter = i
  sim_data = rbind(sim_data, tmp)
}
```

```{r}
get_task_nll(data_ = sim_data, par = c(.03, .05, .03, .06), par_names_ = c("dLott", "dFrac", "sigmaLott", "sigmaFrac"), model_name = "model2", fix_pars_ = list())
```

```{r}
d_range = seq(.01, .1, .02)

recovery_df = data.frame(test_dLott = NA, test_dFrac = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(d_range)){
    test_dFrac = d_range[i]
    test_dLott = d_range[j]
    test_nll = get_task_nll(data_ = sim_data, par = c(test_dLott, test_dFrac, sigmaLott, sigmaFrac), par_names_ = c("dLott", "dFrac", "sigmaLott", "sigmaFrac"), model_name = "model2", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_dLott = test_dLott, test_dFrac = test_dFrac, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```


```{r}
recovery_df %>%
  mutate(test_dLott = as.factor(test_dLott),
         test_dFrac = as.factor(test_dFrac)) %>%
  ggplot(aes(test_dLott, test_dFrac, fill=nll))+
  geom_tile()+
  labs(title = paste0('dLott = ', dLott, ', dFrac = ', dFrac))
```

```{r}
sigma_range = seq(.01, .1, .02)

recovery_df = data.frame(test_sigmaLott = NA, test_sigmaFrac = NA, nll = NA)

for(i in 1:length(sigma_range)){
  for(j in 1:length(sigma_range)){
    test_sigmaFrac = sigma_range[i]
    test_sigmaLott = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_data, par = c(dLott, dFrac, test_sigmaLott, test_sigmaFrac), par_names_ = c("dLott", "dFrac", "sigmaLott", "sigmaFrac"), model_name = "model2", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_sigmaLott = test_sigmaLott, test_sigmaFrac = test_sigmaFrac, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```


```{r}
recovery_df %>%
  # filter(test_sigmaLott > .01 & test_sigmaFrac > .03) %>%
  mutate(test_sigmaLott = as.factor(test_sigmaLott),
         test_sigmaFrac = as.factor(test_sigmaFrac)) %>%
  ggplot(aes(test_sigmaLott, test_sigmaFrac, fill=nll))+
  geom_tile()+
  labs(title = paste0('sigmaLott = ', sigmaLott, ', sigmaFrac = ', sigmaFrac))
```

### Different trials (~single subject)

```{r}
n_trials = 300
stimuli = clean_beh_data_symmnonorm[1:n_trials,] %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
sim_subj = sim_task(stimuli, model_name = "model2", dLott=dLott, dFrac = dFrac, sigmaLott=sigmaLott, sigmaFrac = sigmaFrac)
# sim_subj
```

```{r}
d_range = seq(.01, .1, .02)

recovery_df = data.frame(test_dLott = NA, test_dFrac = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(d_range)){
    test_dFrac = d_range[i]
    test_dLott = d_range[j]
    test_nll = get_task_nll(data_ = sim_subj, par = c(test_dLott, test_dFrac, sigmaLott, sigmaFrac), par_names_ = c("dLott", "dFrac", "sigmaLott", "sigmaFrac"), model_name = "model2", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_dLott = test_dLott, test_dFrac = test_dFrac, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```

```{r}
recovery_df %>%
  mutate(test_dLott = as.factor(test_dLott),
         test_dFrac = as.factor(test_dFrac)) %>%
  ggplot(aes(test_dLott, test_dFrac, fill=nll))+
  geom_tile()+
  labs(title = paste0('dLott = ', dLott, ', dFrac = ', dFrac))
```

```{r}
sigma_range = seq(.01, .1, .02)

recovery_df = data.frame(test_sigmaLott = NA, test_sigmaFrac = NA, nll = NA)

for(i in 1:length(sigma_range)){
  for(j in 1:length(sigma_range)){
    test_sigmaFrac = sigma_range[i]
    test_sigmaLott = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_subj, par = c(dLott, dFrac, test_sigmaLott, test_sigmaFrac), par_names_ = c("dLott", "dFrac", "sigmaLott", "sigmaFrac"), model_name = "model2", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_sigmaLott = test_sigmaLott, test_sigmaFrac = test_sigmaFrac, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```


```{r}
recovery_df %>%
  # filter(test_sigmaLott > .01 & test_sigmaFrac > .03) %>%
  mutate(test_sigmaLott = as.factor(test_sigmaLott),
         test_sigmaFrac = as.factor(test_sigmaFrac)) %>%
  ggplot(aes(test_sigmaLott, test_sigmaFrac, fill=nll))+
  geom_tile()+
  labs(title = paste0('sigmaLott = ', sigmaLott, ', sigmaFrac = ', sigmaFrac))
```
