---
title: 'Experience vs. description based decision-making project: DD model fitting methods and recovery checks'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))


set.seed(38573)
```

# States-space method

Using one integrator model to demo how the likelihood is computed in the state-space method

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
```

See `NB21_LabMeetingFigures.Rmd` for demo figures.

## Particles

Grid of number of particles in each state at each time point

## Probability

Grid of probability of being in each state at each time point


## Multiple integrators

Start with particles

Visualize Antonio's suggestion of a 2D state space


----------------------------------------------------------------------------------------------------

### Same trial

```{r}
d = 0.03
distortedEVDiff = .3
distortedQVDiff = .1
sigma = .05
n_particles = 250
sim_data = data.frame()

for(i in 1:n_particles){
  tmp = sim_trial(d = d, sigma = sigma, distortedEVDiff =distortedEVDiff, distortedQVDiff =distortedQVDiff, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, probFractalDraw = NA)
  tmp$iter = i
  sim_data = rbind(sim_data, tmp)
}
```

```{r}
fit_trial_list = list(model1 = fit_trial)

d_range = seq(.01, .1, .01)
sigma_range = seq(.01, .1, .01)

recovery_df = data.frame(test_d = NA, test_sigma = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(sigma_range)){
    test_d = d_range[i]
    test_sigma = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_data, par = c(test_d, test_sigma), par_names_ = c("d", "sigma"), model_name = "model1", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_d = test_d, test_sigma = test_sigma, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()
```


```{r}
recovery_df %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()

#Zoom in
recovery_df %>%
  filter(test_sigma>.04 & test_d < .06)%>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()
```

### Different trials (~single subject)

```{r}
sim_trial_list = list()
sim_trial_list[['model1']] = sim_trial
```

```{r}
n_trials = 300
stimuli = clean_beh_data[1:n_trials,] %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
sim_subj = sim_task(stimuli, model_name = "model1", d=d, sigma=sigma)
# sim_subj
```

```{r}
d_range = seq(.01, .1, .02)
sigma_range = seq(.01, .1, .02)

recovery_df = data.frame(test_d = NA, test_sigma = NA, nll = NA)

for(i in 1:length(d_range)){
  for(j in 1:length(sigma_range)){
    test_d = d_range[i]
    test_sigma = sigma_range[j]
    test_nll = get_task_nll(data_ = sim_subj, par = c(test_d, test_sigma), par_names_ = c("d", "sigma"), model_name = "model1", fix_pars_ = list())
    recovery_df = rbind(recovery_df,
                        data.frame(test_d = test_d, test_sigma = test_sigma, nll = test_nll))
    
  }
}
recovery_df = recovery_df %>% drop_na()

```

```{r}
recovery_df %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()

recovery_df %>%
  filter(test_sigma > .03) %>%
  mutate(test_d = as.factor(test_d),
         test_sigma = as.factor(test_sigma)) %>%
  ggplot(aes(test_d, test_sigma, fill=nll))+
  geom_tile()
```

