---
title: 'Experience vs. description based decision-making project: DD model fits'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
library(here)
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))


set.seed(38573)
```

# Fits to data

```{r}
cpueaters_path = '/Users/zeynepenkavi/CpuEaters/DescribedVsLearned_beh/analysis/helpers/'
source(paste0(helpers_path, 'optimPostProcess/get_optim_out.R'))
```

```{r}
sim_trial_list = list()
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
sim_trial_list[['model1']] = sim_trial
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_twoIntegrators_sepProbDistortion.R'))
sim_trial_list[['model2']] = sim_trial
```

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamAsymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_asymmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         # distorted_ev_diff = (1-theta)*(1-probFractalDraw)*lottery_ev_diff, #Normalized Symm distortion
         distorted_ev_diff = (1-probFractalDraw)*lottery_ev_diff, #Asymm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)


rm(fit, g_par_ests, par_ests)


```

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamSymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_symmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-(theta*probFractalDraw))*lottery_ev_diff, #Symm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)

rm(fit, g_par_ests, par_ests)


```

```{r}
# Extract set of stimuli that will be used for simulations
sub_stims_asym = clean_beh_data_asymmnonorm %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)

sub_stims_sym = clean_beh_data_symmnonorm %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
```

```{r}
subnums = c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "22", "23", "25", "27")
data_prefix ="sub"
data_suffix = "_data"
```

## One integrator

### Asymm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamAsymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Simulate predicted data

```{r}
oneIntPpcAsymmLinear = data.frame()

for(i in 1:length(unique(oneIntEstsAsymmLinear$subnum))){
  cur_sub = unique(oneIntEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcAsymmLinear = rbind(oneIntPpcAsymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcAsymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

Simulated data with fitted parameters looks good for the logits. It also looks good for most levels of pFractalDraw except for very high levels. So the drift rates combined with the learning rate and prob distortion captures the weight placed on each attribute reasonably well. The mystery is why the predicted choices are so much slower at higher levels of probFractalDraw.  

To understand this we examine the varying part of the drift rate (d*(distorted_ev_diff+distorted_qv_diff)) at each probFractalDraw level. Even though the average of the trialwise varying drift rate is similar across the different levels the distributions are very different, such that more of the drift rates are closer to zero for higher levels of probFractalDraw.

So for decisions to be happening as fast as they do empirically they would need a lot longer to integrate with this drift rate, which is possible during the period between the probFractalDraw and stimulus presentation.

```{r}
clean_beh_data_asymmnonorm %>%
  mutate(distorted_val_diff = distorted_ev_diff+distorted_qv_diff,
         probFractalDraw = as.factor(probFractalDraw)) %>%
  ggplot(aes(distorted_val_diff))+
  geom_histogram(alpha=.5, bins=30)+
  facet_grid(probFractalDraw~.)+
  theme(panel.grid = element_blank())
```


```{r}
clean_beh_data_asymmnonorm %>%
  mutate(distorted_val_diff = distorted_ev_diff+distorted_qv_diff,
         probFractalDraw = as.factor(probFractalDraw)) %>%
  ggplot(aes(probFractalDraw, distorted_val_diff))+
  geom_violin()+
  theme(panel.grid = element_blank())
```

Proof of concept: If we add early integration for trials where fractals matter proprotional to how much they matter would we get choices as fast as empirically observed? 

```{r}
oneIntPpcAsymmLinear_fixRt = oneIntPpcAsymmLinear %>%
  mutate(reactionTime = ifelse(probFractalDraw>.5, reactionTime-(probFractalDraw^16)/2, reactionTime))

sim_sanity_checks(oneIntPpcAsymmLinear_fixRt, checks=c(4), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)

```

#### Early integration demo

```{r}
stimDelay = 250
timeStep = 10
pFracs = seq(0.6, 1, .1)

pFracScaler = function(x) {x^2}
scaledpFracs = unlist(map(pFracs, pFracScaler))
earlyIntSteps = round(rep(stimDelay/timeStep, length(pFracs)) * scaledpFracs)
earlyIntSteps
```

```{r}
clean_beh_data_asymmnonorm %>%
  select(subnum, theta) %>%
  distinct() %>%
  mutate(steps.6 = round((100)*(.6*theta)),
         steps.7 = round((100)*(.7*theta)),
         steps.8 = round((100)*(.8*theta)),
         steps.9 = round((100)*(.9*theta)),
         steps.10 = round((100)*(theta)))
```

Simulate data using the early integration model pluggin in parameters estimated from the non early integration model with single integrator

```{r}
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion_earlyIntegration.R'))
sim_trial_list[['model1ea']] = sim_trial
fit_trial_list = list(model1ea = fit_trial)
```

```{r}
oneIntPpcAsymmLinear_earlyInt = data.frame()

thetas = clean_beh_data_asymmnonorm %>%
  select(subnum, theta) %>% 
  distinct()

for(i in 1:length(unique(oneIntEstsAsymmLinear$subnum))){
  cur_sub = unique(oneIntEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsAsymmLinear %>% filter(subnum == cur_sub)
  cur_theta = thetas %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1ea", d=cur_pars$d, sigma=cur_pars$sigma, theta=cur_theta$theta, stimDelay = 250)
  sim_subj$subnum = cur_sub
  oneIntPpcAsymmLinear_earlyInt = rbind(oneIntPpcAsymmLinear_earlyInt, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcAsymmLinear_earlyInt, checks=c(1,3,4,5), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

Test fitting function for early integration model

```{r}
library(here)
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'ddModels/fit_task.R'))

# tmp = read.csv('/Users/zeynepenkavi/Documents/RangelLab/DescribedVsLearned_beh/analysis/helpers/ddModels/cluster_scripts/sub_data_oneParamAsymmLinear_wTheta/sub01_data.csv')
tmp = read.csv('/Users/zeynepenkavi/Documents/RangelLab/DescribedVsLearned_beh/analysis/helpers/ddModels/cluster_scripts/sub_data_oneParamAsymmLinear_wTheta/sub10_data.csv')
# fit_task(data_ = tmp, model_name_ = "model1ea", pars_ = list(d=cur_pars$d, sigma=cur_pars$sigma, theta=cur_theta$theta, stimDelay = 250))
# fit_task(data_ = tmp, model_name_ = "model1ea", pars_ = list(d=cur_pars$d, sigma=cur_pars$sigma, stimDelay = 250))

start_vals = c(0.932282596703016,0.0299321074307384)

model='oneIntegrator_sepProbDistortion_earlyIntegration'
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_', model,'.R'))
fit_trial_list = list()
fit_trial_list[[model]] = fit_trial

# out=data.frame()
# for (i in 1:nrow(tmp)){
#   out = rbind(out, fit_trial(d=start_vals[1], sigma=start_vals[2], choice = tmp$choice[i], reactionTime = tmp$reactionTime[i], probFractalDraw = tmp$probFractalDraw[i], EVLeft=tmp$EVLeft[i], EVRight=tmp$EVRight[i], QVLeft=tmp$QVLeft[i], QVRight=tmp$QVRight[i], distortedEVDiff = tmp$distortedEVDiff[i], distortedQVDiff = tmp$distortedQVDiff[i], theta=tmp$theta[i]))
# }
# out
# 

# i=11
# fit_trial(d=start_vals[1], sigma=start_vals[2], choice = tmp$choice[i], reactionTime = tmp$reactionTime[i], probFractalDraw = tmp$probFractalDraw[i], EVLeft=tmp$EVLeft[i], EVRight=tmp$EVRight[i], QVLeft=tmp$QVLeft[i], QVRight=tmp$QVRight[i], distortedEVDiff = tmp$distortedEVDiff[i], distortedQVDiff = tmp$distortedQVDiff[i], theta=tmp$theta[i])

fit_task(data_=tmp, model_name_=model, pars_=list(d=start_vals[1], sigma=start_vals[2]), fix_pars_ = list(), fit_trial_list_ = fit_trial_list, debug=FALSE)

```

```{r}
i=13
choice = tmp$choice[i]
reactionTime = tmp$reactionTime[i]
probFractalDraw = tmp$probFractalDraw[i]
EVLeft=tmp$EVLeft[i]
EVRight=tmp$EVRight[i]
QVLeft=tmp$QVLeft[i]
QVRight=tmp$QVRight[i]
distortedEVDiff = tmp$distortedEVDiff[i]
distortedQVDiff = tmp$distortedQVDiff[i]
theta = tmp$theta[i]

barrierDecay=0
barrier=1
nonDecisionTime=0
bias=0
timeStep=10
epsilon = 0
approxStateStep = 0.1
debug=FALSE
stimDelay = 1000
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneIntnoExt_oneParamAsymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Compare parameters from fits with and without the extreme cases

```{r}
oneIntEstsAsymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(oneIntEstsAsymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

### Symm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamSymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsSymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Simulate predicted data

```{r}
oneIntPpcSymmLinear = data.frame()

for(i in 1:length(unique(oneIntEstsSymmLinear$subnum))){
  cur_sub = unique(oneIntEstsSymmLinear$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsSymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcSymmLinear = rbind(oneIntPpcSymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcSymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneIntnoExt_oneParamSymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsSymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Compare parameters from fits with and without the extreme cases

```{r}
oneIntEstsSymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(oneIntEstsSymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
oneIntPpcSymmLinearnoExt = data.frame()

for(i in 1:length(unique(oneIntEstsSymmLinearnoExt$subnum))){
  cur_sub = unique(oneIntEstsSymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = oneIntEstsSymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcSymmLinearnoExt = rbind(oneIntPpcSymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcSymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```

## Two integrators

### Asymm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamAsymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

```{r}
ddm_fit_pars %>%
  rename(dLott = Param1, dFrac = Param2, sigmaLott = Param3, sigmaFrac = Param4, nll = Param5) %>%
  select(-nll) %>%
  gather(key, value, -subnum) %>%
  ggplot(aes(value))+
  geom_histogram(bins=30, position = "identity", alpha=.5)+
  facet_grid(subnum~key, scales="free")
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Distributions of estimated parameters

```{r}
twoIntsEstsAsymmLinear %>%
  select(-subnum) %>%
  gather(key, value) %>%
  ggplot(aes(value))+
  geom_histogram(bins=20, alpha=.5)+
  theme(panel.grid = element_blank())+
  facet_wrap(~key, scales="free")+
  labs(x="", y="")
```

Is there any correlation between the estimated drift rate and the noise?

```{r}
twoIntsEstsAsymmLinear %>%
  gather(key, value, -subnum) %>%
  mutate(par = ifelse(grepl("sigma", key), "sigma", "d"),
         attr= ifelse(grepl("Frac", key), "Frac", "Lott")) %>% 
  select(-key) %>%
  group_by(attr) %>%
  spread(par, value) %>%
  ggplot(aes(d, sigma)) +
  geom_point()+
  theme(panel.grid = element_blank())+
  facet_wrap(~attr)
```

```{r}
twoIntsEstsAsymmLinear %>%
  gather(key, value, -subnum) %>%
  mutate(par = ifelse(grepl("sigma", key), "sigma", "d"),
         attr= ifelse(grepl("Frac", key), "Frac", "Lott")) %>% 
  select(-key) %>%
  group_by(par) %>%
  spread(attr, value) %>%
  ggplot(aes(Frac, Lott))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0))+
  theme(panel.grid = element_blank())+
  facet_wrap(~par)
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinear = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinear = rbind(twoIntsPpcAsymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

Simulate predicted data fixing the noise at the same level for both attributes and a lower level than the estimate parameters

```{r}
twoIntsPpcAsymmLinear_fixSigma = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=abs(cur_pars$dLott), dFrac=cur_pars$dFrac, sigmaLott=.05, sigmaFrac=.05)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinear_fixSigma = rbind(twoIntsPpcAsymmLinear_fixSigma, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinear_fixSigma, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

```{r}
twoIntsPpcAsymmLinear_fixSigma_fixRt = twoIntsPpcAsymmLinear_fixSigma %>%
  mutate(reactionTime = ifelse(probFractalDraw>.5, reactionTime-(probFractalDraw^8), reactionTime))
  

sim_sanity_checks(twoIntsPpcAsymmLinear_fixSigma_fixRt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

#### Fixed noise level

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamAsymmLinear_fixSigma/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
# ddm_fit_pars %>%
#   select(-Param3) %>%
#   gather(key, value, -subnum) %>%
#   ggplot(aes(value,fill=key))+
#   geom_histogram(bins=30, alpha=.5, position="identity")+
#   theme(panel.grid = element_blank())+
#   facet_wrap(~subnum)

twoIntsEstsAsymmLinearfixSigma = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2))
```

Compare parameters from fits with and without the extreme cases

```{r}
twoIntsEstsAsymmLinear %>% 
  select(-sigmaLott, -sigmaFrac) %>%
  mutate(fit = "wSigma") %>%
  rbind(twoIntsEstsAsymmLinearfixSigma %>% mutate(fit = "fixSigma")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(wSigma, fixSigma))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinearfixSigma= data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinearfixSigma$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinearfixSigma$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub) 
  cur_pars = twoIntsEstsAsymmLinearfixSigma %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=.05, sigmaFrac=.05)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinearfixSigma = rbind(twoIntsPpcAsymmLinearfixSigma, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinearfixSigma, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoIntsnoExt_oneParamAsymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsAsymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Compare parameters from fits with and without the extreme cases

```{r}
twoIntsEstsAsymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(twoIntsEstsAsymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinearnoExt = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinearnoExt$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = twoIntsEstsAsymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinearnoExt = rbind(twoIntsPpcAsymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```

### Symm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamSymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsSymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Distributions of estimated parameters

```{r}
twoIntsEstsSymmLinear %>%
  select(-subnum) %>%
  gather(key, value) %>%
  ggplot(aes(value))+
  geom_histogram(bins=20, alpha=.5)+
  theme(panel.grid = element_blank())+
  facet_wrap(~key, scales="free")+
  labs(x="", y="")
```

Simulate predicted data

```{r}
twoIntsPpcSymmLinear = data.frame()

for(i in 1:length(unique(twoIntsEstsSymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsSymmLinear$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsSymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcSymmLinear = rbind(twoIntsPpcSymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcSymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoIntsnoExt_oneParamSymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsSymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Compare parameters from fits with and without the extreme cases

```{r}
twoIntsEstsSymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(twoIntsEstsSymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
twoIntsPpcSymmLinearnoExt = data.frame()

for(i in 1:length(unique(twoIntsEstsSymmLinearnoExt$subnum))){
  cur_sub = unique(twoIntsEstsSymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = twoIntsEstsSymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcSymmLinearnoExt = rbind(twoIntsPpcSymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcSymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```


## Three integrators

Estimated drift rates are an order of magnitude larger than those needed to replicate patterns in the true data.

