---
title: 'Experience vs. description based decision-making project: DD model fits'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'ddModels/fit_task.R'))
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))


set.seed(38573)
```

# Fits to data

```{r}
cpueaters_path = '/Users/zeynepenkavi/CpuEaters/DescribedVsLearned_beh/analysis/helpers/'
source(paste0(helpers_path, 'optimPostProcess/get_optim_out.R'))
```

```{r}
sim_trial_list = list()
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
sim_trial_list[['model1']] = sim_trial
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_twoIntegrators_sepProbDistortion.R'))
sim_trial_list[['model2']] = sim_trial
```

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamAsymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_asymmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         # distorted_ev_diff = (1-theta)*(1-probFractalDraw)*lottery_ev_diff, #Normalized Symm distortion
         distorted_ev_diff = (1-probFractalDraw)*lottery_ev_diff, #Asymm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)


rm(fit, g_par_ests, par_ests)


```

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamSymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_symmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data_symmnonorm = clean_beh_data_symmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-(theta*probFractalDraw))*lottery_ev_diff, #Symm distortion
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff)

rm(fit, g_par_ests, par_ests)


```

```{r}
# Extract set of stimuli that will be used for simulations
sub_stims_asym = clean_beh_data_asymmnonorm %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)

sub_stims_sym = clean_beh_data_symmnonorm %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
```

```{r}
subnums = c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "22", "23", "25", "27")
data_prefix ="sub"
data_suffix = "_data"
```

## One integrator

### Asymm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamAsymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Simulate predicted data

```{r}
oneIntPpcAsymmLinear = data.frame()

for(i in 1:length(unique(oneIntEstsAsymmLinear$subnum))){
  cur_sub = unique(oneIntEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcAsymmLinear = rbind(oneIntPpcAsymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcAsymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneIntnoExt_oneParamAsymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Compare parameters from fits with and without the extreme cases

```{r}
oneIntEstsAsymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(oneIntEstsAsymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

### Symm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamSymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsSymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Simulate predicted data

```{r}
oneIntPpcSymmLinear = data.frame()

for(i in 1:length(unique(oneIntEstsSymmLinear$subnum))){
  cur_sub = unique(oneIntEstsSymmLinear$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsSymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcSymmLinear = rbind(oneIntPpcSymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcSymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneIntnoExt_oneParamSymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsSymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Compare parameters from fits with and without the extreme cases

```{r}
oneIntEstsSymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(oneIntEstsSymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
oneIntPpcSymmLinearnoExt = data.frame()

for(i in 1:length(unique(oneIntEstsSymmLinearnoExt$subnum))){
  cur_sub = unique(oneIntEstsSymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = oneIntEstsSymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcSymmLinearnoExt = rbind(oneIntPpcSymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(oneIntPpcSymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```

## Two integrators

### Asymm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamAsymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

```{r}
ddm_fit_pars %>%
  rename(dLott = Param1, dFrac = Param2, sigmaLott = Param3, sigmaFrac = Param4, nll = Param5) %>%
  select(-nll) %>%
  gather(key, value, -subnum) %>%
  ggplot(aes(value))+
  geom_histogram(bins=30, position = "identity", alpha=.5)+
  facet_grid(subnum~key, scales="free")
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Distributions of estimated parameters

```{r}
twoIntsEstsAsymmLinear %>%
  select(-subnum) %>%
  gather(key, value) %>%
  ggplot(aes(value))+
  geom_histogram(bins=20, alpha=.5)+
  theme(panel.grid = element_blank())+
  facet_wrap(~key, scales="free")+
  labs(x="", y="")
```

Is there any correlation between the estimated drift rate and the noise?

```{r}
twoIntsEstsAsymmLinear %>%
  gather(key, value, -subnum) %>%
  mutate(par = ifelse(grepl("sigma", key), "sigma", "d"),
         attr= ifelse(grepl("Frac", key), "Frac", "Lott")) %>% 
  select(-key) %>%
  group_by(attr) %>%
  spread(par, value) %>%
  ggplot(aes(d, sigma)) +
  geom_point()+
  theme(panel.grid = element_blank())+
  facet_wrap(~attr)
```

```{r}
twoIntsEstsAsymmLinear %>%
  gather(key, value, -subnum) %>%
  mutate(par = ifelse(grepl("sigma", key), "sigma", "d"),
         attr= ifelse(grepl("Frac", key), "Frac", "Lott")) %>% 
  select(-key) %>%
  group_by(par) %>%
  spread(attr, value) %>%
  ggplot(aes(Frac, Lott))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0))+
  theme(panel.grid = element_blank())+
  facet_wrap(~par)
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinear = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinear = rbind(twoIntsPpcAsymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```
Simulate predicted data fixing the noise at the same level for both attributes and a lower level than the estimate parameters

```{r}
twoIntsPpcAsymmLinear_fixSigma = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=abs(cur_pars$dLott), dFrac=cur_pars$dFrac, sigmaLott=.05, sigmaFrac=.05)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinear_fixSigma = rbind(twoIntsPpcAsymmLinear_fixSigma, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinear_fixSigma, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

```{r}
twoIntsPpcAsymmLinear_fixSigma_fixRt = twoIntsPpcAsymmLinear_fixSigma %>%
  mutate(reactionTime = ifelse(probFractalDraw>.5, reactionTime-(abs(log(probFractalDraw))*.5), reactionTime))
  

sim_sanity_checks(twoIntsPpcAsymmLinear_fixSigma_fixRt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoIntsnoExt_oneParamAsymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsAsymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Compare parameters from fits with and without the extreme cases

```{r}
twoIntsEstsAsymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(twoIntsEstsAsymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinearnoExt = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinearnoExt$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = twoIntsEstsAsymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinearnoExt = rbind(twoIntsPpcAsymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcAsymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_asym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```

### Symm distortion

#### With extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamSymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsSymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Distributions of estimated parameters

```{r}
twoIntsEstsSymmLinear %>%
  select(-subnum) %>%
  gather(key, value) %>%
  ggplot(aes(value))+
  geom_histogram(bins=20, alpha=.5)+
  theme(panel.grid = element_blank())+
  facet_wrap(~key, scales="free")+
  labs(x="", y="")
```

Simulate predicted data

```{r}
twoIntsPpcSymmLinear = data.frame()

for(i in 1:length(unique(twoIntsEstsSymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsSymmLinear$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsSymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcSymmLinear = rbind(twoIntsPpcSymmLinear, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcSymmLinear, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym)
```

#### Without extreme cases

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoIntsnoExt_oneParamSymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsSymmLinearnoExt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Compare parameters from fits with and without the extreme cases

```{r}
twoIntsEstsSymmLinear %>%
  mutate(fit = "wExt") %>%
  rbind(twoIntsEstsSymmLinearnoExt %>% mutate(fit = "noExt")) %>%
  gather(par, value, -subnum, -fit) %>%
  group_by(par) %>%
  spread(fit, value) %>%
  ggplot(aes(noExt, wExt))+
  geom_point()+
  geom_abline(aes(slope=1, intercept=0), color="gray")+
  facet_wrap(~par, scales="free")+
  theme(panel.grid = element_blank())
```

Simulate predicted data

```{r}
twoIntsPpcSymmLinearnoExt = data.frame()

for(i in 1:length(unique(twoIntsEstsSymmLinearnoExt$subnum))){
  cur_sub = unique(twoIntsEstsSymmLinearnoExt$subnum)[i]
  cur_stims =  sub_stims_sym %>% filter(subnum == cur_sub) %>% filter(probFractalDraw != 0 & probFractalDraw != 1)
  cur_pars = twoIntsEstsSymmLinearnoExt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcSymmLinearnoExt = rbind(twoIntsPpcSymmLinearnoExt, sim_subj)
}

```

```{r}
sim_sanity_checks(twoIntsPpcSymmLinearnoExt, checks=c(1,3,4,5,6,8), compare_logits = T, compare_rts = T, true_data = sub_stims_sym %>% filter(probFractalDraw != 0 & probFractalDraw != 1))
```


## Three integrators

Estimated drift rates are an order of magnitude larger than those needed to replicate patterns in the true data.

