---
title: 'Experience vs. description based decision-making project: Examine behavioral regressors for fmri GLMs'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---

```{r include=FALSE}
library(tidyverse)
theme_set(theme_bw())
library(here)
library(GGally)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')

source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))

set.seed(38573)
```

Which value regressor best captures activity in value regions?

Chosen RL model: One parameter prob distortion parameter (theta) asymmetrically distorting fractal value

```{r message=FALSE, warning=FALSE}
source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamAsymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data_asymmnonorm = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

rm(fit, g_par_ests, par_ests)

```

true value * prob fractal draw (left_tv_pfrac, right_tv_pfrac)
true value * distorted prob fractal draw (left_tv_wpfrac, right_tv_wpfrac)
qv * prob fractal draw (left_qv_pfrac, right_qv_pfrac)
qv * distorted prob fractal draw (left_qv_wpfrac, right_qv_wpfrac)

```{r}
clean_beh_data_asymmnonorm = clean_beh_data_asymmnonorm %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         wpFrac = theta*probFractalDraw, 
         left_tv_pFrac = fractalLeftProb * probFractalDraw,
         right_tv_pFrac = fractalRightProb * probFractalDraw,
         left_tv_wpFrac = fractalLeftProb * wpFrac,
         right_tv_wpFrac = fractalRightProb * wpFrac,
         left_qv_pFrac = leftQValue * probFractalDraw,
         right_qv_pFrac = rightQValue * probFractalDraw,
         left_qv_wpFrac = leftQValue * wpFrac,
         right_qv_wpFrac = rightQValue * wpFrac,
         left_ev_pLott = leftLotteryEV * (1-probFractalDraw),
         right_ev_pLott = rightLotteryEV * (1-probFractalDraw))
```

value sum = left frac + left lott + right frac + right lott

```{r}
tmp = clean_beh_data_asymmnonorm %>%
  mutate(vsum_tv_pFrac = left_ev_pLott + right_ev_pLott + left_tv_pFrac + right_tv_pFrac,
         vsum_tv_wpFrac = left_ev_pLott + right_ev_pLott + left_tv_wpFrac + right_tv_wpFrac,
         vsum_qv_pFrac = left_ev_pLott + right_ev_pLott + left_qv_pFrac + right_qv_pFrac,
         vsum_qv_wpFrac = left_ev_pLott + right_ev_pLott + left_qv_wpFrac + right_qv_wpFrac) %>%
  select(vsum_tv_pFrac, vsum_tv_wpFrac, vsum_qv_pFrac, vsum_qv_wpFrac)

# ggpairs(tmp)
```

non distorted versus distorted value sum by runs

is the distorted value weak bc there are a bunch of 0's in the beginning?

```{r}
clean_beh_data_asymmnonorm %>%
  mutate(vsum_tv_pFrac = left_ev_pLott + right_ev_pLott + left_tv_pFrac + right_tv_pFrac,
         vsum_tv_wpFrac = left_ev_pLott + right_ev_pLott + left_tv_wpFrac + right_tv_wpFrac,
         vsum_qv_pFrac = left_ev_pLott + right_ev_pLott + left_qv_pFrac + right_qv_pFrac,
         vsum_qv_wpFrac = left_ev_pLott + right_ev_pLott + left_qv_wpFrac + right_qv_wpFrac) %>%
  select(vsum_tv_pFrac, vsum_qv_wpFrac, session, subnum) %>%
  group_by(subnum, session) %>%
  mutate(vsum_tv_pFrac_demean = vsum_tv_pFrac-mean(vsum_tv_pFrac),
         vsum_qv_wpFrac_demean = vsum_qv_wpFrac-mean(vsum_qv_wpFrac))%>%
  ungroup()%>%
  select(-subnum) %>%
  gather(key, value, -session) %>%
  mutate(demeaned = ifelse(grepl("demean", key), "demeaned", "raw")) %>%
  ggplot(aes(value, fill=key)) +
  geom_histogram(alpha=.5, position="identity", bins=30)+
  facet_grid(demeaned~session)+
  geom_abline(aes(slope=1, intercept=0))+
  theme(panel.grid = element_blank(),
        legend.position = "bottom", 
        legend.title = element_blank())+
  labs(x="",y="")

```
```{r}
clean_beh_data_asymmnonorm %>%
  mutate(vsum_tv_pFrac = left_ev_pLott + right_ev_pLott + left_tv_pFrac + right_tv_pFrac,
         vsum_tv_wpFrac = left_ev_pLott + right_ev_pLott + left_tv_wpFrac + right_tv_wpFrac,
         vsum_qv_pFrac = left_ev_pLott + right_ev_pLott + left_qv_pFrac + right_qv_pFrac,
         vsum_qv_wpFrac = left_ev_pLott + right_ev_pLott + left_qv_wpFrac + right_qv_wpFrac) %>%
  select(vsum_tv_pFrac, vsum_qv_wpFrac, session, subnum, trialNum) %>%
  filter(trialNum>20) %>%
  group_by(subnum, session) %>%
  mutate(vsum_tv_pFrac_demean = vsum_tv_pFrac-mean(vsum_tv_pFrac),
         vsum_qv_wpFrac_demean = vsum_qv_wpFrac-mean(vsum_qv_wpFrac))%>%
  ggplot(aes(vsum_tv_pFrac_demean, vsum_qv_wpFrac_demean)) +
  geom_point()+
  facet_wrap(~session)+
  geom_abline(aes(slope=1, intercept=0))+
  theme(panel.grid = element_blank())

```

value diff = (left frac + left lott) - (right frac + right lott)

```{r}
tmp = clean_beh_data_asymmnonorm %>%
  mutate(vdiff_tv_pFrac = abs((left_ev_pLott + left_tv_pFrac) - (right_ev_pLott + right_tv_pFrac)),
         vdiff_tv_wpFrac = abs((left_ev_pLott + left_tv_wpFrac) - (right_ev_pLott + right_tv_wpFrac)),
         vdiff_qv_pFrac = abs((left_ev_pLott + left_qv_pFrac) - (right_ev_pLott + right_qv_pFrac)),
         vdiff_qv_wpFrac = abs((left_ev_pLott + left_qv_wpFrac) - (right_ev_pLott + right_qv_wpFrac))) %>%
  select(vdiff_tv_pFrac, vdiff_tv_wpFrac, vdiff_qv_pFrac, vdiff_qv_wpFrac)

ggpairs(tmp)
```

value chosen - unchosen = (chosen frac + chosen lott) - (unchosen frac + unchosen lott)

```{r}
tmp = clean_beh_data_asymmnonorm %>%
  mutate(chosen_ev_pLott = ifelse(choiceLeft == 1, left_ev_pLott, right_ev_pLott),
         unchosen_ev_pLott = ifelse(choiceLeft == 0, left_ev_pLott, right_ev_pLott),
         chosen_tv_pFrac = ifelse(choiceLeft == 1, left_tv_pFrac, right_tv_pFrac),
         chosen_tv_wpFrac = ifelse(choiceLeft == 1, left_tv_wpFrac, right_tv_wpFrac),
         chosen_qv_pFrac = ifelse(choiceLeft == 1, left_qv_pFrac, right_qv_pFrac),
         chosen_qv_wpFrac = ifelse(choiceLeft == 1, left_qv_wpFrac, right_qv_wpFrac),
         unchosen_tv_pFrac = ifelse(choiceLeft == 0, left_tv_pFrac, right_tv_pFrac),
         unchosen_tv_wpFrac = ifelse(choiceLeft == 0, left_tv_wpFrac, right_tv_wpFrac),
         unchosen_qv_pFrac  = ifelse(choiceLeft == 0, left_qv_pFrac, right_qv_pFrac),
         unchosen_qv_wpFrac = ifelse(choiceLeft == 0, left_qv_wpFrac, right_qv_wpFrac),
         vchosendiff_tv_pFrac = (chosen_ev_pLott + chosen_tv_pFrac) - (unchosen_ev_pLott + unchosen_tv_pFrac),
         vchosendiff_tv_wpFrac = (chosen_ev_pLott + chosen_tv_wpFrac) - (unchosen_ev_pLott + unchosen_tv_wpFrac),
         vchosendiff_qv_pFrac = (chosen_ev_pLott + chosen_qv_pFrac) - (unchosen_ev_pLott + unchosen_qv_pFrac),
         vchosendiff_qv_wpFrac = (chosen_ev_pLott + chosen_qv_wpFrac) - (unchosen_ev_pLott + unchosen_qv_wpFrac)) %>%
  select(vchosendiff_tv_pFrac, vchosendiff_tv_wpFrac, vchosendiff_qv_pFrac, vchosendiff_qv_wpFrac)

ggpairs(tmp)
```
