---
title: 'Experience vs. description based decision-making project: Figure for Arrowhead poster'
output:
  html_document:
    toc: yes
    toc_float: yes
    code_folding: 'hide'
  pdf_document:
    toc: yes
---



```{r include=FALSE}
library(broom)
library(tidyverse)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'01_clean_behavioral_data.R'))
source(paste0(helpers_path, 'get_qvals.R'))
fig_out_path = paste0(here(), '/outputs/fig/')
theme_set(theme_bw())
```

# Choice logit with EV, true V, QV

```{r message=FALSE, warning=FALSE}

source(paste0(helpers_path, 'rlModels/fit_rl_hierarchical_oneParamAsymmLinearProbDistortion_rpeBoth.R'))

clean_beh_data = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  spread(par, est) %>%
  left_join(clean_beh_data, by='subnum')

## Add Q values of fractals to each trial
clean_beh_data = clean_beh_data %>%
  group_by(subnum) %>%
  do(get_qvals(., model_name="rpeBoth")) %>%
  ungroup()

clean_beh_data = clean_beh_data %>%
  mutate(rightLotteryEV = referenceProb * referenceValue,
         leftLotteryEV = lotteryValue * lotteryProb,
         lottery_ev_diff = leftLotteryEV - rightLotteryEV,
         fractal_qv_diff = leftQValue - rightQValue,
         distorted_ev_diff = (1-probFractalDraw)*lottery_ev_diff,
         distorted_qv_diff = theta*probFractalDraw*fractal_qv_diff,
         probFractalDraw = as.factor(probFractalDraw),
         fractal_prob_diff = fractalLeftProb - fractalRightProb)

rm(fit, g_par_est, par_ests)
```

```{r}
truev_mod = clean_beh_data %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ lottery_ev_diff + fractal_prob_diff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term != "(Intercept)") %>%
  select(probFractalDraw, term, estimate, std.error)

qv_mod = clean_beh_data %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ lottery_ev_diff + fractal_qv_diff, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
  filter(term == "fractal_qv_diff") %>%
  select(probFractalDraw, term, estimate, std.error)

qv_theta_mod = clean_beh_data %>%
  mutate(fractal_qv_diff_theta = fractal_qv_diff * theta) %>%
  nest(data = -probFractalDraw) %>% 
  mutate(
    fit = map(data, ~ glm(choiceLeft ~ lottery_ev_diff + fractal_qv_diff_theta, data = .x, family=binomial(link="logit"))),
    tidied = map(fit, tidy)
  ) %>% 
  unnest(tidied) %>%
   filter(term == "fractal_qv_diff_theta") %>%
  select(probFractalDraw, term, estimate, std.error)
```

```{r}
p = rbind(truev_mod, qv_mod, qv_theta_mod) %>%
  mutate(reg = ifelse(term %in% c("lottery_ev_diff", "lottery_ev_diff_theta"), "Lottery EV Difference", ifelse(term == "fractal_prob_diff", "True Fractal Value Difference", ifelse(term %in% c("fractal_qv_diff"),"Fractal QV Difference", NA))),
         reg = factor(reg, levels=c("True Fractal Value Difference", "Lottery EV Difference", "Fractal QV Difference")),
         theta = grepl("theta", term),
         fract = ifelse(reg == "Fractal QV Difference", T, F)) %>%
  ggplot(aes(probFractalDraw, estimate, col=reg, group=reg, alpha=theta))+
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2, size=3)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[3:1])+
  scale_alpha_manual(guide = "none", values=c(1,0))+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  theme(legend.position = "bottom",
        legend.background = element_blank(),
        legend.box = "vertical",
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=20))+
  labs(color="", x= "p(FD)", y="Beta estimate")+
  expand_limits(y=c(-1,11))+
  scale_y_continuous(breaks=seq(0, 10, 2.5))+
  guides(col = guide_legend(nrow = 1))

#grab legend before removing it
legend <- cowplot::get_legend(p)

p =p + theme(legend.position = "none")
p

# ggsave(file=paste0(fig_out_path, 'neuroecon_logit_build1.jpg'), p, height = 5, width=8, units="in")
```

```{r}
ggsave(file=paste0(fig_out_path, 'neuroecon_logit_legend.jpg'), legend, height = 2, width=11, units="in")
```

# Choice logit with theta corrected QV

```{r}
p = rbind(truev_mod %>% filter(term == "lottery_ev_diff"), qv_mod, qv_theta_mod) %>%
  mutate(reg = ifelse(term %in% c("lottery_ev_diff", "lottery_ev_diff_theta"), "Lottery EV Difference", ifelse(term == "fractal_prob_diff", "True Fractal Value Difference", ifelse(term %in% c("fractal_qv_diff","fractal_qv_diff_theta"),"Fractal QV Difference", NA))),
         reg = factor(reg, levels=c("True Fractal Value Difference", "Lottery EV Difference", "Fractal QV Difference")),
         theta = grepl("theta", term),
         fract = ifelse(reg == "Fractal QV Difference", T, F)) %>%
  ggplot(aes(probFractalDraw, estimate, col=reg, group=term, alpha = theta))+
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2, size=3)+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  scale_color_manual(values = cbbPalette[2:1])+
  scale_alpha_manual(guide = "none", values=c(.5, 1))+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.03, inherit.aes = F)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.03, inherit.aes = F)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.03, inherit.aes = F)+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x= "p(FD)", y="Beta estimate")+
  expand_limits(y=c(-1,11))+
  scale_y_continuous(breaks=seq(0, 10, 2.5))

ggsave(file=paste0(fig_out_path, 'neuroecon_logit_build2.jpg'), p, height = 5, width=8, units="in")
p
```

# Plain RT inverse U

```{r}
p = clean_beh_data %>%
  mutate(logRt = log(reactionTime)) %>%
  group_by(probFractalDraw) %>%
  summarise(.groups = "keep",
            mean_logRt = mean(logRt),
            sem_logRt = sd(logRt)/sqrt(n())) %>%
  ggplot(aes(probFractalDraw, mean_logRt))+
  geom_point(position=position_dodge(width=.5), size=3)+
  geom_errorbar(aes(ymin = mean_logRt - sem_logRt, ymax = mean_logRt + sem_logRt), width=.2,position=position_dodge(width=.5), size=2)+
  labs(y="Mean Log RT", x="p(FD)")+
  scale_color_manual(values = c(cbbPalette[3], cbbPalette[5:6]))+
   theme(panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.text = element_text(size=18),
        legend.title = element_text(size=20))+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.05)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.05)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.05)+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.43, .43))
  

ggsave(file=paste0(fig_out_path, 'neuroecon_rt_by_pFrac.jpg'), p, height = 5, width=8, units="in")
p
```

# DDM demo plots

```{r}
sim_trial_list = list()
fit_trial_list = list()
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion.R'))
sim_trial_list[['model1']] = sim_trial
fit_trial_list[['model1']] = fit_trial
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_twoIntegrators_sepProbDistortion.R'))
sim_trial_list[['model2']] = sim_trial
source(paste0(helpers_path, 'ddModels/r_ddm_models/ddm_oneIntegrator_sepProbDistortion_earlyIntegration.R'))
sim_trial_list[['model1ea']] = sim_trial
fit_trial_list[['model1ea']] = fit_trial
```

## Single integrator

```{r}
pFrac = .3
theta = .7
EVLeft = .7
EVRight = .5
distortedEVDiff = (1-pFrac)*(EVLeft-EVRight)
QVLeft = .1
QVRight = .4
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)

tmp = sim_trial_list[['model1']](d = .05, sigma = .03, distortedEVDiff = distortedEVDiff, distortedQVDiff = distortedQVDiff, probFractalDraw = NA, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

p = tmp$debug_df %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  geom_line(size=3)+
  geom_vline(aes(xintercept=0), size=1)+
  geom_hline(aes(yintercept=1), size=2)+
  geom_hline(aes(yintercept=-1), size=2)+
  annotate(geom="segment", x=0, xend=max(tmp$debug_df$time), y=0, yend=0, size=2, linetype="dashed")+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x = "Time", y="RDV")+
  scale_y_continuous(breaks=c(-1,0,1))+
  annotate(geom="text", x=.5, y = .85, label = "Left", hjust=0, size = 11)+
  annotate(geom="text", x=.5, y = -.85, label = "Right", hjust=0, size = 11)+
  annotate(geom="text", x=-7, y = -.85, label = "Stimulus presentation", hjust=0, size = 8, angle=90)

p
ggsave(file=paste0(fig_out_path, 'neuroecon_oneInt_demo.jpg'), p, height = 5, width=8, units="in")
```

## Two integrators

```{r}
pFrac = .3
theta = .7
EVLeft = .7
EVRight = .5
distortedEVDiff = (1-pFrac)*(EVLeft-EVRight)
QVLeft = .1
QVRight = .4
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)

sim_dLott = .02
sim_dFrac = .06
sim_sigma = .03

tmp = sim_trial_list[['model2']](dLott=sim_dLott, dFrac=sim_dFrac,  sigmaLott = sim_sigma, sigmaFrac = sim_sigma, distortedEVDiff = distortedEVDiff , distortedQVDiff = distortedQVDiff , probFractalDraw = 2, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE)

p = tmp$debug_df %>%
  select(lotteryRDV, fractalRDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  geom_line(size=3)+
  geom_vline(aes(xintercept=0), size=1)+
  geom_hline(aes(yintercept=1), size=2)+
  geom_hline(aes(yintercept=-1), size=2)+
  annotate(geom="segment", x=0, xend=max(tmp$debug_df$time), y=0, yend=0, size=2, linetype="dashed")+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x = "Time", y="RDV")+
  scale_y_continuous(breaks=c(-1,0,1))+
  annotate(geom="text", x=.5, y = .85, label = "Left", hjust=0, size = 11)+
  annotate(geom="text", x=.5, y = -.85, label = "Right", hjust=0, size = 11)+
  annotate(geom="text", x=-10, y = -.85, label = "Stimulus presentation", hjust=0, size = 8, angle=90)+
  scale_color_manual(values=cbbPalette[1:2])

ggsave(file=paste0(fig_out_path, 'neuroecon_twoInt_demo.jpg'), p, height = 5, width=8, units="in")
p
```

## Single integrator with early integration


```{r}
pFrac = .8
theta = .9
EVLeft = .7
EVRight = .5
distortedEVDiff = (1-pFrac)*(EVLeft-EVRight)
QVLeft = .1
QVRight = .4
distortedQVDiff = theta*pFrac*(QVLeft-QVRight)

tmp = sim_trial_list[['model1ea']](d = .05, sigma = .03, distortedEVDiff = distortedEVDiff, distortedQVDiff = distortedQVDiff, probFractalDraw = pFrac, barrierDecay = 0, bias = 0, EVLeft = NA, EVRight = NA, QVLeft = NA, QVRight = NA, debug=TRUE, theta=theta, stimDelay = 500)

p = tmp$debug_df %>%
  drop_na() %>%
  select(RDV, time) %>%
  gather(key, value, -time) %>%
  ggplot(aes(time, value, color=key))+
  geom_line(size=3)+
  geom_vline(aes(xintercept=0), size=1)+
  geom_hline(aes(yintercept=1), size=2)+
  geom_hline(aes(yintercept=-1), size=2)+
  geom_hline(aes(yintercept=0), size=2, linetype="dashed")+
  # annotate(geom="segment", x=0, xend=max(tmp$debug_df$time), y=0, yend=0, size=2, linetype="dashed")+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x = "Time", y="RDV")+
  scale_y_continuous(breaks=c(-1,0,1))+
  annotate(geom="text", x=.5, y = .85, label = "Left", hjust=0, size = 11)+
  annotate(geom="text", x=.5, y = -.85, label = "Right", hjust=0, size = 11)+
  annotate(geom="text", x=-7, y = -.85, label = "Stimulus presentation", hjust=0, size = 8, angle=90)+
  annotate(geom="text", x=30, y = 0.25, label = "If p(FD)>0.5", hjust=0, size = 8)

p
ggsave(file=paste0(fig_out_path, 'neuroecon_oneIntEarlyInt_demo.jpg'), p, height = 5, width=8, units="in")
```

# DDM fits

```{r}
cpueaters_path = '/Users/zeynepenkavi/CpuEaters/DescribedVsLearned_beh/analysis/helpers/'
source(paste0(helpers_path, 'optimPostProcess/get_optim_out.R'))
source(paste0(helpers_path,'ddModels/sim_task.R'))
source(paste0(helpers_path,'optimPostProcess/sim_sanity_checks.R'))
```

```{r}
subnums = c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "22", "23", "25", "27")
data_prefix ="sub"
data_suffix = "_data"
```

```{r}
clean_beh_data_asymmnonorm = clean_beh_data

sub_stims_asym = clean_beh_data_asymmnonorm %>%
  select(leftLotteryEV, rightLotteryEV, leftQValue, rightQValue, probFractalDraw, reactionTime, choiceLeft, subnum, distorted_ev_diff, distorted_qv_diff, theta) %>%
  rename(EVLeft = leftLotteryEV, EVRight = rightLotteryEV, QVLeft = leftQValue, QVRight = rightQValue, distortedEVDiff = distorted_ev_diff, distortedQVDiff = distorted_qv_diff)
```

## Single integrator

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamAsymmLinear/')

model = "oneIntegrator_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

Simulate predicted data

```{r}
oneIntPpcAsymmLinear = data.frame()

for(i in 1:length(unique(oneIntEstsAsymmLinear$subnum))){
  cur_sub = unique(oneIntEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = oneIntEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1", d=cur_pars$d, sigma=cur_pars$sigma)
  sim_subj$subnum = cur_sub
  oneIntPpcAsymmLinear = rbind(oneIntPpcAsymmLinear, sim_subj)
}

```

```{r}
p = sim_sanity_checks(oneIntPpcAsymmLinear, checks = c(5), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2, size=3)+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  theme(legend.position = "none",
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x= "p(FD)", y="Beta estimate")+
  expand_limits(y=c(-1,11))+
  scale_y_continuous(breaks=seq(0, 10, 2.5))

ggsave(file=paste0(fig_out_path, 'neuroecon_oneIntLogitSim.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
p = sim_sanity_checks(oneIntPpcAsymmLinear, checks = c(4), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(aes(alpha = data_type),size=3)+
  geom_errorbar(aes(ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt),width=.2,size=2)+
  labs(y="Mean Log RT", x="p(FD)")+
  scale_color_manual(values = c("black", "gray"))+
  scale_alpha_manual(values = c(1,.5))+
   theme(panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.position = "none")+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.43, .43))

ggsave(file=paste0(fig_out_path, 'neuroecon_oneIntRTSim.jpg'), p, height = 5, width=8, units="in")
p
```

## Two integrators

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitTwoInts_oneParamAsymmLinear/')

model = "twoIntegrators_sepProbDistortion"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
twoIntsEstsAsymmLinear = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(dLott = mean(Param1),
            dFrac = mean(Param2),
            sigmaLott = mean(Param3),
            sigmaFrac = mean(Param4))
```

Simulate predicted data

```{r}
twoIntsPpcAsymmLinear = data.frame()

for(i in 1:length(unique(twoIntsEstsAsymmLinear$subnum))){
  cur_sub = unique(twoIntsEstsAsymmLinear$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub)
  cur_pars = twoIntsEstsAsymmLinear %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model2", dLott=cur_pars$dLott, dFrac=cur_pars$dFrac, sigmaLott=cur_pars$sigmaLott, sigmaFrac=cur_pars$sigmaFrac)
  sim_subj$subnum = cur_sub
  twoIntsPpcAsymmLinear = rbind(twoIntsPpcAsymmLinear, sim_subj)
}

```


```{r}
p = sim_sanity_checks(twoIntsPpcAsymmLinear , checks = c(5), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2, size=3)+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  theme(legend.position = "none",
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x= "p(FD)", y="Beta estimate")+
  expand_limits(y=c(-1,11))+
  scale_y_continuous(breaks=seq(0, 10, 2.5))

ggsave(file=paste0(fig_out_path, 'neuroecon_twoIntsLogitSim.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
p = sim_sanity_checks(twoIntsPpcAsymmLinear, checks = c(4), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(aes(alpha = data_type),size=3)+
  geom_errorbar(aes(ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt),width=.2,size=2)+
  labs(y="Mean Log RT", x="p(FD)")+
  scale_color_manual(values = c("black", "gray"))+
  scale_alpha_manual(values = c(1,.5))+
   theme(panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.position = "none")+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.43, .43))

ggsave(file=paste0(fig_out_path, 'neuroecon_twoIntsRTSim.jpg'), p, height = 5, width=8, units="in")
p
```

## Single integrator with early integration

```{r}
optim_out_path = paste0(cpueaters_path, 'ddModels/cluster_scripts/optim_out/fitOneInt_oneParamAsymmLinear_earlyIntegration/')

model = "oneIntegrator_sepProbDistortion_earlyIntegration"  

ddm_fit_pars = data.frame()

for(i in 1:length(subnums)){
  cur_subnum = subnums[i]
  tmp = get_optim_out(model_=model, data_=paste0(data_prefix, cur_subnum, data_suffix), optim_out_path_=optim_out_path, iters_ = F)
  tmp$subnum = cur_subnum
  ddm_fit_pars = rbind.all.columns(tmp, ddm_fit_pars)
}
```

Summarise subject parameters as a mean of the converged values from different starting points

```{r}
oneIntEstsAsymmLinear_earlyInt = ddm_fit_pars %>%
  group_by(subnum) %>%
  summarise(d = mean(Param1),
            sigma = mean(Param2))
```

```{r}
oneIntPpcAsymmLinear_earlyInt = data.frame()

for(i in 1:length(unique(oneIntEstsAsymmLinear_earlyInt$subnum))){
  cur_sub = unique(oneIntEstsAsymmLinear_earlyInt$subnum)[i]
  cur_stims =  sub_stims_asym %>% filter(subnum == cur_sub) %>%
    mutate(probFractalDraw = as.numeric(as.character(probFractalDraw)))
  cur_pars = oneIntEstsAsymmLinear_earlyInt %>% filter(subnum == cur_sub)
  sim_subj = sim_task(cur_stims, model_name = "model1ea", d=cur_pars$d, sigma=cur_pars$sigma, theta=unique(cur_stims$theta), stimDelay=500)
  sim_subj$subnum = cur_sub
  oneIntPpcAsymmLinear_earlyInt = rbind(oneIntPpcAsymmLinear_earlyInt, sim_subj)
}

```


```{r}
p = sim_sanity_checks(oneIntPpcAsymmLinear_earlyInt , checks = c(5), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(size=3)+
  geom_line(size=3)+
  geom_errorbar(aes(ymin = estimate - std.error, ymax = estimate +std.error), width=0.2, size=3)+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01, inherit.aes = F)+
  theme(legend.position = "none",
        axis.text = element_text(size=24),
        axis.title = element_text(size=24))+
  labs(color="", x= "p(FD)", y="Beta estimate")+
  expand_limits(y=c(-1,11))+
  scale_y_continuous(breaks=seq(0, 10, 2.5))

ggsave(file=paste0(fig_out_path, 'neuroecon_oneIntEarlyIntLogitSim.jpg'), p, height = 5, width=8, units="in")
p
```

```{r}
p = sim_sanity_checks(oneIntPpcAsymmLinear_earlyInt, checks = c(4), true_data = sub_stims_asym, compare_logits = T, logit_facets = F, return_plot = T)

p = p[[1]] +
  geom_point(aes(alpha = data_type),size=3)+
  geom_errorbar(aes(ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt),width=.2,size=2)+
  labs(y="Mean Log RT", x="p(FD)")+
  scale_color_manual(values = c("black", "gray"))+
  scale_alpha_manual(values = c(1,.5))+
   theme(panel.grid = element_blank(),
        axis.text = element_text(size=24),
        axis.title = element_text(size=24),
        legend.position = "none")+
  geom_rect(aes(xmin=.5, xmax=1.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=5.5, xmax=6.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  geom_rect(aes(xmin=10.5, xmax=11.5, ymin=-Inf, ymax=Inf), color="transparent", fill="light gray", alpha=0.01)+
  scale_y_continuous(breaks = c(-.3, 0, .3), limits=c(-.43, .43))

ggsave(file=paste0(fig_out_path, 'neuroecon_oneIntEarlyIntRTSim.jpg'), p, height = 5, width=8, units="in")
p
```