---
title: "Experience vs. description based decision-making project: Behavioral manipulation checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(gridExtra)
library(brms)
library(here)
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
# theme_set(theme_bw())
theme_set(theme_classic())
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
```

```{r include=FALSE}
helpers_path = here('analysis/helpers/')
source(paste0(helpers_path,'rlModels/fit_rl_hierarchical.R'))
source(paste0(helpers_path,'add_inferred_pars.R'))
```

Add estimated model parameters and inferred bundle values using those parameters.

```{r}
clean_beh_data = add_inferred_pars(clean_beh_data, par_ests)
```

# Psychometric choice curves

Psychometric curve for all trials with weighted value difference. Q-values for the fractals and the weights for the two attributes are determined by the posterior means of the hierarchically fit two systems model. Blue lines indicate individual subjects.

```{r}
clean_beh_data %>%
  ggplot(aes(leftBundleValAdv, choiceLeft))+
  geom_line(aes(group=subnum),stat="smooth",formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, se=FALSE, alpha=.1, size=1, color=cbbPalette[5])+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, color=cbbPalette[3], alpha=.75)+
  labs(y = "p(Left)", x = "V(left)-V(right)", title="Psychometric choice curve based on weighted value difference between bundles")
```

The dependence of choice on the bundle value difference holds for all levels of p(Frac) (not shown).

```{r warning=FALSE, eval=FALSE}
clean_beh_data %>%
  ggplot(aes(leftbundleValAdv, choiceLeft))+
  geom_line(aes(group=subnum),stat="smooth",formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, se=FALSE, alpha=.1, size=1, color=cbbPalette[5])+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, color=cbbPalette[3], alpha=.75)+
  labs(y = "p(Left)", x = "V(left)-V(right)")+
  facet_grid(. ~ probFractalDraw)+
  theme(axis.ticks.x=element_blank(),
        axis.text.x=element_blank())
```

## Single relevant attribute trials

If subjects have understood the task then in these trials only the value difference of the relevant attribute should have an effect on choice. This is true on average as shown in the figure below but the blue lines depicting individual subjects suggest that there are individual differences in how much the choice relies on the Q-value difference even when it is the only relevant attribute. This will be explored more below.

```{r warning=FALSE}
clean_beh_data %>%
   filter(probFractalDraw == 1 | probFractalDraw == 0) %>%
  select(subnum, leftQVAdv, leftEVAdv, choiceLeft, probFractalDraw) %>%
  gather(key, value, -choiceLeft, -probFractalDraw, -subnum) %>%  
  mutate(key = ifelse(key == "leftEVAdv", "EV_left - EV_right", "QV_left - QV_right"),
         probFractalDraw = ifelse(probFractalDraw == 0, "p(Fractal)=0", "p(Fractal)=1")) %>%
  ggplot(aes(value, choiceLeft))+
  # geom_jitter(width=0.03, height=0.08, alpha = 0.05)+
  geom_line(aes(group=subnum),stat='smooth',formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, se=FALSE, alpha=.1, size=1, color=cbbPalette[5])+
  geom_smooth(formula = 'y~x', method = "glm", method.args = list(family=binomial), fullrange=TRUE, color=cbbPalette[3])+
  facet_grid(probFractalDraw~key)+
  xlab("")+
  ylab("p(Left)")
```

<!-- Multilevel model checking if the slopes of the top row above are different than 0. -->

```{r eval=FALSE}
m1 = brm(choiceLeft ~ leftQVAdv + leftEVAdv + (1|subnum),
        data=tmp %>% filter(probFractalDraw == 0), family=bernoulli(link="logit"))
```

<!-- When probability of a fractal is 0 the expected value (EV) difference between the lotteries (i.e. the only relevant attribute of each bundle) has a strong effect. The higher the EV of the left lottery the more likely the left bundle is chosen.  -->

<!-- There is also a much smaller negative effect of the Q-value difference even though the fractal values should be irrelevant.  -->

```{r eval=FALSE}
summary(m1)
```

<!-- Multilevel model checking if the slopes of the bottom row above are different than 0. -->

```{r eval=FALSE}
m2 = brm(choiceLeft ~ leftQVAdv + leftEVAdv + (1|subnum),
        data=tmp %>% filter(probFractalDraw == 1), family=bernoulli(link="logit"))
```

<!-- When the probability of the fractal draw is 1 so the reward only depends on the fractals only the learned Q-values for the fractals have an effect on choice (the lottery EV difference has no effect). -->

```{r eval=FALSE}
summary(m2)
```

```{r eval=FALSE}
rm(tmp, m1, m2)
```

<!-- # Probability distortion -->

```{r eval=FALSE, echo=FALSE}
tmp = par_ests %>%
  group_by(subnum, par) %>%
  summarise(est = mean(value), .groups='keep') %>%
  filter(par != "beta" & par != "alpha") %>%
  spread(par, est)

tmp = do.call("rbind", replicate(11, tmp, simplify = FALSE)) %>%
  arrange(subnum) %>%
  ungroup() %>%
  mutate(pFrac = rep(seq(0, 1, .1), 25), 
         wpFrac = (delta*pFrac^gamma)/(delta*pFrac^gamma + (1-pFrac)^gamma)) 

tmp %>%
  mutate(delta_gt_1 = ifelse(delta>=1, "delta >= 1", "delta < 1 "),
         gamma_gt_1 = ifelse(gamma>=1,"gamma >= 1", "gamma < 1")) %>%
  ggplot(aes(pFrac, wpFrac, group=subnum))+
  geom_line(aes(col = as.factor(gamma_gt_1), linetype=as.factor(delta_gt_1)))+
  geom_abline(slope=1, intercept=0, linetype="dashed")+
  labs(x="p(Fractal)", y="w(pFractal)", title="Distortion of p(Fractal)", color = element_blank(), linetype=element_blank())
```

# Attribute weights

Since there are two attributes in each bundle the observed and learned values of these attributes can agree or disagree on which bundle is better to choose. Trials where the fractal and lottery value difference favors the same bundle are called *no conflict* trials and trials where they favor different bundles are called *conflict* trials. 

The true weight of each attribute is controlled and determined by the probability that a trial's reward would depend on a fractal or lottery draw. Subjects' choice can, however, indicate that they distort these weights. If a subjective distortion of this sort exists it should be reflected in choice as a bias towards one attribute over the other.

In conflict trials:  
- when reward depends more on lotteries (p(Fractal)<.5) people correctly choose the bundle with the better lottery above chance.  
- when reward depends equally on both attributes (p(Fractal)=.5) people are slightly *biased* towards the bundle with the better lottery.  
- when reward depends more on fractals (p(Fractal)>.5) people choose the bundle with the better fractal more frequently than when the reward depended more on lotteries *but not as much as they choose the better lottery for the equivalent levels of relevance*  

In no conflict trials:  
- when reward depends more or equally on lotteries people correctly choose the bundle that has both the better fractal and the better lottery.  

Choice patterns for both conflict and no conflict trials when p(Fractal)>.5 suggests that subjects' decision **correctly** relies less on the lottery and more on the fractal values but the inference about the inference about the fractal values is more error prone. This might be due to noise in the fractal value representation because it involves learning and cannot be read off the screen.  

```{r}
clean_beh_data %>% 
  group_by(probFractalDraw, subnum, conflictTrial) %>%
  summarise(choseBetterLottery = mean(choseBetterLottery),
            .groups='keep') %>%
  ungroup() %>%
  group_by(probFractalDraw, conflictTrial) %>%
  summarise(sem_choseBetterLottery = sem(choseBetterLottery),
            choseBetterLottery = mean(choseBetterLottery),
            .groups='keep') %>%
  ggplot(aes(as.factor(probFractalDraw), choseBetterLottery))+
  geom_point(color=cbbPalette[3], size = 2)+
  geom_errorbar(aes(ymax=choseBetterLottery + sem_choseBetterLottery, ymin=choseBetterLottery - sem_choseBetterLottery), width = 0.2, color=cbbPalette[3])+
  geom_line(group=1, color=cbbPalette[3])+
  geom_hline(yintercept=0.5, linetype="dashed", size=1.5)+
  facet_grid(conflictTrial~.)+
  labs(x="p(Fractal)",y="Choice of bundle with better lottery")

```

## Psychometric analysis

To confirm that subjects' choice relied more on the relevant attribute regardless of conflict type we ran a logit analysis where we modeled choice as a function of both the expected value and the learned Q-value difference. We used a fixed effects analysis allowing for subject-specific random intercepts.

```{r}
source(paste0(helpers_path,'logit_choiceLeft_mixedEffects_conflictCollapsed.R'))
```

- Regardless of whether there is a conflict between the attributes for each bundle the effect of the fractal QV difference  **correctly increases** as fractals become more consequential for the trial's reward while the effect of the lottery EV difference **correctly decreases**.   
- While the effect of the QV difference is **correctly 0** when the lottery matters more lottery EV difference has an **biasing positive** effect on choice even when it is less relevant for the trial's reward than the fractals. This reduces to 0 only when the lottery values are entirely irrelevant.  
- Consequently, for the same level of relevance lottery EV difference has a bigger effect on choice than the fractal QV difference.

```{r}
out_choiceLeft %>%
  mutate(est = as.numeric(est),
         l95 = as.numeric(l95),
         u95 = as.numeric(u95)) %>%
  mutate(iv = ifelse(iv == "leftEVAdv", "EV(left)-EV(right)", "QV(left)-QV(right)")) %>%
  ggplot(aes(probFractalDraw, est, col=iv))+
  geom_point(size=2)+
  geom_line(aes(group=iv))+
  geom_errorbar(aes(ymin=l95, ymax=u95), width=0.1)+
  geom_hline(yintercept=0,linetype="dashed")+
  theme(legend.position = "bottom")+
  scale_color_manual(values=c(cbbPalette[2], cbbPalette[1]))+
  labs(color="", y="Logit slope estimate (DV = choiceLeft)", x="p(Fractal)")
```

